### 2011-02-17 lids/twittersearchwrap/paper/paper.tex
added paper

\documentclass[a4paper]{article}

\usepackage{fullpage}
\usepackage{setspace}
\usepackage{url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{latexsym}

\usepackage{graphicx}
\usepackage{subfig}

\onehalfspacing

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{query}{Query}

\newcommand{\nop}[1]{}

\title{Mapping Microblogging Posts to Encyclopedia Articles}
\author{David M\"{u}ller \and Uta L\"{o}sch \and Andreas Harth}

\begin{document}

\maketitle

\begin{abstract}
We describe a method to map Twitter posts to Wikipedia articles.
\end{abstract}

\section{Introduction}

Need context/signal to feed wikifier \cite{key:wikifier}.

\section{Method Overview}

System Architecture shown in Figure \ref{fig:arch}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=.6\linewidth]{architecture.eps}
  \caption{System architecture}
  \label{fig:arch}
\end{figure}

\section{Experiments and Evaluation}

Trending topics are listed in Table \ref{tbl:terms}.

\begin{table}[ht*]
\centering
\begin{tabular}{ l }
Search term                    \\
\hline
\#s21 \\
Karlsruhe\\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

\section{Conclusion}

\bibliographystyle{abbrv}
\bibliography{bib}

\end{document}

### 2011-02-17 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Follow external links option - still alpha

@@ -1,15 +1,19 @@
 package com.ontologycentral.twittersearchwrap;
 
 import java.io.BufferedReader;
+import java.io.ByteArrayInputStream;
+import java.io.DataInputStream;
 import java.io.IOException;
 import java.io.InputStream;
 import java.io.InputStreamReader;
 import java.io.OutputStream;
+import java.io.Reader;
 import java.io.StringReader;
 import java.net.HttpURLConnection;
 import java.net.URI;
 import java.net.URISyntaxException;
 import java.net.URL;
+import java.net.URLConnection;
 import java.net.URLEncoder;
 import java.text.SimpleDateFormat;
 import java.util.Calendar;
@@ -26,6 +30,14 @@ import javax.xml.transform.Transformer;
 import javax.xml.transform.TransformerException;
 import javax.xml.transform.stream.StreamResult;
 import javax.xml.transform.stream.StreamSource;
+
+import com.google.appengine.api.urlfetch.FetchOptions;
+import com.google.appengine.api.urlfetch.FetchOptions.Builder;
+import com.google.appengine.api.urlfetch.HTTPMethod;
+import com.google.appengine.api.urlfetch.HTTPRequest;
+import com.google.appengine.api.urlfetch.HTTPResponse;
+import com.google.appengine.api.urlfetch.URLFetchService;
+import com.google.appengine.api.urlfetch.URLFetchServiceFactory;
 
 @SuppressWarnings("serial")
 public class SearchServlet extends HttpServlet {
@@ -100,25 +112,77 @@ public class SearchServlet extends HttpServlet {
 //					cache.put(u, str);
 //				}
 				
-				
 				// WIKIFY Search feed data
 
 				String[] split = str.split("</title>");
-				
 				StringBuilder tweets = new StringBuilder();
 				
 				for(int i = 1; i<split.length-1; i++){
 					
 					String[] splitsplit = split[i].split("<title>");
-					
 					tweets.append(" " + splitsplit[1]);
 					
+				}
+				
+				// If extern=true get content from referenced websites as string and use in wikifier
+				String extern = req.getParameter("extern");
+				if(extern==null){
+					extern = "false";
+				}
+				
+				StringBuffer externalWebsites = new StringBuffer();
+				
+				if(extern.equals("true")){
+					
+					// Get HTTP-links
+					String[] splitContent = str.split("</content>");
+					StringBuilder tweetsHTML = new StringBuilder();
+					
[…]

### 2011-02-18 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java
Getting content from external websites - now working

@@ -18,6 +18,7 @@ public class Wikify {
 	
 	public static String cleanTweets (String input){
 	   input = input.replace("http://", "");
+	   input = input.replaceAll("<.*>", "");
        return input;
 	}
 

### 2011-02-18 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Getting content from external websites - now working

@@ -2,18 +2,13 @@ package com.ontologycentral.twittersearchwrap;
 
 import java.io.BufferedReader;
 import java.io.ByteArrayInputStream;
-import java.io.DataInputStream;
 import java.io.IOException;
 import java.io.InputStream;
 import java.io.InputStreamReader;
 import java.io.OutputStream;
-import java.io.Reader;
 import java.io.StringReader;
 import java.net.HttpURLConnection;
-import java.net.URI;
-import java.net.URISyntaxException;
 import java.net.URL;
-import java.net.URLConnection;
 import java.net.URLEncoder;
 import java.text.SimpleDateFormat;
 import java.util.Calendar;
@@ -31,7 +26,6 @@ import javax.xml.transform.TransformerException;
 import javax.xml.transform.stream.StreamResult;
 import javax.xml.transform.stream.StreamSource;
 
-import com.google.appengine.api.urlfetch.FetchOptions;
 import com.google.appengine.api.urlfetch.FetchOptions.Builder;
 import com.google.appengine.api.urlfetch.HTTPMethod;
 import com.google.appengine.api.urlfetch.HTTPRequest;
@@ -61,11 +55,11 @@ public class SearchServlet extends HttpServlet {
 			
 			query = URLEncoder.encode(query, "utf-8");
 
-			System.out.println(query);
+			System.out.println("SEARCH-QUERY: " + query);
 
 			URL u = new URL("http://search.twitter.com/search.atom?lang=en&q=" + query + "&rpp=100");
 			
-			System.out.println(u);
+			System.out.println("SEARCH-URL:   " + u);
 			
 			try {
 				if (cache != null && cache.containsKey(u)) {
@@ -154,34 +148,59 @@ public class SearchServlet extends HttpServlet {
 					for (int i = 0; i < urls.length; i++) {
 						
 						// Dont use internal twitter links containing javascript which cannot be handled
-						if(!urls[i].contains(";")){
-							HTTPRequest request = new HTTPRequest(new URL(urls[i]), HTTPMethod.POST, Builder.allowTruncate());
-							URLFetchService service = URLFetchServiceFactory.getURLFetchService();
-							HTTPResponse response = service.fetch(request);
-							byte[] content = response.getContent();
+						if(!urls[i].contains("twitter")){
 							
+							HTTPResponse response = null;
+							Boolean timeout = false;
+							byte[] content = null;
+							
+							try {
[…]

### 2011-02-18 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -12,7 +12,7 @@ public class Wikify {
 	
 	public static void main(String[] args){
 		
-		startWikify(args[0]);
+		startWikify(args[0], "en");
 		
 	};
 	
@@ -22,9 +22,13 @@ public class Wikify {
        return input;
 	}
 
-	public static Set<String> startWikify (String input){
-		
+	public static Set<String> startWikify (String input, String lang){
 		String uri = "http://km.aifb.kit.edu/services/wpmservlet-en/web/service";
+		
+		if(lang.equals("de")){
+			uri = "http://km.aifb.kit.edu/services/wpmservlet-de/web/service";
+		}
+		
 	    Wikifier w = new Wikifier(uri, "david's bot");
 	    
 	    input = cleanTweets(input);

### 2011-02-18 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -11,10 +11,13 @@ import java.net.HttpURLConnection;
 import java.net.URL;
 import java.net.URLEncoder;
 import java.text.SimpleDateFormat;
+import java.util.ArrayList;
 import java.util.Calendar;
 import java.util.Iterator;
+import java.util.List;
 import java.util.Locale;
 import java.util.Set;
+import java.util.StringTokenizer;
 
 import javax.cache.Cache;
 import javax.servlet.ServletContext;
@@ -27,6 +30,7 @@ import javax.xml.transform.stream.StreamResult;
 import javax.xml.transform.stream.StreamSource;
 
 import com.google.appengine.api.urlfetch.FetchOptions.Builder;
+import com.google.appengine.api.urlfetch.HTTPHeader;
 import com.google.appengine.api.urlfetch.HTTPMethod;
 import com.google.appengine.api.urlfetch.HTTPRequest;
 import com.google.appengine.api.urlfetch.HTTPResponse;
@@ -50,16 +54,20 @@ public class SearchServlet extends HttpServlet {
 
 		try {
 			String query = req.getParameter("q");
+			String lang = req.getParameter("lang");
+			if(lang==null){
+				lang="en";
+			}
 //			String id = req.getRequestURI();
 //			id = id.substring(id.lastIndexOf("/")+1);
 			
 			query = URLEncoder.encode(query, "utf-8");
 
-			System.out.println("SEARCH-QUERY: " + query);
+			System.out.println("SEARCH-QUERY:   " + query);
 
-			URL u = new URL("http://search.twitter.com/search.atom?lang=en&q=" + query + "&rpp=100");
+			URL u = new URL("http://search.twitter.com/search.atom?q=" + query + "&rpp=100");
 			
-			System.out.println("SEARCH-URL:   " + u);
+			System.out.println("SEARCH-URL:     " + u);
 			
 			try {
 				if (cache != null && cache.containsKey(u)) {
@@ -153,13 +161,18 @@ public class SearchServlet extends HttpServlet {
 							HTTPResponse response = null;
 							Boolean timeout = false;
 							byte[] content = null;
+							String encoded = "utf-8";
 							
 							try {
 								HTTPRequest request = new HTTPRequest(new URL(urls[i]), HTTPMethod.GET, Builder.allowTruncate());
 								URLFetchService service = URLFetchServiceFactory.getURLFetchService();
 								response = service.fetch(request);
[…]

### 2011-02-18 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -172,7 +172,7 @@ public class SearchServlet extends HttpServlet {
 								encoded = responseHeader.getValue().split("charset=")[1];
 								content = response.getContent();
 							} catch (Exception e) {
-								System.out.println("TIMEOUT connecting to " + urls[i]);
+								System.out.println("ERROR connecting to " + urls[i]);
 								timeout = true;
 							}
 							

### 2011-02-18 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -172,8 +172,8 @@ public class SearchServlet extends HttpServlet {
 								encoded = responseHeader.getValue().split("charset=")[1];
 								content = response.getContent();
 							} catch (Exception e) {
-								System.out.println("ERROR connecting to " + urls[i]);
-								timeout = true;
+//								System.out.println("ERROR connecting to " + urls[i]);
+//								timeout = true;
 							}
 							
 							if (!timeout && response!=null && content!=null){

### 2011-02-18 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java
Wichtige Änderungen an den Regex

@@ -17,8 +17,8 @@ public class Wikify {
 	};
 	
 	public static String cleanTweets (String input){
-	   input = input.replace("http://", "");
-	   input = input.replaceAll("<.*>", "");
+	   input = input.replaceAll("http://.*?\\s", "");
+	   input = input.replaceAll("<.*?>", "");
        return input;
 	}
 

### 2011-02-18 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -186,7 +186,7 @@ public class SearchServlet extends HttpServlet {
 								String lines = null;
 								Boolean contained1 = false;
 								Boolean contained2 = false;
-								while ((lines = reader.readLine()) != null && words.size()<1000) {
+								while ((lines = reader.readLine()) != null && words.size()<50) {
 								StringTokenizer st = new StringTokenizer(lines.toString().replaceAll("\\<.*?\\>", ""));
 								if(contained1 && lines.toLowerCase().contains(("<\\body>"))){
 									contained2 = true;
@@ -195,7 +195,7 @@ public class SearchServlet extends HttpServlet {
 									contained1 = true;
 								}
 								if(contained1 && !contained2){
-									while (st.hasMoreTokens() && words.size()<1000) {
+									while (st.hasMoreTokens() && words.size()<50) {
 										  String tok = st.nextToken();
 										  words.add(tok);
 									}

### 2011-02-18 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -32,7 +32,8 @@ public class Wikify {
 	    Wikifier w = new Wikifier(uri, "david's bot");
 	    
 	    input = cleanTweets(input);
-			               
+		System.out.println("WIKIFIER Input:");
+		System.out.println(input);
 	    Node[] nx = new Node[] { DC.TITLE, new Literal(input) } ;
 			               
 		Set<Node[]> set = new HashSet<Node[]>();

### 2011-02-18 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -32,8 +32,8 @@ public class Wikify {
 	    Wikifier w = new Wikifier(uri, "david's bot");
 	    
 	    input = cleanTweets(input);
-		System.out.println("WIKIFIER Input:");
-		System.out.println(input);
+		//System.out.println("WIKIFIER Input:");
+		//System.out.println(input);
 	    Node[] nx = new Node[] { DC.TITLE, new Literal(input) } ;
 			               
 		Set<Node[]> set = new HashSet<Node[]>();

### 2011-02-21 lids/twittersearchwrap/paper/paper.tex

@@
-\documentclass[a4paper]{article}
+\documentclass{llncs}
+%\documentclass[a4paper]{article}
 
@@
 
-\newtheorem{definition}{Definition}
-\newtheorem{theorem}{Theorem}
-\newtheorem{example}{Example}
+%\newtheorem{definition}{Definition}
+%\newtheorem{theorem}{Theorem}
+%\newtheorem{example}{Example}
 \newtheorem{query}{Query}
@@
 \title{Mapping Microblogging Posts to Encyclopedia Articles}
-\author{David M\"{u}ller \and Uta L\"{o}sch \and Andreas Harth}
-
+\author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
+\institute{
+	Karlsruhe Institute of Technology (KIT), D-76131 Karlsruhe, Germany\\ 
+	\email{uta.loesch@kit.edu},\\
+	\email{david.mueller@student.kit.edu},\\
+	\email{harth@kit.edu}
+}
 \begin{document}
@@
 
+Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
+The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters.
+Twitter has a total of about 190 million of users who produce 65 million tweets a day.
+Thus, Twitter represents a huge data source on the web.
+
+Twitter offers the possibility to search for tweets containing a specific term or hash tags.
+This search returns a fixed number of most recent tweets containing the search term.
+However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for.
+As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+To facilitate this
+
+Why need Wikipedia entities?
+
 Need context/signal to feed wikifier \cite{key:wikifier}.
@@
   \centering
-  \includegraphics[width=.6\linewidth]{architecture.eps}
+  \includegraphics[width=.6\linewidth]{architecture}
   \caption{System architecture}
@@
 
+\begin{definition}[Stability]
+
+\end{definition}
+
+\section{Related Work}
+
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before.
+
+Passant et al.
+\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hash tags.
+The idea is to use URIs as hash tags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
 \section{Conclusion}

### 2011-02-21 trunk/lids/twittersearchwrap/paper/paper.tex

--- 2011-02-21 lids/twittersearchwrap/paper/paper.tex
@@
 As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
-To facilitate this
+To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
+These entities will not only help to understand the search terms
 
@@
 
+Methods performed by the implemented system can be grouped into five sequential
+steps. 
+In a first step the wrapper fetches the atom feed generated by the
+twitter search api\footnote{\url{http://dev.twitter.com/doc/get/search}} to a
+search query. The generated feed contains information about the 100 most recent
+twitter posts and their authors which match the search query.
+
 System Architecture shown in Figure \ref{fig:arch}.
@@
   \includegraphics[width=.6\linewidth]{architecture}
-  \caption{System architecture}
+  \caption{System Architecture}
   \label{fig:arch}
@@
 
-\begin{table}[ht*]
-\centering
-\begin{tabular}{ l }
-Search term                    \\
-\hline
-\#s21 \\
-Karlsruhe\\
-\end{tabular}
-\caption{Search terms}\label{tbl:terms}
-\end{table}
+%\begin{table}[ht*]
+%\centering
+%\begin{tabular}{ 1 }
+%Search term                    \\
+%\hline
+%\#s21 \\
+%Karlsruhe\\
+%\end{tabular}
+%\caption{Search terms}\label{tbl:terms}
+%\end{table}
 
@@
 
-Passant et al.
-\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+Passant et al. \cite{key:smob} have proposed a data model for making twitter
+data available on the Semantic Web.
 They propose a data model which allows for the association of URIs with users, microblogs and microposts.

### 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 
-Methods performed by the implemented system can be grouped into five sequential
-steps. 
-In a first step the wrapper fetches the atom feed generated by the
-twitter search api\footnote{\url{http://dev.twitter.com/doc/get/search}} to a
-search query. The generated feed contains information about the 100 most recent
-twitter posts and their authors which match the search query.
-
-System Architecture shown in Figure \ref{fig:arch}.
+The implemented system (further called twitter search wrapper) is called with
+a query and returns a rdf\footnote{\url{http://www.w3.org/RDF/}} document
+describing the most recent twitter posts (further called tweets) matching the
+given query. The returned rdf document furthermore contains a mapping of the
+query to Wikipedia articles which based on the content published by users that most recently used the query in their
+posts maps to articles best describing the content of tweets related to the
+query. An overview of the System Architecture is given in Figure \ref{fig:arch}.
+In detail, methods performed by the twitter search wrapper can be grouped
+and best described in five sequential steps (see Figure \ref{fig:arch}) .
 
@@
 \end{figure}
+
+In a first step the implemented twitter search wrapper fetches the atom feed
+generated by the twitter search
+api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
+query. The generated feed contains information about the 100 most recently published publicly visible tweets and
+their authors which match the search query. The tweets itself are described by
+their content, publishing date, authors and optionally a geographic location.
 

### 2011-02-22 lids/twittersearchwrap/paper/paper.tex

@@
 
-System Architecture shown in Figure \ref{fig:arch}.
+The implemented
+system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
+(further called Twitter Search Wrapper) is called with a query and returns a
+rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
+twitter posts (further called tweets) matching the given query. The returned rdf
+document furthermore contains a mapping of the query to Encyclopedia articles
+which based on the content published by users that most recently used the query
+in their posts maps to articles best describing the content of tweets related to
+the query. An overview of the System Architecture is given in Figure
+\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
+Search Wrapper can be grouped into five sequential steps (see Figure
+\ref{fig:arch}) .
 
@@
   \includegraphics[width=.6\linewidth]{architecture}
-  \caption{System architecture}
+  \caption{System Architecture}
   \label{fig:arch}
 \end{figure}
+
+In a first step the Twitter Search Wrapper fetches the atom feed
+generated by the twitter search
+api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
+query. The generated feed contains information about the 100 most recently published publicly visible tweets and
+their authors which match the search query. The tweets itself are described by
+their content, publishing date, authors and optionally a geographic location.
+
+In a second (optional) step hyperlinks posted in tweets of the fetched
+feed are followed, content of the referenced website's body is fetched and
+processed to the Wrapper. This option is triggered calling the Wrapper
+service with attribute extern=true.
+
+The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
+tweets that matched the search query and optional content of their referenced websites is merged
+to a single input string which is used as input for the Wikifier. The service
+returns a list of matching articles of the English
+Wikipedia. Optionally the wrapper can be initially called with lang=de to
+trigger mapping to the German Wikipedia.
+
+The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
+generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
+describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
+DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
+Wikifier) describing the documents content.
 

### 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex

--- 2011-02-21 lids/twittersearchwrap/paper/paper.tex
@@
 
-\newcommand{\nop}[1]{}
+%\newcommand{\nop}[1]{}
 
@@
 \begin{abstract}
-We describe a method to map Twitter posts to Wikipedia articles.
+Search results on Twitter are hard to analyze and read.
+To facilitate understanding the meaning of a search term in the context of Twitter, we have developed a system which annotates search results with entities that best describe the search result, thus offering a means of quickly grasping the meaning of the search results and at the same time providing starting points for further exploration of the search results' context.
+In an evaluation we show that the entities used for annotation represent the tweet's content in a suitable manner and that the annotations remain stable over time, i.e.
+when executing the same search at different times, the same entities are returned.
 \end{abstract}
@@
 As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
-To facilitate this
+To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
+These entities will not only help to understand the search terms, but also serve as a starting point when searching for further information related to the search result.
+This also helps to determine what the meaning of cryptic hash tags such as $\#s21$ or $\#ka$ mean.
 
-Why need Wikipedia entities?
+In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
+While it would be more interesting to annotate each single tweet with relevant entities, tweets are too short to contain much relevant information which could be used as input for the annotation tool.
+Thus, we chose to generate annotations for the whole search result.
 
-Need context/signal to feed wikifier \cite{key:wikifier}.
+The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics.
+Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
+
+Annotations should be stable over time, unless the topics discussed in the tweets containing the search term change.
+In nan evaluation of our approach we have tried to analyse the stability of the result.
+
+The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation
 
 \section{Method Overview}
+\label{sect:method}
 
-System Architecture shown in Figure \ref{fig:arch}.
+The implemented
+system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
+(further called Twitter Search Wrapper) is called with a query and returns a
+rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
+twitter posts (further called tweets) matching the given query. The returned rdf
+document furthermore contains a mapping of the query to Encyclopedia articles
+which based on the content published by users that most recently used the query
+in their posts maps to articles best describing the content of tweets related to
+the query. An overview of the System Architecture is given in Figure
+\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
+Search Wrapper can be grouped into five sequential steps (see Figure
+\ref{fig:arch}) .
+>>>>>>> .r181
 
@@
 
+In a first step the Twitter Search Wrapper fetches the atom feed
+generated by the twitter search
+api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
+query. The generated feed contains information about the 100 most recently published publicly visible tweets and
+their authors which match the search query. The tweets itself are described by
+their content, publishing date, authors and optionally a geographic location.
+
+In a second (optional) step hyperlinks posted in tweets of the fetched
+feed are followed, content of the referenced website's body is fetched and
+processed to the Wrapper. This option is triggered calling the Wrapper
+service with attribute extern=true.
+
+The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
+tweets that matched the search query and optional content of their referenced websites is merged
+to a single input string which is used as input for the Wikifier. The service
+returns a list of matching articles of the English
+Wikipedia. Optionally the wrapper can be initially called with lang=de to
+trigger mapping to the German Wikipedia.
+
+The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
+generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
+describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
+DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
+Wikifier) describing the documents content.
+
 \section{Experiments and Evaluation}
+\label{sect:eval}
 
@@
 \centering
-\begin{tabular}{ l }
+\begin{tabular}{ c }
 Search term                    \\

### 2011-02-22 lids/twittersearchwrap/paper/paper.tex

@@
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms
+These entities will not only help to understand the search terms, but also serve as a starting point when searching for further information related to the search result.
+This also helps to determine what the meaning of cryptic hash tags such as $\#s21$ or $\#ka$ mean.
 
-Why need Wikipedia entities?
+In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
+While it would be more interesting to annotate each single tweet with relevant entities, tweets are too short to contain much relevant information which could be used as input for the annotation tool.
+Thus, we chose to generate annotations for the whole search result.
 
-Need context/signal to feed wikifier \cite{key:wikifier}.
+The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics.
+Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
+
+Annotations should be stable over time, unless the topics discussed in the tweets containing the search term change.
+In nan evaluation of our approach we have tried to analyse the stability of the result.
+
+The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation
 
 \section{Method Overview}
+\label{sect:method}
 
@@
 \section{Experiments and Evaluation}
+\label{sect:eval}
 
@@
 
-%\begin{table}[ht*]
-%\centering
-%\begin{tabular}{ 1 }
-%Search term                    \\
-%\hline
-%\#s21 \\
-%Karlsruhe\\
-%\end{tabular}
-%\caption{Search terms}\label{tbl:terms}
-%\end{table}
+\begin{table}[ht*]
+\centering
+\begin{tabular}{ c }
+Search term                    \\
+\hline
+\#s21 \\
+Karlsruhe\\
+\end{tabular}
+\caption{Search terms}\label{tbl:terms}
+\end{table}
 

### 2011-02-22 lids/twittersearchwrap/paper/paper.tex

@@
 (further called Twitter Search Wrapper) is called with a query and returns a
-rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
-twitter posts (further called tweets) matching the given query. The returned rdf
+rdf\footnote{\url{http://www.w3.org/RDF/}} document semantically describing the
+most recent twitter posts (further called tweets) matching the given query. The returned rdf
 document furthermore contains a mapping of the query to Encyclopedia articles
@@
 feed are followed, content of the referenced website's body is fetched and
-processed to the Wrapper. This option is triggered calling the Wrapper
-service with attribute extern=true.
+processed to the Wrapper. This option is triggered calling the Twitter Search
+Wrapper with attribute extern=true.
 
@@
 The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
-generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
+generates a rdf document using popular ontologies (foaf, dublincore, geo) to
 describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to

### 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
-(further called Twitter Search Wrapper) is called with a query and returns a
-rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
-twitter posts (further called tweets) matching the given query. The returned rdf
+(further called Twitter Search Wrapper) is called with a query representing
+the twitter search term and returns a rdf\footnote{\url{http://www.w3.org/RDF/}}
+document semantically describing the most recent twitter posts (further called tweets) matching the given query. The returned rdf
 document furthermore contains a mapping of the query to Encyclopedia articles
-which based on the content published by users that most recently used the query
-in their posts maps to articles best describing the content of tweets related to
-the query. An overview of the System Architecture is given in Figure
+which based on the content published by users that most recently used the search
+term in their posts maps to articles best describing the content of tweets
+related to the term. An overview of the System Architecture is given in Figure
 \ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
@@
 \ref{fig:arch}) .
->>>>>>> .r181
 
@@
 In a first step the Twitter Search Wrapper fetches the atom feed
-generated by the twitter search
-api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
-query. The generated feed contains information about the 100 most recently published publicly visible tweets and
-their authors which match the search query. The tweets itself are described by
+generated by the Twitter Search
+API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
+query. The generated feed contains the data of the 100 most recently published
+publicly visible tweets and their authors which match the search query. The tweets itself are described by
 their content, publishing date, authors and optionally a geographic location.
@@
 feed are followed, content of the referenced website's body is fetched and
-processed to the Wrapper. This option is triggered calling the Wrapper
-service with attribute extern=true.
+processed to the Wrapper. This option is triggered calling the Twitter Search
+Wrapper with attribute extern=true.
 
-The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
-tweets that matched the search query and optional content of their referenced websites is merged
+The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
+the tweets that matched the search query and optional content of their referenced websites is merged
 to a single input string which is used as input for the Wikifier. The service
 returns a list of matching articles of the English
-Wikipedia. Optionally the wrapper can be initially called with lang=de to
-trigger mapping to the German Wikipedia.
+Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
+to trigger mapping to the German Wikipedia.
 
-The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
-generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
-describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
+The list of matching Wikipedia articles is finally returned to the Wrapper. The
+Wrapper generates a rdf document using popular ontologies (foaf, dublincore, geo) to
+describe the data related to the returned tweets and their content using
+'rdfs:seeAlso' triples to link the document to
 DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
-Wikifier) describing the documents content.
+Wikifier) that have been mapped to the documents content.
 

### 2011-02-22 lids/twittersearchwrap/paper/paper.tex
added keywords

@@
 
+Keywords: Twitter, Wikipedia, DBpedia, RDF
+
 \section{Introduction}
@@
 system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
-(further called Twitter Search Wrapper) is called with a query and returns a
-rdf\footnote{\url{http://www.w3.org/RDF/}} document semantically describing the
-most recent twitter posts (further called tweets) matching the given query. The returned rdf
+(further called Twitter Search Wrapper) is called with a query representing
+the twitter search term and returns a rdf\footnote{\url{http://www.w3.org/RDF/}}
+document semantically describing the most recent twitter posts (further called tweets) matching the given query. The returned rdf
 document furthermore contains a mapping of the query to Encyclopedia articles
-which based on the content published by users that most recently used the query
-in their posts maps to articles best describing the content of tweets related to
-the query. An overview of the System Architecture is given in Figure
+which based on the content published by users that most recently used the search
+term in their posts maps to articles best describing the content of tweets
+related to the term. An overview of the System Architecture is given in Figure
 \ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
@@
 
+% 1. Schicke Suchanfrage an Twitter Search API
+% Ich würde etwas ausführlicher erklären, was die Twitter Search API macht (an welcher Stelle im Paper müsste man nochmal überlegen).
+% 2. Greife Ergebnisse ab
+
 In a first step the Twitter Search Wrapper fetches the atom feed
-generated by the twitter search
-api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
-query. The generated feed contains information about the 100 most recently published publicly visible tweets and
-their authors which match the search query. The tweets itself are described by
+generated by the Twitter Search
+API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
+query. The generated feed contains the data of the 100 most recently published
+publicly visible tweets and their authors which match the search query. The tweets themselves are described by
 their content, publishing date, authors and optionally a geographic location.
+
+%Sind das XML-Daten oder wie werden die beschrieben?
 
@@
 
-The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
-tweets that matched the search query and optional content of their referenced websites is merged
+The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
+the tweets that matched the search query and optional content of their referenced websites is merged
 to a single input string which is used as input for the Wikifier. The service
 returns a list of matching articles of the English
-Wikipedia. Optionally the wrapper can be initially called with lang=de to
-trigger mapping to the German Wikipedia.
+Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
+to trigger mapping to the German Wikipedia.
 
-The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
-generates a rdf document using popular ontologies (foaf, dublincore, geo) to
-describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
+%Vielleicht kurzes Bsp.
+oder so?
+Problem ist, dass ich, glaube ich, nicht verstanden hätte, was gemacht wird, wenn ich es nicht wüsste.
+Oder einfach etwas  ausführlicher beschreiben, wie der Inputstring generiert wird.
+
+The list of matching Wikipedia articles is finally returned to the Wrapper. The
+Wrapper generates a rdf document using popular ontologies (foaf, dublincore, geo) to
+describe the data related to the returned tweets and their content using
+'rdfs:seeAlso' triples to link the document to
 DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
-Wikifier) describing the documents content.
+Wikifier) that have been mapped to the documents content.
+
+%Ausgabe würde ich ausführlicher beschreiben. Wie wird ein Tweet dargestellt? Wie kommen die Wikipediaentitäten rein? Welche Typen und Relationen werden wofür verwendet?
 

### 2011-02-22 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Changes in retrieval from external data

@@ -167,13 +167,18 @@ public class SearchServlet extends HttpServlet {
 								HTTPRequest request = new HTTPRequest(new URL(urls[i]), HTTPMethod.GET, Builder.allowTruncate());
 								URLFetchService service = URLFetchServiceFactory.getURLFetchService();
 								response = service.fetch(request);
-								List<HTTPHeader> responseHeaders = response.getHeaders();
-								HTTPHeader responseHeader = responseHeaders.get(7);
-								encoded = responseHeader.getValue().split("charset=")[1];
+								try {
+									List<HTTPHeader> responseHeaders = response.getHeaders();
+									HTTPHeader responseHeader = responseHeaders.get(7);
+									encoded = responseHeader.getValue().split("charset=")[1];
+								} catch (Exception e) {
+//									System.out.println("CHARSET not retrievable at " + urls[i]);
+//									System.out.println("CHARSET assuming utf-8");
+								}
 								content = response.getContent();
 							} catch (Exception e) {
-//								System.out.println("ERROR connecting to " + urls[i]);
-//								timeout = true;
+								System.out.println("ERROR connecting to " + urls[i]);
+								timeout = true;
 							}
 							
 							if (!timeout && response!=null && content!=null){
@@ -186,8 +191,10 @@ public class SearchServlet extends HttpServlet {
 								String lines = null;
 								Boolean contained1 = false;
 								Boolean contained2 = false;
-								while ((lines = reader.readLine()) != null && words.size()<50) {
-								StringTokenizer st = new StringTokenizer(lines.toString().replaceAll("\\<.*?\\>", ""));
+								while ((lines = reader.readLine()) != null && words.size()<100) {
+								String thisline = lines.replaceAll("\\<.*?\\>", "");
+								thisline = lines.replaceAll("<.*?>", "");
+								StringTokenizer st = new StringTokenizer(thisline);
 								if(contained1 && lines.toLowerCase().contains(("<\\body>"))){
 									contained2 = true;
 								}
@@ -195,7 +202,7 @@ public class SearchServlet extends HttpServlet {
 									contained1 = true;
 								}
 								if(contained1 && !contained2){
-									while (st.hasMoreTokens() && words.size()<50) {
+									while (st.hasMoreTokens() && words.size()<100) {
 										  String tok = st.nextToken();
 										  words.add(tok);
 									}
[…]

### 2011-02-22 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -18,7 +18,7 @@ public class Wikify {
 	
 	public static String cleanTweets (String input){
 	   input = input.replaceAll("http://.*?\\s", "");
-	   input = input.replaceAll("<.*?>", "");
+	   //input = input.replaceAll("<.*?>", "");
        return input;
 	}
 

### 2011-02-22 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
HTML Conversion finally working almost properly

@@ -2,10 +2,12 @@ package com.ontologycentral.twittersearchwrap;
 
 import java.io.BufferedReader;
 import java.io.ByteArrayInputStream;
+import java.io.ByteArrayOutputStream;
 import java.io.IOException;
 import java.io.InputStream;
 import java.io.InputStreamReader;
 import java.io.OutputStream;
+import java.io.Reader;
 import java.io.StringReader;
 import java.net.HttpURLConnection;
 import java.net.URL;
@@ -28,6 +30,13 @@ import javax.xml.transform.Transformer;
 import javax.xml.transform.TransformerException;
 import javax.xml.transform.stream.StreamResult;
 import javax.xml.transform.stream.StreamSource;
+
+import org.apache.xerces.xni.parser.XMLDocumentFilter;
+import org.apache.xerces.xni.parser.XMLInputSource;
+import org.apache.xerces.xni.parser.XMLParserConfiguration;
+import org.cyberneko.html.HTMLConfiguration;
+import org.cyberneko.html.filters.ElementRemover;
+import org.cyberneko.html.filters.Writer;
 
 import com.google.appengine.api.urlfetch.FetchOptions.Builder;
 import com.google.appengine.api.urlfetch.HTTPHeader;
@@ -161,7 +170,7 @@ public class SearchServlet extends HttpServlet {
 							HTTPResponse response = null;
 							Boolean timeout = false;
 							byte[] content = null;
-							String encoded = "utf-8";
+							String encoded = "UTF-8";
 							
 							try {
 								HTTPRequest request = new HTTPRequest(new URL(urls[i]), HTTPMethod.GET, Builder.allowTruncate());
@@ -181,32 +190,46 @@ public class SearchServlet extends HttpServlet {
 								timeout = true;
 							}
 							
+							
+							// create element remover filter
+							ElementRemover remover;
+							remover = new ElementRemover();
+							remover.removeElement("script");
+							remover.removeElement("link");
+							remover.removeElement("style");
+							remover.removeElement("CDATA");
+							remover.removeElement("<!--");
+							remover.removeElement("meta");
+							
 							if (!timeout && response!=null && content!=null){
 							if (response.getResponseCode() == 200){
 								System.out.println("EXTERNAL URL: " + urls[i]);
 								ByteArrayInputStream bais = new ByteArrayInputStream(content);
-								BufferedReader reader = new BufferedReader(new InputStreamReader(bais, encoded));								
[…]

### 2011-02-22 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -215,8 +215,9 @@ public class SearchServlet extends HttpServlet {
 //								Boolean contained2 = false;
 								while ((lines = reader.readLine()) != null && words.size()<50) {
 								String thisline = lines.replaceAll("\\<.*?\\>", "");
-								thisline = thisline.replaceAll("<.*?>", "");
-//								thisline = thisline.replaceAll("(.*?)", "");
+								thisline = thisline.replaceAll("\\(.*?\\)", "");
+								thisline = thisline.replaceAll("\\{.*?\\}", "");
+								thisline = thisline.replaceAll("\\s+", " ");
 								StringTokenizer st = new StringTokenizer(thisline);
 //								if(contained1 && lines.toLowerCase().contains(("<\\body>"))){
 //									contained2 = true;
@@ -243,9 +244,8 @@ public class SearchServlet extends HttpServlet {
 							}
 						}
 					}
-					// Remove multiple whitespaces and add to string containing tweets
-					System.out.println(externalWebsites.toString().replaceAll("\\s+", " "));
-					tweets.append(externalWebsites.toString().replaceAll("\\s+", " "));
+					// Append external content to tweet content
+					tweets.append(externalWebsites.toString());
 				}
 				Set<String> wikifyResult = Wikify.startWikify(tweets.toString(),lang);
 				System.out.println("WIKIFY RESULTS:");

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex

@@
 
-\title{Mapping Microblogging Posts to Encyclopedia Articles}
+\title{Mapping Microblog Posts to Encyclopedia Articles}
 \author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
@@
 The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million tweets a day.
-Thus, Twitter represents a huge data source on the web.
+Twitter has a total of about 190 million of users who produce 65 million twitter messages a day.
+Thus, twitter represents a huge data source on the web.
 
-Twitter offers the possibility to search for tweets containing a specific term or hash tags.
-This search returns a fixed number of most recent tweets containing the search term.
-However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for.
-As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+Twitter offers the possibility to search for twitter messages containing a specific term or hash tags.
+This search returns a fixed number of most recent messages containing the search term.
+However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
+As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms, but also serve as a starting point when searching for further information related to the search result.
-This also helps to determine what the meaning of cryptic hash tags such as $\#s21$ or $\#ka$ mean.
+These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+
+On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or evecnt.
+For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will probably be tagged with $\#eswc2011$.
+If a user encounters this hash tag and does not understand it, he can search for this hash tag.
+Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
+These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
 
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
-While it would be more interesting to annotate each single tweet with relevant entities, tweets are too short to contain much relevant information which could be used as input for the annotation tool.
+While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
 Thus, we chose to generate annotations for the whole search result.
@@
 
-Annotations should be stable over time, unless the topics discussed in the tweets containing the search term change.
-In nan evaluation of our approach we have tried to analyse the stability of the result.
+Annotations should be stable over time, unless the topics discussed in the twitter messages containing the search term change.
+In an evaluation of our approach we have tried to analyze the stability of the result.
 
-The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation
+Our contributions thus are:
+\begin{itemize}
+	\item an approach for finding entities which are related to a search on twitter
+	\item an implementation of our approach
+	\item an evaluation of the stability and relevance of the entities found with our approach.
+\end{itemize}
+
+The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation, we are dealing with Related Work in Section~\ref{sect:relWork}, before we conclude in Section~\ref{sect:conclusion}.
 
@@
 the twitter search term and returns a rdf\footnote{\url{http://www.w3.org/RDF/}}
-document semantically describing the most recent twitter posts (further called tweets) matching the given query. The returned rdf
+document semantically describing the most recent twitter posts (further called twitter messages) matching the given query. The returned rdf
 document furthermore contains a mapping of the query to Encyclopedia articles
 which based on the content published by users that most recently used the search
-term in their posts maps to articles best describing the content of tweets
+term in their posts maps to articles best describing the content of twitter messages
 related to the term. An overview of the System Architecture is given in Figure
@@
 query. The generated feed contains the data of the 100 most recently published
-publicly visible tweets and their authors which match the search query. The tweets themselves are described by
+publicly visible twitter messages and their authors which match the search query. The twitter messages themselves are described by
 their content, publishing date, authors and optionally a geographic location.
@@
 
-In a second (optional) step hyperlinks posted in tweets of the fetched
+In a second (optional) step hyperlinks posted in twitter messages of the fetched
 feed are followed, content of the referenced website's body is fetched and
@@
 The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
-the tweets that matched the search query and optional content of their referenced websites is merged
+the twitter messages that matched the search query and optional content of their referenced websites is merged
 to a single input string which is used as input for the Wikifier. The service
@@
 Wrapper generates a rdf document using popular ontologies (foaf, dublincore, geo) to
-describe the data related to the returned tweets and their content using
+describe the data related to the returned twitter messages and their content using
 'rdfs:seeAlso' triples to link the document to
@@
 \section{Related Work}
+\label{sect:relWork}
 
@@
 It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
+
 \section{Conclusion}
+\label{sect:conclusion}
 

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex

@@
 
-The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation, we are dealing with Related Work in Section~\ref{sect:relWork}, before we conclude in Section~\ref{sect:conclusion}.
+The rest of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
+
+\section{Related Work}
+\label{sect:relWork}
+
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before: Passant et al.
+\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hash tags.
+The idea is to use URIs as hash tags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
+
+A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
+%System beschreiben
 
@@
 
-\section{Related Work}
-\label{sect:relWork}
-
-Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before.
-
-Passant et al. \cite{key:smob} have proposed a data model for making twitter
-data available on the Semantic Web.
-They propose a data model which allows for the association of URIs with users, microblogs and microposts.
-To this end, SIOC and FOAF vocabularies are used and extended.
-Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
-Additionally, they propose the use of so-called semantic hash tags.
-The idea is to use URIs as hash tags (e.g.
-\emph{\#geo:Paris\_France}).
-It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
-
 \section{Conclusion}

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex

@@
 These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
-
+% Konzept von Hashtags genauer erklären? Warum sind Hashtags sinnvoll?
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
@@
 The implemented
-system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
-(further called Twitter Search Wrapper) is called with a query representing
-the twitter search term and returns a rdf\footnote{\url{http://www.w3.org/RDF/}}
-document semantically describing the most recent twitter posts (further called twitter messages) matching the given query. The returned rdf
-document furthermore contains a mapping of the query to Encyclopedia articles
-which based on the content published by users that most recently used the search
-term in their posts maps to articles best describing the content of twitter messages
-related to the term. An overview of the System Architecture is given in Figure
-\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
-Search Wrapper can be grouped into five sequential steps (see Figure
-\ref{fig:arch}) .
+system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
+the twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
+document semantically describing the most recent twitter posts matching the
+given query. The returned RDF document furthermore contains a mapping of the
+query to Encyclopedia articles which based on the content published by users that most recently used the search
+term in their posts maps to articles best describing the content of Twitter
+messages related to the term. An overview of the System Architecture is given in Figure
+\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
+Twitter Search Wrapper can be grouped into five sequential steps (see Figure
+\ref{fig:arch}). We will follow those steps along a simple example, using
+\#ka (a hashtag frequently used to describe posts related to the city of
+Karlsruhe, Germany) as search term for the Twitter Search wrapper.
 
@@
 
-In a first step the Twitter Search Wrapper fetches the atom feed
+\begin{enumerate}
+  \item 
+In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
 generated by the Twitter Search
-API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
-query. The generated feed contains the data of the 100 most recently published
-publicly visible twitter messages and their authors which match the search query. The twitter messages themselves are described by
-their content, publishing date, authors and optionally a geographic location.
-
-%Sind das XML-Daten oder wie werden die beschrieben?
-
-In a second (optional) step hyperlinks posted in twitter messages of the fetched
+API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
+search query. The generated feed contains the data of the 100 most recently published
+publicly visible Twitter messages and their authors which match the search query.
+The messages themselves are described by their content, publishing date, authors
+and optionally a geographic location.\linebreak\linebreak
+In the given example, calling the Wrapper with query '\#ka' will return a
+document containing all most recent Twitter posts and their meta information
+whose content matched the search string '\#ka'. Taking a closer look, a single
+retrieved post might have the following content: \newline\linebreak 
+\texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
+\linebreak
+\item
+In a second (optional) step hyperlinks posted in messages of the fetched
 feed are followed, content of the referenced website's body is fetched and
 processed to the Wrapper. This option is triggered calling the Twitter Search
-Wrapper with attribute extern=true.
-
+Wrapper with attribute extern=true.\newline
+\linebreak
+Following the initial example, the given sample post contained a link to
+\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
+text:\newline
+\linebreak
+''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+south-west of Germany,\newline famed for its fan-shaped historic street plan,
+where margraves reigned in times past,\newline and German joie de vivre reigns
+today.}''\newline\linebreak
+The text is fetched and returned to the Wrapper. The same accounts for
+content of all other websites that were referenced in the list of posts matching
+the query \#ka.\newline
+\item
 The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
-the twitter messages that matched the search query and optional content of their referenced websites is merged
-to a single input string which is used as input for the Wikifier. The service
+the Twitter messages that matched the search query and optional content of their
+referenced websites is merged to a single input string which is used as input for the Wikifier. The service
 returns a list of matching articles of the English
 Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
-to trigger mapping to the German Wikipedia.
-
-%Vielleicht kurzes Bsp.
-oder so?
-Problem ist, dass ich, glaube ich, nicht verstanden hätte, was gemacht wird, wenn ich es nicht wüsste.
-Oder einfach etwas  ausführlicher beschreiben, wie der Inputstring generiert wird.
-
-The list of matching Wikipedia articles is finally returned to the Wrapper. The
-Wrapper generates a rdf document using popular ontologies (foaf, dublincore, geo) to
-describe the data related to the returned twitter messages and their content using
-'rdfs:seeAlso' triples to link the document to
-DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
-Wikifier) that have been mapped to the documents content.
-
-%Ausgabe würde ich ausführlicher beschreiben. Wie wird ein Tweet dargestellt? Wie kommen die Wikipediaentitäten rein? Welche Typen und Relationen werden wofür verwendet?
+to trigger mapping to the German Wikipedia.\newline\linebreak
+In the given example, content of all posts related to the search term '\#ka' is
+merged with retrieved external website content. Taking a closer look at the
+single post we merge its content and content of its referenced website to
+a single string:\newline\linebreak
+\texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
+where paths converge - a legendary city in the sunny\newline south-west of
+Germany, famed for its fan-shaped historic street plan, where margraves\newline
+reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
+This string is appended to Twitter content and external content of all other
+posts that have been retrieved in this way matching the initial query \#ka and
+used as input for the Wikifier.\newline
+  \item
+The Wikifier now maps the input string to relevant Wikipedia articles. A
+detailed description of this process can be found under \cite{key:wikifier}. 
+The list of matching Wikipedia articles is finally returned to the
+Wrapper.\newline\linebreak
+In the given example, a desired mapping of the contents of posts related to the
+hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
+mapping to Wikipedia articles describing content related to Karlsruhe. We just
+assume this results in mappings to the articles for Karlsruhe, Germany and the
+Karlsruhe\_Institute\_of\_Technology.\newline
+  \item
+The Wrapper finally generates a RDF document using popular ontologies
+(foaf\footnote{http://xmlns.com/foaf/spec/},
+dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
+returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
+the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
+output of the Wikifier) that have been mapped to the documents content.
+At this point DBPedia is chosen as referenced encyclopedia, because its
+semantic nature and description of Wikipedia article content contributes to a
+coherent semantic description. \newline\linebreak Coming back to the example,
+the output RDF document containes the following triples to reference the DBPedia
+mappings:\newline\linebreak \texttt{<rdfs:seeAlso
+rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+\texttt{<rdfs:seeAlso
+rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
+The twitter posts matching the search term \#ka are all described in the output
+document. As an example, the description for the initially given post might
+result in the following RDF output:\newline\linebreak
+\texttt{<rdf:Description
+rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+show/1234567890\#id">\newline <foaf:page
+rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+<foaf:maker
+rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+</dc:description>\newline
+</rdf:Description>\newline}
+\end{enumerate}
 

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex

@@
 system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
-the twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
-document semantically describing the most recent twitter posts matching the
+the Twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
+document semantically describing the most recent Twitter messages matching the
 given query. The returned RDF document furthermore contains a mapping of the
@@
 \end{figure}
-
-% 1. Schicke Suchanfrage an Twitter Search API
-% Ich würde etwas ausführlicher erklären, was die Twitter Search API macht (an welcher Stelle im Paper müsste man nochmal überlegen).
-% 2. Greife Ergebnisse ab
 
@@
 coherent semantic description. \newline\linebreak Coming back to the example,
-the output RDF document containes the following triples to reference the DBPedia
-mappings:\newline\linebreak \texttt{<rdfs:seeAlso
+the output RDF document containes the following triples to reference the
+DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
 rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline

### 2011-02-23 trunk/lids/twittersearchwrap/paper/paper.tex

--- 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex
@@
 
-\newcommand{\nop}[1]{}
+%\newcommand{\nop}[1]{}
 
-\title{Mapping Microblogging Posts to Encyclopedia Articles}
+\title{Mapping Microblog Posts to Encyclopedia Articles}
 \author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
@@
 \begin{abstract}
-We describe a method to map Twitter posts to Wikipedia articles.
+Search results on Twitter are hard to analyze and read.
+To facilitate understanding the meaning of a search term in the context of Twitter, we have developed a system which annotates search results with entities that best describe the search result, thus offering a means of quickly grasping the meaning of the search results and at the same time providing starting points for further exploration of the search results' context.
+In an evaluation we show that the entities used for annotation represent the tweet's content in a suitable manner and that the annotations remain stable over time, i.e.
+when executing the same search at different times, the same entities are returned.
 \end{abstract}
+
+Keywords: Twitter, Wikipedia, DBpedia, RDF
 
@@
 The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million tweets a day.
-Thus, Twitter represents a huge data source on the web.
+Twitter has a total of about 190 million of users who produce 65 million twitter messages a day.
+Thus, twitter represents a huge data source on the web.
 
-Twitter offers the possibility to search for tweets containing a specific term or hash tags.
-This search returns a fixed number of most recent tweets containing the search term.
-However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for.
-As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+Twitter offers the possibility to search for twitter messages containing a specific term or hash tags.
+This search returns a fixed number of most recent messages containing the search term.
+However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
+As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms
+These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
 
-Why need Wikipedia entities?
+On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or evecnt.
+For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will probably be tagged with $\#eswc2011$.
+If a user encounters this hash tag and does not understand it, he can search for this hash tag.
+Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
+These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
+% Konzept von Hashtags genauer erklären? Warum sind Hashtags sinnvoll?
+In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
+While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
+Thus, we chose to generate annotations for the whole search result.
 
-Need context/signal to feed wikifier \cite{key:wikifier}.
+The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics.
+Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
+
+Annotations should be stable over time, unless the topics discussed in the twitter messages containing the search term change.
+In an evaluation of our approach we have tried to analyze the stability of the result.
+
+Our contributions thus are:
+\begin{itemize}
+	\item an approach for finding entities which are related to a search on twitter
+	\item an implementation of our approach
+	\item an evaluation of the stability and relevance of the entities found with our approach.
+\end{itemize}
+
+The rest of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
+
+\section{Related Work}
+\label{sect:relWork}
+
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before: Passant et al.
+\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hash tags.
+The idea is to use URIs as hash tags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
+
+A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
+%System beschreiben
 
 \section{Method Overview}
+\label{sect:method}
 
-The implemented system (further called twitter search wrapper) is called with
-a query and returns a rdf\footnote{\url{http://www.w3.org/RDF/}} document
-describing the most recent twitter posts (further called tweets) matching the
-given query. The returned rdf document furthermore contains a mapping of the
-query to Wikipedia articles which based on the content published by users that most recently used the query in their
-posts maps to articles best describing the content of tweets related to the
-query. An overview of the System Architecture is given in Figure \ref{fig:arch}.
-In detail, methods performed by the twitter search wrapper can be grouped
-and best described in five sequential steps (see Figure \ref{fig:arch}) .
+The implemented
+system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
+the Twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
+document semantically describing the most recent Twitter messages matching the
+given query. The returned RDF document furthermore contains a mapping of the
+query to Encyclopedia articles which based on the content published by users that most recently used the search
+term in their posts maps to articles best describing the content of Twitter
+messages related to the term. An overview of the System Architecture is given in Figure
+\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
+Twitter Search Wrapper can be grouped into five sequential steps (see Figure
+\ref{fig:arch}). We will follow those steps along a simple example, using
+\#ka (a hashtag frequently used to describe posts related to the city of
+Karlsruhe, Germany) as search term for the Twitter Search wrapper.
 
@@
 
-In a first step the implemented twitter search wrapper fetches the atom feed
-generated by the twitter search
-api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
-query. The generated feed contains information about the 100 most recently published publicly visible tweets and
-their authors which match the search query. The tweets itself are described by
-their content, publishing date, authors and optionally a geographic location.
+\begin{enumerate}
+  \item 
+In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
+generated by the Twitter Search
+API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
+search query. The generated feed contains the data of the 100 most recently published
+publicly visible Twitter messages and their authors which match the search query.
+The messages themselves are described by their content, publishing date, authors
+and optionally a geographic location.\linebreak\linebreak
+In the given example, calling the Wrapper with query '\#ka' will return a
+document containing all most recent Twitter posts and their meta information
+whose content matched the search string '\#ka'. Taking a closer look, a single
+retrieved post might have the following content: \newline\linebreak 
+\texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
+\linebreak
+\item
+In a second (optional) step hyperlinks posted in messages of the fetched
+feed are followed, content of the referenced website's body is fetched and
+processed to the Wrapper. This option is triggered calling the Twitter Search
+Wrapper with attribute extern=true.\newline
+\linebreak
+Following the initial example, the given sample post contained a link to
+\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
+text:\newline
+\linebreak
+''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+south-west of Germany,\newline famed for its fan-shaped historic street plan,
+where margraves reigned in times past,\newline and German joie de vivre reigns
+today.}''\newline\linebreak
+The text is fetched and returned to the Wrapper. The same accounts for
+content of all other websites that were referenced in the list of posts matching
+the query \#ka.\newline
+\item
+The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
+the Twitter messages that matched the search query and optional content of their
+referenced websites is merged to a single input string which is used as input for the Wikifier. The service
+returns a list of matching articles of the English
+Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
+to trigger mapping to the German Wikipedia.\newline\linebreak
+In the given example, content of all posts related to the search term '\#ka' is
+merged with retrieved external website content. Taking a closer look at the
+single post we merge its content and content of its referenced website to
+a single string:\newline\linebreak
+\texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
+where paths converge - a legendary city in the sunny\newline south-west of
+Germany, famed for its fan-shaped historic street plan, where margraves\newline
+reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
+This string is appended to Twitter content and external content of all other
+posts that have been retrieved in this way matching the initial query \#ka and
+used as input for the Wikifier.\newline
+  \item
+The Wikifier now maps the input string to relevant Wikipedia articles. A
+detailed description of this process can be found under \cite{key:wikifier}. 
+The list of matching Wikipedia articles is finally returned to the
+Wrapper.\newline\linebreak
+In the given example, a desired mapping of the contents of posts related to the
+hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
+mapping to Wikipedia articles describing content related to Karlsruhe. We just
+assume this results in mappings to the articles for Karlsruhe, Germany and the
+Karlsruhe\_Institute\_of\_Technology.\newline
+  \item
+The Wrapper finally generates a RDF document using popular ontologies
+(foaf\footnote{http://xmlns.com/foaf/spec/},
+dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
+returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
+the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
+output of the Wikifier) that have been mapped to the documents content.
+At this point DBPedia is chosen as referenced encyclopedia, because its
+semantic nature and description of Wikipedia article content contributes to a
+coherent semantic description in the RDF document. \newline\linebreak Coming
+back to the example, the output RDF document contains the following triples to reference the
+DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
+rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+\texttt{<rdfs:seeAlso
+rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
+The twitter posts matching the search term \#ka are all described in the output
+document. As an example, the description for the initially given post might
+result in the following RDF output:\newline\linebreak
+\texttt{<rdf:Description
+rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+show/1234567890\#id">\newline <foaf:page
+rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+<foaf:maker
+rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+</dc:description>\newline
+</rdf:Description>\newline}
+\end{enumerate}
 
 \section{Experiments and Evaluation}
+\label{sect:eval}
 
@@
 
-\section{Related Work}
-
-Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before.
-
-Passant et al. \cite{key:smob} have proposed a data model for making twitter
-data available on the Semantic Web.
-They propose a data model which allows for the association of URIs with users, microblogs and microposts.
-To this end, SIOC and FOAF vocabularies are used and extended.
-Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
-Additionally, they propose the use of so-called semantic hash tags.
-The idea is to use URIs as hash tags (e.g.
-\emph{\#geo:Paris\_France}).
-It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
 \section{Conclusion}
+\label{sect:conclusion}
 

### 2011-02-23 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -18,7 +18,13 @@ public class Wikify {
 	
 	public static String cleanTweets (String input){
 	   input = input.replaceAll("http://.*?\\s", "");
-	   //input = input.replaceAll("<.*?>", "");
+	   input = input.trim();
+	   input = input.replaceAll("\\r|\\n", "");
+	   input = input.replaceAll("\\\\", "");
+	   input = input.replace("/", "");
+	   input = input.replace(";", "");
+	   input = input.replace("<", "");
+	   input = input.replace(">", "");
        return input;
 	}
 
@@ -32,15 +38,23 @@ public class Wikify {
 	    Wikifier w = new Wikifier(uri, "david's bot");
 	    
 	    input = cleanTweets(input);
-		//System.out.println("WIKIFIER Input:");
-		//System.out.println(input);
+
+//	    System.out.println("WIKIFY Input:");
+//		System.out.println(input);
 	    Node[] nx = new Node[] { DC.TITLE, new Literal(input) } ;
 			               
 		Set<Node[]> set = new HashSet<Node[]>();
 		set.add(nx);
 			    
+		Set<String> ret = null;
+	
+		try {
+			ret = w.wikify(new Resource("http://example.org/"), set);
+		} catch (Exception e) {
+			e.printStackTrace();
+		}
 		
-		return w.wikify(new Resource("http://example.org/"), set);
+		return ret;
 	}
 	
 }

### 2011-02-23 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -163,10 +163,9 @@ public class SearchServlet extends HttpServlet {
 					
 					// Get content of linked sites
 					for (int i = 0; i < urls.length; i++) {
-						
+
 						// Dont use internal twitter links containing javascript which cannot be handled
 						if(!urls[i].contains("twitter")){
-							
 							HTTPResponse response = null;
 							Boolean timeout = false;
 							byte[] content = null;
@@ -201,51 +200,49 @@ public class SearchServlet extends HttpServlet {
 							remover.removeElement("<!--");
 							remover.removeElement("meta");
 							
-							if (!timeout && response!=null && content!=null){
-							if (response.getResponseCode() == 200){
-								System.out.println("EXTERNAL URL: " + urls[i]);
-								ByteArrayInputStream bais = new ByteArrayInputStream(content);
-								BufferedReader firstreader = new BufferedReader(new InputStreamReader(bais, encoded));	
-								String readerstring = getHtmlFilteredString(firstreader);
-								BufferedReader reader = new BufferedReader(new StringReader(readerstring));
-								
-								List<String> words = new ArrayList<String>();
-								String lines = null;
-//								Boolean contained1 = false;
-//								Boolean contained2 = false;
-								while ((lines = reader.readLine()) != null && words.size()<50) {
-								String thisline = lines.replaceAll("\\<.*?\\>", "");
-								thisline = thisline.replaceAll("\\(.*?\\)", "");
-								thisline = thisline.replaceAll("\\{.*?\\}", "");
-								thisline = thisline.replaceAll("\\s+", " ");
-								StringTokenizer st = new StringTokenizer(thisline);
-//								if(contained1 && lines.toLowerCase().contains(("<\\body>"))){
-//									contained2 = true;
-//								}
-//								if(lines.toLowerCase().contains(("<body"))){
-//									contained1 = true;
-//								}
-//								if(contained1 && !contained2){
-									while (st.hasMoreTokens() && words.size()<50) {
-										  String tok = st.nextToken();
-										  words.add(tok);
-									}
-//								}
-								for (int j = 0; j < words.size(); j++) {
-									externalWebsites.append(words.get(j));
-									externalWebsites.append(" ");
-								}
-									
-								
-								}
 
-							    
-							}
+							if (!timeout && response != null && content != null) {
+								if (response.getResponseCode() == 200) {
+									System.out.println("EXTERNAL URL: "
+											+ urls[i]);
[…]

### 2011-02-23 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Removed Expires

@@ -275,9 +275,9 @@ public class SearchServlet extends HttpServlet {
 			Transformer t = (Transformer)ctx.getAttribute(Listener.T);
 
 			resp.setHeader("Cache-Control", "public");
-			Calendar c = Calendar.getInstance();
-			c.add(Calendar.DATE, 1);
-			resp.setHeader("Expires", RFC822.format(c.getTime()));
+//			Calendar c = Calendar.getInstance();
+//			c.add(Calendar.DATE, 1);
+//			resp.setHeader("Expires", RFC822.format(c.getTime()));
 
 			try {
 				    StreamSource ssource = new StreamSource(sr);

### 2011-02-23 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/Wikify.java

@@ -48,11 +48,9 @@ public class Wikify {
 			    
 		Set<String> ret = null;
 	
-		try {
-			ret = w.wikify(new Resource("http://example.org/"), set);
-		} catch (Exception e) {
-			e.printStackTrace();
-		}
+		
+		ret = w.wikify(new Resource("http://example.org/"), set);
+
 		
 		return ret;
 	}

### 2011-02-23 lids/twittersearchwrap/paper/paper.tex
added open issues in conclusion

@@
 semantic nature and description of Wikipedia article content contributes to a
-coherent semantic description. \newline\linebreak Coming back to the example,
-the output RDF document containes the following triples to reference the
+coherent semantic description in the RDF document. \newline\linebreak Coming
+back to the example, the output RDF document contains the following triples to reference the
 DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
@@
 
+@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka
+
+@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages
+
+@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
+
 \bibliographystyle{abbrv}

### 2011-02-24 lids/twittersearchwrap/paper/paper.tex

@@
 %\newcommand{\nop}[1]{}
+
+\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
 
@@
 Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
-The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters.
+The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of twitter the restriction is 140 characters.
 Twitter has a total of about 190 million of users who produce 65 million twitter messages a day.
@@
 
-Twitter offers the possibility to search for twitter messages containing a specific term or hash tags.
+On Twitter it is possible to search for messages containing a specific term or hash tag.
 This search returns a fixed number of most recent messages containing the search term.
@@
 
-On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or evecnt.
-For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will probably be tagged with $\#eswc2011$.
-If a user encounters this hash tag and does not understand it, he can search for this hash tag.
+On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or event.
+For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
+If a user encounters this hash tag and does not understand it, he can search for it on twitter.
 Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
 These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
-% Konzept von Hashtags genauer erklären? Warum sind Hashtags sinnvoll?
+
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
@@
 
-The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics.
+The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
 Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
@@
 
-Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before: Passant et al.
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
+
+The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
+Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
+
+Passant et al.
 \cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
@@
 To this end, SIOC and FOAF vocabularies are used and extended.
-Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
+Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced.
 Additionally, they propose the use of so-called semantic hash tags.
@@
 \emph{\#geo:Paris\_France}).
-It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
+It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.
+
+Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks.
+They have instantiated their system to analyze data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
 
 A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
-%System beschreiben
+%uhe: System beschreiben
 
@@
 
-The implemented
-system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
-the Twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
+The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/} document describing the search result, i.e.
+the most recent messages that match the query, the authors of these messages and the most relevant entities for this result.
+
+The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
+the Twitter search term and returns a RDF}
 document semantically describing the most recent Twitter messages matching the
@@
 
-\begin{definition}[Stability]
+The goal of our evaluation was to examine the stability of the entity annotations over time.
+To achieve this, we have repeatedly executed the same set of queries.
+\myremark{TODO}{How frequently?
+How long?
+Which queries?}
+In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains.
+We have then evaluated the results with respect to several measures:
 
+\begin{definition}[Evaluation Measures]
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with entities $E_1,\ldots,E_n$, we define:
+\begin{itemize}
+	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
+	\item The global stability of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{\bigcap_{i=1}^{n}E_i}{\bigcup_{i=1}^{n}E_i}$$
+	\item The stability for a single term is defined as the fraction of result sets in which it occurs: 
+$$st(t)=\frac{|\{i|t\in E_i\}|}{n}$$
+\end{itemize}
 \end{definition}

### 2011-02-24 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Exceptions bei Timeout

@@ -186,6 +186,7 @@ public class SearchServlet extends HttpServlet {
 								content = response.getContent();
 							} catch (Exception e) {
 								System.out.println("ERROR connecting to " + urls[i]);
+								e.printStackTrace();
 								timeout = true;
 							}
 							

### 2011-02-24 trunk/lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Google URLfetch Klassen durch Standard Java ersetzt

@@ -1,7 +1,6 @@
 package com.ontologycentral.twittersearchwrap;
 
 import java.io.BufferedReader;
-import java.io.ByteArrayInputStream;
 import java.io.ByteArrayOutputStream;
 import java.io.IOException;
 import java.io.InputStream;
@@ -14,7 +13,6 @@ import java.net.URL;
 import java.net.URLEncoder;
 import java.text.SimpleDateFormat;
 import java.util.ArrayList;
-import java.util.Calendar;
 import java.util.Iterator;
 import java.util.List;
 import java.util.Locale;
@@ -38,13 +36,6 @@ import org.cyberneko.html.HTMLConfiguration;
 import org.cyberneko.html.filters.ElementRemover;
 import org.cyberneko.html.filters.Writer;
 
-import com.google.appengine.api.urlfetch.FetchOptions.Builder;
-import com.google.appengine.api.urlfetch.HTTPHeader;
-import com.google.appengine.api.urlfetch.HTTPMethod;
-import com.google.appengine.api.urlfetch.HTTPRequest;
-import com.google.appengine.api.urlfetch.HTTPResponse;
-import com.google.appengine.api.urlfetch.URLFetchService;
-import com.google.appengine.api.urlfetch.URLFetchServiceFactory;
 
 @SuppressWarnings("serial")
 public class SearchServlet extends HttpServlet {
@@ -166,32 +157,37 @@ public class SearchServlet extends HttpServlet {
 
 						// Dont use internal twitter links containing javascript which cannot be handled
 						if(!urls[i].contains("twitter")){
-							HTTPResponse response = null;
-							Boolean timeout = false;
-							byte[] content = null;
-							String encoded = "UTF-8";
 							
+						    BufferedReader content = null;
+							String response = "";
+							String encoded = "UTF-8";
 							try {
-								HTTPRequest request = new HTTPRequest(new URL(urls[i]), HTTPMethod.GET, Builder.allowTruncate());
-								URLFetchService service = URLFetchServiceFactory.getURLFetchService();
-								response = service.fetch(request);
+								// Create the HttpURLConnection
+								URL url = new URL(urls[i]);
+								HttpURLConnection connection = (HttpURLConnection) url.openConnection();
+								content = null;
+								connection.setRequestMethod("GET");
+								connection.setReadTimeout(15*1000);
+								connection.connect();
+
+								// Read the output from the server
+								content = new BufferedReader(new InputStreamReader(connection.getInputStream()));
+								response = connection.getResponseMessage();
 								try {
[…]

### 2011-02-24 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java

@@ -13,6 +13,7 @@ import java.net.URL;
 import java.net.URLEncoder;
 import java.text.SimpleDateFormat;
 import java.util.ArrayList;
+import java.util.HashSet;
 import java.util.Iterator;
 import java.util.List;
 import java.util.Locale;
@@ -146,28 +147,36 @@ public class SearchServlet extends HttpServlet {
 					}
 					
 					String[] tweetsHTMLSplit = tweetsHTML.toString().split("&lt;a href=&quot;");
-					String[] urls = new String[tweetsHTMLSplit.length-1];
+					String[] urlarray = new String[tweetsHTMLSplit.length-1];
 					
 					for(int i = 1; i<tweetsHTMLSplit.length; i++){
-					    urls[i-1] = tweetsHTMLSplit[i].toString().split("&quot;&gt;")[0];
+					    urlarray[i-1] = tweetsHTMLSplit[i].toString().split("&quot;&gt;")[0];
 					}
 					
-					// Get content of linked sites
-					for (int i = 0; i < urls.length; i++) {
+					Set<String> urls = new HashSet();
+					
+				    for(int i=0; i<urlarray.length;i++){
+				        urls.add(urlarray[i]);
+				     }
+				    
+				    Iterator<String> urlit = urls.iterator();
+				    // Get content of linked sites
+				    while (urlit.hasNext()) {
+						String thisurl = urlit.next().toString();
 
 						// Dont use internal twitter links containing javascript which cannot be handled
-						if(!urls[i].contains("twitter")){
+						if(!thisurl.contains("twitter")){
 							
 						    BufferedReader content = null;
 							String response = "";
 							String encoded = "UTF-8";
 							try {
 								// Create the HttpURLConnection
-								URL url = new URL(urls[i]);
+								URL url = new URL(thisurl);
 								HttpURLConnection connection = (HttpURLConnection) url.openConnection();
 								content = null;
 								connection.setRequestMethod("GET");
-								connection.setReadTimeout(15*1000);
+								connection.setReadTimeout(2*1000);
 								connection.connect();
 
 								// Read the output from the server
@@ -178,12 +187,12 @@ public class SearchServlet extends HttpServlet {
 										encoded = connection.getContentEncoding();
 									};
 								} catch (Exception e) {
-									System.out.println("ERROR retrieving charset from " + urls[i]);
+									System.out.println("ERROR retrieving charset from " + thisurl);
[…]

### 2011-02-24 lids/twittersearchwrap/src/com/ontologycentral/twittersearchwrap/SearchServlet.java
Nur 25 URLs werden ausgelesen bei extern=true

@@ -160,13 +160,18 @@ public class SearchServlet extends HttpServlet {
 				     }
 				    
 				    Iterator<String> urlit = urls.iterator();
+				    
+				    // Maximum of 25 links used
+				    int count=0;
+				    
 				    // Get content of linked sites
-				    while (urlit.hasNext()) {
+				    while (urlit.hasNext() && count<25) {
+				    	
 						String thisurl = urlit.next().toString();
 
 						// Dont use internal twitter links containing javascript which cannot be handled
 						if(!thisurl.contains("twitter")){
-							
+
 						    BufferedReader content = null;
 							String response = "";
 							String encoded = "UTF-8";
@@ -208,7 +213,10 @@ public class SearchServlet extends HttpServlet {
 							
 
 							if (response.equals("OK") && content != null) {
-									System.out.println("EXTERNAL URL: " + thisurl);
+								
+								   	count=count+1;
+								
+									System.out.println("EXTERNAL URL No.: " + count + " : " + thisurl);
 									String readerstring = getHtmlFilteredString(content, encoded);
 									readerstring = readerstring.replaceAll("\\<.*?\\>", "");
 									readerstring = readerstring.replaceAll("\\(.*?\\)", "");

### 2011-02-24 trunk/lids/twittersearchwrap/paper/paper.tex

--- 2011-02-22 trunk/lids/twittersearchwrap/paper/paper.tex
@@
 
-\title{Mapping Microblogging Posts to Encyclopedia Articles}
+\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
+
+\title{Mapping Microblog Posts to Encyclopedia Articles}
 \author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
@@
 Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
-The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million tweets a day.
-Thus, Twitter represents a huge data source on the web.
+The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of twitter the restriction is 140 characters.
+Twitter has a total of about 190 million of users who produce 65 million twitter messages a day.
+Thus, twitter represents a huge data source on the web.
 
-Twitter offers the possibility to search for tweets containing a specific term or hash tags.
-This search returns a fixed number of most recent tweets containing the search term.
-However, it is hard to grasp the context of these tweets and to get further information on the topic that was searched for.
-As ach single tweet is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+On Twitter it is possible to search for messages containing a specific term or hash tag.
+This search returns a fixed number of most recent messages containing the search term.
+However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
+As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms, but also serve as a starting point when searching for further information related to the search result.
-This also helps to determine what the meaning of cryptic hash tags such as $\#s21$ or $\#ka$ mean.
+These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+
+On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or event.
+For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
+If a user encounters this hash tag and does not understand it, he can search for it on twitter.
+Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
+These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
 
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
-While it would be more interesting to annotate each single tweet with relevant entities, tweets are too short to contain much relevant information which could be used as input for the annotation tool.
+While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
 Thus, we chose to generate annotations for the whole search result.
 
-The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics.
+The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
 Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
 
-Annotations should be stable over time, unless the topics discussed in the tweets containing the search term change.
-In nan evaluation of our approach we have tried to analyse the stability of the result.
+Annotations should be stable over time, unless the topics discussed in the twitter messages containing the search term change.
+In an evaluation of our approach we have tried to analyze the stability of the result.
 
-The rest of this paper is organized as follows: in Section~\ref{sect:method} we present our system, in Section~\ref{sect:eval} we present the results of our evaluation
+Our contributions thus are:
+\begin{itemize}
+	\item an approach for finding entities which are related to a search on twitter
+	\item an implementation of our approach
+	\item an evaluation of the stability and relevance of the entities found with our approach.
+\end{itemize}
+
+The rest of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
+
+\section{Related Work}
+\label{sect:relWork}
+
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
+
+The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
+Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
+
+Passant et al.
+\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hash tags.
+The idea is to use URIs as hash tags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.
+\myremark{Uta}{Andreas, hättest Du noch einen Satz dazu, warum das Mapping auf RDF anders gemacht wurde als in SMOB?}
+
+Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks.
+They have instantiated their system to analyze data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
+
+A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
+%uhe: System beschreiben
 
@@
 
-The implemented
-system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}}
-(further called Twitter Search Wrapper) is called with a query and returns a
-rdf\footnote{\url{http://www.w3.org/RDF/}} document describing the most recent
-twitter posts (further called tweets) matching the given query. The returned rdf
-document furthermore contains a mapping of the query to Encyclopedia articles
-which based on the content published by users that most recently used the query
-in their posts maps to articles best describing the content of tweets related to
-the query. An overview of the System Architecture is given in Figure
-\ref{fig:arch}. Taking a more detailed look, methods performed by the Twitter
-Search Wrapper can be grouped into five sequential steps (see Figure
-\ref{fig:arch}) .
->>>>>>> .r181
+The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result, i.e.
+the most recent messages that match the query, the authors of these messages and the most relevant entities for this result.
+
+The architecture of our proposed system is shown in Figure~\ref{fig:arch}.
+Upon receipt of a query four steps are performed.
+In the following we will illustrate these steps using the example of a search for the hash tag $\#ka$, a hashtag which is frequently used to describe posts related to the city of Karlsruhe, Germany.
 
@@
 
-In a first step the Twitter Search Wrapper fetches the atom feed
-generated by the twitter search
-api\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given search
-query. The generated feed contains information about the 100 most recently published publicly visible tweets and
-their authors which match the search query. The tweets itself are described by
-their content, publishing date, authors and optionally a geographic location.
+\begin{enumerate}
+	\item In a first step, the most recent search results for the query are obtained. In our example, calling the Wrapper with query $\#ka$ will return a
+document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
 
-In a second (optional) step hyperlinks posted in tweets of the fetched
-feed are followed, content of the referenced website's body is fetched and
-processed to the Wrapper. This option is triggered calling the Wrapper
-service with attribute extern=true.
+An example for a single retrieved post is the following: \texttt{''Just returned from a wonderful holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets''}
+\myremark{Frage}{Sollte man da auch noch die Metadaten (Autor, Uhrzeit) mit angeben?}
 
-The Wrapper now calls the Wikifier \cite{key:wikifier} service. Content of the
-tweets that matched the search query and optional content of their referenced websites is merged
-to a single input string which is used as input for the Wikifier. The service
-returns a list of matching articles of the English
-Wikipedia. Optionally the wrapper can be initially called with lang=de to
-trigger mapping to the German Wikipedia.
+  \item In a second (optional) step hyperlinks posted in messages of the fetched feed are followed, content of the referenced website's body is fetched and processed by the Wrapper.
+The idea is to acquire additional content which is used as additional signal when searching for entities.
+We have thought of other methods for enriching the result, like searching for other messages posted by users which have posted messages in the result set.
+However, these alternative method are more likely to introduce noise in the signal which is used for obtaining relevant entities.
 
-The list of matching Wikipedia articles is returned to the Wrapper. The Wrapper
-generates a rdf document using popular ontologies (foaf, dublincore,\ldots) to
-describe the data related to the returned tweets and their content including 'rdfs:seeAlso' links to
-DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted output of the
-Wikifier) describing the documents content.
+In our example, the message contains a link to\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe.
+Dereferencing this URL and grabbing the text found at the link gives us the following text:''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
+
+	\item In a third step entities matching the search result are retrieved.
+The content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
+The result of this step is a list of matching articles of the English Wikipedia.
+
+In our example, the contents of all posts related to the search term '\#ka' are merged with the retrieved external website content.
+Thus, the post obtained from step 1 would be matched with the website content obtained in step 2 into a single input stream: \texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets.
+Karlsruhe, where paths \newline converge - a legendary city in the sunny south-west of Germany, famed for its \newline fan-shaped historic street plan, where margraves reigned in times past, and German \newline joie de vivre reigns today.}
+This string is appended to the Twitter content and the external content of all other posts in the result.
+
+In the example, we would expect to find entities which are related to Karlsruhe, like Karlsruhe, Germany or the Karlsruhe\_Institute\_of\_Technology.
+
+	\item	Finally, an RDF document is generated representing the search results and the annotations.
+
+	Continuing our example, the output RDF document contains the following triples to reference the DBPedia mappings: 
+	\myremark{Uta}{Bei den Tripeln fehlt das Subjekt}
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+	Karlsruhe\_Institute\_of\_Technology"/>}
+
+	The twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
+
+	\texttt{<rdf:Description rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+	show/1234567890\#id">\newline
+	<foaf:page rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+	<geo:lat>49.010239</geo:lat>\newline 
+	<geo:long>8.411879</geo:long>\newline
+	<foaf:maker rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+	show?screen\_name=sample\_user\_12345\#id"/>\newline 
+	<dc:description>\newline
+	Just returned from a wonderful holiday in \#ka.
+	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+	</dc:description>\newline
+	</rdf:Description>\newline}
+\end{enumerate}
+\myremark{Uta}{Gibt es was, was man zu Dublin Core zitieren kann?}
+
+\section{Implementation}
+
+In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
+
+The implementation is based on a set of existing components: Twitter search results are obtained by using the twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
+The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors.
+The messages themselves are described by their content, publishing date, authors
+and optionally a geographic location.
+
+The optional step of dereferencing URLs which are posted in messages contained in the result set can be triggered using the option \texttt{extern=true}.
+To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first $k$ words.
+\myremark{TODO}{Was ist der cut-off-Wert?}
+
+The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
+
+The RDF document describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs.
+DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.
+
+%The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
+%the Twitter search term and returns a RDF}
+%document semantically describing the most recent Twitter messages matching the
+%given query. The returned RDF document furthermore contains a mapping of the
+%query to Encyclopedia articles which based on the content published by users that most recently used the search
+%term in their posts maps to articles best describing the content of Twitter
+%messages related to the term. An overview of the System Architecture is given in Figure
+%\ref{fig:arch}.\newline 
+%Taking a more detailed look, methods performed by the
+%Twitter Search Wrapper can be grouped into five sequential steps (see Figure
+%\ref{fig:arch}). We will follow those steps along a simple example, using
+%\#ka (a hashtag frequently used to describe posts related to the city of
+%Karlsruhe, Germany) as search term for the Twitter Search wrapper.
+
+%\begin{enumerate}
+%  \item 
+%In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
+%generated by the Twitter Search
+%API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
+%search query. The generated feed contains the data of the 100 most recently published
+%publicly visible Twitter messages and their authors which match the search query.
+%The messages themselves are described by their content, publishing date, authors
+%and optionally a geographic location.\linebreak\linebreak
+%In the given example, calling the Wrapper with query '\#ka' will return a
+%document containing all most recent Twitter posts and their meta information
+%whose content matched the search string '\#ka'. Taking a closer look, a single
+%retrieved post might have the following content: \newline\linebreak 
+%\texttt{Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
+%\linebreak
+%\item
+%In a second (optional) step hyperlinks posted in messages of the fetched
+%feed are followed, content of the referenced website's body is fetched and
+%processed to the Wrapper. This option is triggered calling the Twitter Search
+%Wrapper with attribute extern=true.\newline
+%\linebreak
+%Following the initial example, the given sample post contained a link to
+%\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
+%text:\newline
+%\linebreak
+%''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+%south-west of Germany,\newline famed for its fan-shaped historic street plan,
+%where margraves reigned in times past,\newline and German joie de vivre reigns
+%today.}''\newline\linebreak
+%The text is fetched and returned to the Wrapper. The same accounts for
+%content of all other websites that were referenced in the list of posts matching
+%the query \#ka.\newline
+%\item
+%The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
+%the Twitter messages that matched the search query and optional content of their
+%referenced websites is merged to a single input string which is used as input for the Wikifier. The service
+%returns a list of matching articles of the English
+%Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
+%to trigger mapping to the German Wikipedia.\newline\linebreak
+%In the given example, content of all posts related to the search term '\#ka' is
+%merged with retrieved external website content. Taking a closer look at the
+%single post we merge its content and content of its referenced website to
+%a single string:\newline\linebreak
+%\texttt{Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
+%where paths converge - a legendary city in the sunny\newline south-west of
+%Germany, famed for its fan-shaped historic street plan, where margraves\newline
+%reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
+%This string is appended to Twitter content and external content of all other
+%posts that have been retrieved in this way matching the initial query \#ka and
+%used as input for the Wikifier.\newline
+%  \item
+%The Wikifier now maps the input string to relevant Wikipedia articles. A
+%detailed description of this process can be found under \cite{key:wikifier}. 
+%The list of matching Wikipedia articles is finally returned to the
+%Wrapper.\newline\linebreak
+%In the given example, a desired mapping of the contents of posts related to the
+%hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
+%mapping to Wikipedia articles describing content related to Karlsruhe. We just
+%assume this results in mappings to the articles for Karlsruhe, Germany and the
+%Karlsruhe\_Institute\_of\_Technology.\newline
+%  \item
+%The Wrapper finally generates a RDF document using popular ontologies
+%(foaf\footnote{http://xmlns.com/foaf/spec/},
+%dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
+%returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
+%the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
+%output of the Wikifier) that have been mapped to the documents content.
+%At this point DBPedia is chosen as referenced encyclopedia, because its
+%semantic nature and description of Wikipedia article content contributes to a
+%coherent semantic description in the RDF document. \newline\linebreak Coming
+%back to the example, the output RDF document contains the following triples to reference the
+%DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
+%rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+%\texttt{<rdfs:seeAlso
+%rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+%\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+%Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
+%The twitter posts matching the search term \#ka are all described in the output
+%document. As an example, the description for the initially given post might
+%result in the following RDF output:\newline\linebreak
+%\texttt{<rdf:Description
+%rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+%show/1234567890\#id">\newline <foaf:page
+%rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+%<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+%<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+%<foaf:maker
+%rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+%show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+%Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+%</dc:description>\newline
+%</rdf:Description>\newline}
+%\end{enumerate}
 
@@
 
-\begin{definition}[Stability]
+The goal of our evaluation was to examine the stability of the entity annotations over time.
+To achieve this, we have repeatedly executed the same set of queries.
+\myremark{TODO}{How frequently?
+How long?
+Which queries?}
+In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains.
+We have then evaluated the results with respect to several measures:
 
+\begin{definition}[Evaluation Measures]
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with entities $E_1,\ldots,E_n$, we define:
+\begin{itemize}
+	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
+	\item The global stability of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{\bigcap_{i=1}^{n}E_i}{\bigcup_{i=1}^{n}E_i}$$
+	\item The stability for a single term is defined as the fraction of result sets in which it occurs: 
+$$st(t)=\frac{|\{i|t\in E_i\}|}{n}$$
+\end{itemize}
 \end{definition}
 
-\section{Related Work}
+\section{Conclusion}
+\label{sect:conclusion}
 
-Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before.
+@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka
 
-Passant et al. \cite{key:smob} have proposed a data model for making twitter
-data available on the Semantic Web.
-They propose a data model which allows for the association of URIs with users, microblogs and microposts.
-To this end, SIOC and FOAF vocabularies are used and extended.
-Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced.
-Additionally, they propose the use of so-called semantic hash tags.
-The idea is to use URIs as hash tags (e.g.
-\emph{\#geo:Paris\_France}).
-It becomes thus possible to link microposts to entities in the Linked Open Data cloud.
-\section{Conclusion}
+@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages
+
+@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
 

### 2011-02-24 lids/twittersearchwrap/paper/paper.tex

@@
 It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.
+\myremark{Uta}{Andreas, hättest Du noch einen Satz dazu, warum das Mapping auf RDF anders gemacht wurde als in SMOB?}
 
@@
 
-The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/} document describing the search result, i.e.
+The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result, i.e.
 the most recent messages that match the query, the authors of these messages and the most relevant entities for this result.
 
-The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
-the Twitter search term and returns a RDF}
-document semantically describing the most recent Twitter messages matching the
-given query. The returned RDF document furthermore contains a mapping of the
-query to Encyclopedia articles which based on the content published by users that most recently used the search
-term in their posts maps to articles best describing the content of Twitter
-messages related to the term. An overview of the System Architecture is given in Figure
-\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
-Twitter Search Wrapper can be grouped into five sequential steps (see Figure
-\ref{fig:arch}). We will follow those steps along a simple example, using
-\#ka (a hashtag frequently used to describe posts related to the city of
-Karlsruhe, Germany) as search term for the Twitter Search wrapper.
+The architecture of our proposed system is shown in Figure~\ref{fig:arch}.
+Upon receipt of a query four steps are performed.
+In the following we will illustrate these steps using the example of a search for the hash tag $\#ka$, a hashtag which is frequently used to describe posts related to the city of Karlsruhe, Germany.
 
@@
 \begin{enumerate}
-  \item 
-In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
-generated by the Twitter Search
-API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
-search query. The generated feed contains the data of the 100 most recently published
-publicly visible Twitter messages and their authors which match the search query.
-The messages themselves are described by their content, publishing date, authors
-and optionally a geographic location.\linebreak\linebreak
-In the given example, calling the Wrapper with query '\#ka' will return a
-document containing all most recent Twitter posts and their meta information
-whose content matched the search string '\#ka'. Taking a closer look, a single
-retrieved post might have the following content: \newline\linebreak 
-\texttt{Just returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
-\linebreak
-\item
-In a second (optional) step hyperlinks posted in messages of the fetched
-feed are followed, content of the referenced website's body is fetched and
-processed to the Wrapper. This option is triggered calling the Twitter Search
-Wrapper with attribute extern=true.\newline
-\linebreak
-Following the initial example, the given sample post contained a link to
-\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
-text:\newline
-\linebreak
-''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
-south-west of Germany,\newline famed for its fan-shaped historic street plan,
-where margraves reigned in times past,\newline and German joie de vivre reigns
-today.}''\newline\linebreak
-The text is fetched and returned to the Wrapper. The same accounts for
-content of all other websites that were referenced in the list of posts matching
-the query \#ka.\newline
-\item
-The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
-the Twitter messages that matched the search query and optional content of their
-referenced websites is merged to a single input string which is used as input for the Wikifier. The service
-returns a list of matching articles of the English
-Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
-to trigger mapping to the German Wikipedia.\newline\linebreak
-In the given example, content of all posts related to the search term '\#ka' is
-merged with retrieved external website content. Taking a closer look at the
-single post we merge its content and content of its referenced website to
-a single string:\newline\linebreak
-\texttt{Just returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
-where paths converge - a legendary city in the sunny\newline south-west of
-Germany, famed for its fan-shaped historic street plan, where margraves\newline
-reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
-This string is appended to Twitter content and external content of all other
-posts that have been retrieved in this way matching the initial query \#ka and
-used as input for the Wikifier.\newline
-  \item
-The Wikifier now maps the input string to relevant Wikipedia articles. A
-detailed description of this process can be found under \cite{key:wikifier}. 
-The list of matching Wikipedia articles is finally returned to the
-Wrapper.\newline\linebreak
-In the given example, a desired mapping of the contents of posts related to the
-hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
-mapping to Wikipedia articles describing content related to Karlsruhe. We just
-assume this results in mappings to the articles for Karlsruhe, Germany and the
-Karlsruhe\_Institute\_of\_Technology.\newline
-  \item
-The Wrapper finally generates a RDF document using popular ontologies
-(foaf\footnote{http://xmlns.com/foaf/spec/},
-dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
-returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
-the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
-output of the Wikifier) that have been mapped to the documents content.
-At this point DBPedia is chosen as referenced encyclopedia, because its
-semantic nature and description of Wikipedia article content contributes to a
-coherent semantic description in the RDF document. \newline\linebreak Coming
-back to the example, the output RDF document contains the following triples to reference the
-DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
-rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-\texttt{<rdfs:seeAlso
-rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+	\item In a first step, the most recent search results for the query are obtained. In our example, calling the Wrapper with query $\#ka$ will return a
+document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
+
+An example for a single retrieved post is the following: \texttt{''Just returned from a wonderful holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets''}
+\myremark{Frage}{Sollte man da auch noch die Metadaten (Autor, Uhrzeit) mit angeben?}
+
+  \item In a second (optional) step hyperlinks posted in messages of the fetched feed are followed, content of the referenced website's body is fetched and processed by the Wrapper.
+The idea is to acquire additional content which is used as additional signal when searching for entities.
+We have thought of other methods for enriching the result, like searching for other messages posted by users which have posted messages in the result set.
+However, these alternative method are more likely to introduce noise in the signal which is used for obtaining relevant entities.
+
+In our example, the message contains a link to\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe.
+Dereferencing this URL and grabbing the text found at the link gives us the following text:''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
+
+	\item In a third step entities matching the search result are retrieved.
+The content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
+The result of this step is a list of matching articles of the English Wikipedia.
+
+In our example, the contents of all posts related to the search term '\#ka' are merged with the retrieved external website content.
+Thus, the post obtained from step 1 would be matched with the website content obtained in step 2 into a single input stream: \texttt{Just returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets.
+Karlsruhe, where paths \newline converge - a legendary city in the sunny south-west of Germany, famed for its \newline fan-shaped historic street plan, where margraves reigned in times past, and German \newline joie de vivre reigns today.}
+This string is appended to the Twitter content and the external content of all other posts in the result.
+
+In the example, we would expect to find entities which are related to Karlsruhe, like Karlsruhe, Germany or the Karlsruhe\_Institute\_of\_Technology.
+
+	\item	Finally, an RDF document is generated representing the search results and the annotations.
+
+	Continuing our example, the output RDF document contains the following triples to reference the DBPedia mappings: 
+	\myremark{Uta}{Bei den Tripeln fehlt das Subjekt}
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
 	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
-The twitter posts matching the search term \#ka are all described in the output
-document. As an example, the description for the initially given post might
-result in the following RDF output:\newline\linebreak
-\texttt{<rdf:Description
-rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
-show/1234567890\#id">\newline <foaf:page
-rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+	Karlsruhe\_Institute\_of\_Technology"/>}
+
+	The twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
+
+	\texttt{<rdf:Description rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+	show/1234567890\#id">\newline
+	<foaf:page rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
 	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
-<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
-<foaf:maker
-rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+	<geo:lat>49.010239</geo:lat>\newline 
+	<geo:long>8.411879</geo:long>\newline
+	<foaf:maker rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+	show?screen\_name=sample\_user\_12345\#id"/>\newline 
+	<dc:description>\newline
 	Just returned from a wonderful holiday in \#ka.
@@
 \end{enumerate}
+\myremark{Uta}{Gibt es was, was man zu Dublin Core zitieren kann?}
+
+\section{Implementation}
+
+In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
+
+The implementation is based on a set of existing components: Twitter search results are obtained by using the twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
+The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors.
+The messages themselves are described by their content, publishing date, authors
+and optionally a geographic location.
+
+The optional step of dereferencing URLs which are posted in messages contained in the result set can be triggered using the option \texttt{extern=true}.
+To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first $k$ words.
+\myremark{TODO}{Was ist der cut-off-Wert?}
+
+The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
+
+The RDF document describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs.
+DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.
+
+\myremark{Uta}{David, kannst Du das Ausgabeformat noch etwas ausführlicher beschreiben? Welche Informationen werden genau dargestellt, welche Relationen werden wofür verwendet?}
+
+%The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
+%the Twitter search term and returns a RDF}
+%document semantically describing the most recent Twitter messages matching the
+%given query. The returned RDF document furthermore contains a mapping of the
+%query to Encyclopedia articles which based on the content published by users that most recently used the search
+%term in their posts maps to articles best describing the content of Twitter
+%messages related to the term. An overview of the System Architecture is given in Figure
+%\ref{fig:arch}.\newline 
+%Taking a more detailed look, methods performed by the
+%Twitter Search Wrapper can be grouped into five sequential steps (see Figure
+%\ref{fig:arch}). We will follow those steps along a simple example, using
+%\#ka (a hashtag frequently used to describe posts related to the city of
+%Karlsruhe, Germany) as search term for the Twitter Search wrapper.
+
+%\begin{enumerate}
+%  \item 
+%In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
+%generated by the Twitter Search
+%API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
+%search query. The generated feed contains the data of the 100 most recently published
+%publicly visible Twitter messages and their authors which match the search query.
+%The messages themselves are described by their content, publishing date, authors
+%and optionally a geographic location.\linebreak\linebreak
+%In the given example, calling the Wrapper with query '\#ka' will return a
+%document containing all most recent Twitter posts and their meta information
+%whose content matched the search string '\#ka'. Taking a closer look, a single
+%retrieved post might have the following content: \newline\linebreak 
+%\texttt{Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
+%\linebreak
+%\item
+%In a second (optional) step hyperlinks posted in messages of the fetched
+%feed are followed, content of the referenced website's body is fetched and
+%processed to the Wrapper. This option is triggered calling the Twitter Search
+%Wrapper with attribute extern=true.\newline
+%\linebreak
+%Following the initial example, the given sample post contained a link to
+%\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
+%text:\newline
+%\linebreak
+%''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
+%south-west of Germany,\newline famed for its fan-shaped historic street plan,
+%where margraves reigned in times past,\newline and German joie de vivre reigns
+%today.}''\newline\linebreak
+%The text is fetched and returned to the Wrapper. The same accounts for
+%content of all other websites that were referenced in the list of posts matching
+%the query \#ka.\newline
+%\item
+%The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
+%the Twitter messages that matched the search query and optional content of their
+%referenced websites is merged to a single input string which is used as input for the Wikifier. The service
+%returns a list of matching articles of the English
+%Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
+%to trigger mapping to the German Wikipedia.\newline\linebreak
+%In the given example, content of all posts related to the search term '\#ka' is
+%merged with retrieved external website content. Taking a closer look at the
+%single post we merge its content and content of its referenced website to
+%a single string:\newline\linebreak
+%\texttt{Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
+%where paths converge - a legendary city in the sunny\newline south-west of
+%Germany, famed for its fan-shaped historic street plan, where margraves\newline
+%reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
+%This string is appended to Twitter content and external content of all other
+%posts that have been retrieved in this way matching the initial query \#ka and
+%used as input for the Wikifier.\newline
+%  \item
+%The Wikifier now maps the input string to relevant Wikipedia articles. A
+%detailed description of this process can be found under \cite{key:wikifier}. 
+%The list of matching Wikipedia articles is finally returned to the
+%Wrapper.\newline\linebreak
+%In the given example, a desired mapping of the contents of posts related to the
+%hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
+%mapping to Wikipedia articles describing content related to Karlsruhe. We just
+%assume this results in mappings to the articles for Karlsruhe, Germany and the
+%Karlsruhe\_Institute\_of\_Technology.\newline
+%  \item
+%The Wrapper finally generates a RDF document using popular ontologies
+%(foaf\footnote{http://xmlns.com/foaf/spec/},
+%dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
+%returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
+%the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
+%output of the Wikifier) that have been mapped to the documents content.
+%At this point DBPedia is chosen as referenced encyclopedia, because its
+%semantic nature and description of Wikipedia article content contributes to a
+%coherent semantic description in the RDF document. \newline\linebreak Coming
+%back to the example, the output RDF document contains the following triples to reference the
+%DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
+%rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+%\texttt{<rdfs:seeAlso
+%rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+%\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+%Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
+%The twitter posts matching the search term \#ka are all described in the output
+%document. As an example, the description for the initially given post might
+%result in the following RDF output:\newline\linebreak
+%\texttt{<rdf:Description
+%rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
+%show/1234567890\#id">\newline <foaf:page
+%rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
+%<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+%<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+%<foaf:maker
+%rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+%show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+%Just returned from a wonderful holiday in \#ka.
+%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+%</dc:description>\newline
+%</rdf:Description>\newline}
+%\end{enumerate}
 

### 2011-02-25 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
-The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of twitter the restriction is 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million twitter messages a day.
-Thus, twitter represents a huge data source on the web.
+The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters.
+Twitter has a total of about 190 million of users who produce 65 million Twitter messages a day.
+Thus, Twitter represents a huge data source on the web.
 
@@
 However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
-As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+As each single Twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
@@
 
-On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or event.
-For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
-If a user encounters this hash tag and does not understand it, he can search for it on twitter.
+Furthermore, this annotation will help to understand hash tags.
+Hash tags are frequently used to associate messages with a specific topic, place, person or event on Twitter.
+For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
+If a user encounters this hash tag and does not understand it, he can search for it on Twitter.
+However, as discussed before, to understand a search result is difficult and time-consuming.
 Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
-These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
+These entities will help the user to gain an understanding in which context the hash tag is used and what it may mean.
+
+Finding entities matching a query, especially a query for a given hash tag is difficult due to synonyms and homonyms in the set of hash tags that are frequently used.
+For example, both the hash tags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
+The tag $\#ka$ is however also used in the context of the car type Ford Ka.
+Thus, when searching for $\#ka$ on Twitter, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
+An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.
 
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
-While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
+While it would be more interesting to annotate each single Twitter message with relevant entities, Twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
 Thus, we chose to generate annotations for the whole search result.
@@
 
-Annotations should be stable over time, unless the topics discussed in the twitter messages containing the search term change.
+Annotations should be stable over time, unless the topics discussed in the Twitter messages containing the search term change.
 In an evaluation of our approach we have tried to analyze the stability of the result.
@@
 \begin{itemize}
-	\item an approach for finding entities which are related to a search on twitter
+	\item an approach for finding entities which are related to a search on Twitter
 	\item an implementation of our approach
@@
 Passant et al.
-\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+\cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web.
 They propose a data model which allows for the association of URIs with users, microblogs and microposts.
@@
 It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.
-\myremark{Uta}{Andreas, hättest Du noch einen Satz dazu, warum das Mapping auf RDF anders gemacht wurde als in SMOB?}
+In contrast to this approach we do not require users to change their behavior by requiring them to use another type of hash tags.
+Instead, our method finds Linked Open Data entities which are related to the query automatically.
 
@@
 The system by Passant et al.
-\cite{key:smob} is used for transforming twitter data to semantic data.
+\cite{key:smob} is used for transforming Twitter data to semantic data.
 The triplified data can then be analysed using SPARQL.
@@
 
-The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result, i.e.
-the most recent messages that match the query, the authors of these messages and the most relevant entities for this result.
+The goal of our method is to, given a search query $q$ as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e.
+the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result.
 
@@
 
-	The twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
+	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
 
@@
 
-The implementation is based on a set of existing components: Twitter search results are obtained by using the twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
+The implementation is based on a set of existing components: Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
 The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors.
@@
 DBpedia has been chosen as these entities allow for a more coherent presentation of the content in the context of RDF.
+
+\myremark{Uta}{David, kannst Du das Ausgabeformat noch etwas ausführlicher beschreiben? Welche Informationen werden genau dargestellt, welche Relationen werden wofür verwendet?}
 
@@
 \begin{definition}[Evaluation Measures]
-Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with entities $E_1,\ldots,E_n$, we define:
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, we define:
 \begin{itemize}
 	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
-	\item The global stability of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{\bigcap_{i=1}^{n}E_i}{\bigcup_{i=1}^{n}E_i}$$
-	\item The stability for a single term is defined as the fraction of result sets in which it occurs: 
-$$st(t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	A high $adt(q)$ means that new messages that match the query $q$ are not generated very often. If new messages matching the query $q$ are frequently published, then the $adt(q)$ is low.
+	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
+	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
+On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
+	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
+	$$ts(q,t_i)=\begin{cases} |E_i| & i=1 \\
+														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
+	Here again, a value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.
+	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
+$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
 \end{itemize}
@@
 
+\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
 \section{Conclusion}

### 2011-02-25 lids/twittersearchwrap/paper/paper.tex
added some related work

@@
 
+Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
+As such, our approach is closely related.
+Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
+Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
+The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
+The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
+%uhe: System beschreiben
+Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
+We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
+
+In order to make tweets more searchable and make them useful for the described
+scenario one would need to have represent them in a structured format and associate
+those tweets with the topics that refer to. As a basic approach we process the text of
+the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+concepts related to a tweet, but is useful only on a limited number of tweets directly
+mentioning a particular topic. In the example data set we produced from ESWC2010,
+tweet topics are represented using dc:subject property.
+
 Passant et al.
-\cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web.
+\cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web.
 They propose a data model which allows for the association of URIs with users, microblogs and microposts.
@@
 The system by Passant et al.
-\cite{key:smob} is used for transforming twitter data to semantic data.
+\cite{key:smob} is used for transforming Twitter data to semantic data.
 The triplified data can then be analysed using SPARQL.
 They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
-
-A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
-%uhe: System beschreiben
 
@@
 
+\subsection{Setup}
+
 Trending topics are listed in Table \ref{tbl:terms}.
@@
 
+\subsection{Measures}
+
 The goal of our evaluation was to examine the stability of the entity annotations over time.
@@
 \begin{definition}[Evaluation Measures]
-Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with entities $E_1,\ldots,E_n$, we define:
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, we define:
 \begin{itemize}
 	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
-	\item The global stability of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{\bigcap_{i=1}^{n}E_i}{\bigcup_{i=1}^{n}E_i}$$
-	\item The stability for a single term is defined as the fraction of result sets in which it occurs: 
-$$st(t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	A high $adt(q)$ means that new messages that match the query $q$ are not generated very often. If new messages matching the query $q$ are frequently published, then the $adt(q)$ is low.
+	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
+	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
+On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
+	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
+	$$ts(q,t_i)=\begin{cases} |E_i| & i=1 \\
+														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
+	Here again, a value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.
+	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
+$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
 \end{itemize}
 \end{definition}
+
+\subsection{Results}
+
+\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+
+\subsection{Discussion}
+
+@@@highlight the remarkable outcomes
+@@@what is did we learn from the results?
 

### 2011-02-28 lids/twittersearchwrap/paper/paper.tex
added weps-3 challenge

@@
 
+The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
+The corpus contains evaluation results solicited via Mechanical Turk.
+In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
+@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?
+
 Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
@@
 Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
+% from stakovic et al.
+%In order to make tweets more searchable and make them useful for the described
+%scenario one would need to have represent them in a structured format and associate
+%those tweets with the topics that refer to. As a basic approach we process the text of
+%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+%concepts related to a tweet, but is useful only on a limited number of tweets directly
+%mentioning a particular topic. In the example data set we produced from ESWC2010,
+%tweet topics are represented using dc:subject property.
+
 Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
@@
 We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
-
-In order to make tweets more searchable and make them useful for the described
-scenario one would need to have represent them in a structured format and associate
-those tweets with the topics that refer to. As a basic approach we process the text of
-the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
-concepts related to a tweet, but is useful only on a limited number of tweets directly
-mentioning a particular topic. In the example data set we produced from ESWC2010,
-tweet topics are represented using dc:subject property.
 

### 2011-03-02 trunk/lids/twittersearchwrap/paper/paper.tex
added a few remarks

@@
 
+The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
+The corpus contains evaluation results solicited via Mechanical Turk.
+In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
+@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?
+
+Softic et al \cite{key:softic} have developed a framework and system for mining
+data from social networks.
+They have instantiated their system to analyze data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
+Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
+As such, our approach is closely related.
+Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
+% from stakovic et al.
+%In order to make tweets more searchable and make them useful for the described
+%scenario one would need to have represent them in a structured format and associate
+%those tweets with the topics that refer to. As a basic approach we process the text of
+%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+%concepts related to a tweet, but is useful only on a limited number of tweets directly
+%mentioning a particular topic. In the example data set we produced from ESWC2010,
+%tweet topics are represented using dc:subject property.
+
+Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
+The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
+The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
+%uhe: System beschreiben
+Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
+We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
+
 Passant et al.
@@
 
-A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
-%uhe: System beschreiben
-
 \section{Method Overview}
@@
 \begin{enumerate}
-	\item In a first step, the most recent search results for the query are obtained. In our example, calling the Wrapper with query $\#ka$ will return a
-document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
+	\item In a first step, the most recent search results for the query are
+	obtained.\newline In our example, calling the Wrapper with query $\#ka$ will
+	return a document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
 
-An example for a single retrieved post is the following: \texttt{''Just returned from a wonderful holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets''}
-\myremark{Frage}{Sollte man da auch noch die Metadaten (Autor, Uhrzeit) mit angeben?}
+An example for a single retrieved post is the following: ''\texttt{Just
+returned from a wonderful holiday in \#ka.
+\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}'', posted by
+Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
+the message has been posted be furthermore known.
 
-  \item In a second (optional) step hyperlinks posted in messages of the fetched feed are followed, content of the referenced website's body is fetched and processed by the Wrapper.
+  \item In a second (optional) step hyperlinks posted in messages of the fetched
+  feed are followed, content of the referenced website is fetched and processed by the Wrapper.
 The idea is to acquire additional content which is used as additional signal when searching for entities.
 We have thought of other methods for enriching the result, like searching for other messages posted by users which have posted messages in the result set.
-However, these alternative method are more likely to introduce noise in the signal which is used for obtaining relevant entities.
+However, these alternative methods are more likely to introduce noise in the signal which is used for obtaining relevant entities.
 
-In our example, the message contains a link to\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe.
-Dereferencing this URL and grabbing the text found at the link gives us the following text:''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
-south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
+In our example, the message contains a link to
+\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
+tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
+text found at the link gives us the following text: ''\texttt{Karlsruhe, where
+paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
 
@@
 
-	Continuing our example, the output RDF document contains the following triples to reference the DBPedia mappings: 
-	\myremark{Uta}{Bei den Tripeln fehlt das Subjekt}
+	Continuing our example, the output RDF document contains the following triples
+	to reference the DBPedia mappings:\newline
+	\texttt{<rdf:Description rdf:about=""/>}\newline
 	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
@@
 	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-	Karlsruhe\_Institute\_of\_Technology"/>}
-
+	Karlsruhe\_Institute\_of\_Technology"/>}\newline
+	\texttt{</rdf:Description>}\newline
 	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
@@
 
-The optional step of dereferencing URLs which are posted in messages contained in the result set can be triggered using the option \texttt{extern=true}.
-To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first $k$ words.
-\myremark{TODO}{Was ist der cut-off-Wert?}
+The optional step of dereferencing URLs which are posted in messages contained
+in the result set can be triggered using the option \texttt{extern=true}.
+To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first 50 words.
 
@@
 \end{table}
+
+\subsection{Measures}
 
@@
 
+\subsection{Results}
+
 \myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+
+\subsection{Discussion}
+
+@@@highlight the remarkable outcomes
+@@@what is did we learn from the results?
+
 \section{Conclusion}

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

@@
 %\newcommand{\nop}[1]{}
+
+\setlength{\tabcolsep}{2pt}
 
@@
 
+Softic et al \cite{key:softic} have developed a framework and system for mining
+data from social networks.
+They have instantiated their system to analyze data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
 Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
@@
 
-Trending topics are listed in Table \ref{tbl:terms}.
+Topics trending worldwide and in Germany at Twitter retrieved at February 24th
+17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
+constitute a basis of input search terms for our evaluation of the Twitter
+Search Wrapper.
 
@@
 \centering
-\begin{tabular}{ c }
-Search term                    \\
+\begin{tabular}{ |l|l| }
 \hline
-\#s21 \\
-Karlsruhe\\
+\textsc{Trending Topic} & \textsc{Location}  \\
+\hline
+\#goodlucknickj & Worldwide \\
+\#smalljoys & Worldwide \\
+\#thingsthedevilinvented & Worldwide \\
+Adam Wainwright & Worldwide \\
+CatchPetrovaFire & Worldwide \\
+Gadafi & Worldwide \\
+Libia & Worldwide \\
+Precious Minaj & Worldwide \\
+Tommy John & Worldwide \\
+\hline
+\#gaddafi & Germany \\
+\#guttenberg & Germany \\
+\#libya & Germany \\
+Doktorarbeit & Germany \\
+Gef\"{u}hl & Germany \\
+Lion & Germany \\
+MBP & Germany \\
+Thunderbolt & Germany \\
+Vorratsdatenspeicherung & Germany \\
+\hline
 \end{tabular}
@@
 
-The goal of our evaluation was to examine the stability of the entity annotations over time.
-To achieve this, we have repeatedly executed the same set of queries.
-\myremark{TODO}{How frequently?
-How long?
-Which queries?}
-In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains.
-We have then evaluated the results with respect to several measures:
+The goal of our evaluation was to examine the stability of the entity
+annotations over time. To achieve this, we have repeatedly executed the same set
+of queries using the retrieved trending topics given in Table \ref{tbl:terms}
+as input queries for the evaluation. The set of queries was executed twice per
+hour in a 24 hour time frame starting from the moment the topics were identified
+and retrieved as trending topics. In a first step we have filtered the result
+sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:
 

### 2011-03-03 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 
-Trending topics are listed in Table \ref{tbl:terms}.
+Topics trending worldwide and in Germany at Twitter retrieved on February 24th
+17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
+constitute a basis of input search terms for our evaluation of the Twitter
+Search Wrapper.
 
@@
 
-The goal of our evaluation was to examine the stability of the entity annotations over time.
-To achieve this, we have repeatedly executed the same set of queries.
-\myremark{TODO}{How frequently?
-How long?
-Which queries?}
-In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains.
-We have then evaluated the results with respect to several measures:
+The goal of our evaluation was to examine the stability of the entity
+annotations over time. To achieve this, we have repeatedly executed the same set
+of queries and saved the returned data. Two methods for this data acquisition
+were identified: \begin{definition}[Data Acquisition Methods]
+\begin{itemize}
+\item Temporal Sliding Window: The query is executed and the n most
+recent results are retrieved every t minutes. The Temporal Sliding Window method
+may lead to duplicate messages in the retrieved documents, but needs to handle much less data and
+allows for an analysis over larger time frames.
+\item k-item Sliding Window: The k-item Sliding Window methods retrieves all
+messages that match the query exactly one time. Each time k new messages are
+available matching the given query a document containing those k messages
+is retrieved. This method can lead to high data volume and needs constant
+monitoring of recently posted messages matching the search term.
+\end{itemize}
+\end{definition}
+
+Using the retrieved trending topics given in Table \ref{tbl:terms}
+as input queries for the evaluation, the set of queries was executed twice
+per hour using the Temporal Sliding Window method for data acquisition in a 24
+hour time frame starting from the moment the topics were identified as trending topics.  We have then evaluated the results with respect to several measures:
 

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

@@
 
-Topics trending worldwide and in Germany at Twitter retrieved at February 24th
+Topics trending worldwide and in Germany at Twitter retrieved on February 24th
 17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
@@
 annotations over time. To achieve this, we have repeatedly executed the same set
-of queries using the retrieved trending topics given in Table \ref{tbl:terms}
-as input queries for the evaluation. The set of queries was executed twice per
-hour in a 24 hour time frame starting from the moment the topics were identified
-and retrieved as trending topics. In a first step we have filtered the result
-sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:
+of queries and saved the returned data. Two methods for this data acquisition
+were identified: \begin{definition}[Data Acquisition Methods]
+\begin{itemize}
+\item {\bf Temporal Sliding Window}\newline The query is executed and the n
+most recent results are retrieved every t minutes. The Temporal Sliding Window
+method may lead to duplicate messages in the retrieved documents, but needs to
+handle much less data and allows for an analysis over larger time frames.
+\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
+retrieves all messages that match the query exactly one time. Each time k new messages are
+available matching the given query a document containing those k messages
+is retrieved. This method can lead to high data volume and needs constant
+monitoring of recently posted messages matching the search term.
+\end{itemize}
+\end{definition}
+
+We considered the trending topics on Twitter a good set of input queries for
+our evaluation approach. Trending topics often cover a variety of recently
+talked about topics which due to its recent nature may be of high interest for
+further processing. Using the retrieved trending topics given in Table
+\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics.
+We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach.
+We have then evaluated the results
+with respect to several measures:
 

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

@@
 \begin{abstract}
-Search results on Twitter are hard to analyze and read.
-To facilitate understanding the meaning of a search term in the context of Twitter, we have developed a system which annotates search results with entities that best describe the search result, thus offering a means of quickly grasping the meaning of the search results and at the same time providing starting points for further exploration of the search results' context.
-In an evaluation we show that the entities used for annotation represent the tweet's content in a suitable manner and that the annotations remain stable over time, i.e.
+To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context.
+In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e.
 when executing the same search at different times, the same entities are returned.

### 2011-03-07 lids/twittersearchwrap/src/analysis/ExtractedInformationOfFile.java

@@ -1,0 +1,29 @@
+package analysis;
+
+import java.util.List;
+
+public class ExtractedInformationOfFile {
+int id;
+List<String> dbpedialinks;
+double avgtimebetweentweets;
+
+public int getId() {
+	return id;
+}
+public void setId(int id) {
+	this.id = id;
+}
+public List<String> getDbpedialinks() {
+	return dbpedialinks;
+}
+public void setDbpedialinks(List<String> dbpedialinks) {
+	this.dbpedialinks = dbpedialinks;
+}
+public double getAvgtimebetweentweets() {
+	return avgtimebetweentweets;
+}
+public void setAvgtimebetweentweets(double avgtimebetweentweets) {
+	this.avgtimebetweentweets = avgtimebetweentweets;
+}
+
+}

### 2011-03-07 trunk/lids/twittersearchwrap/src/analysis/StartAnalysis.java

@@ -1,0 +1,194 @@
+package analysis;
+
+import java.io.BufferedInputStream;
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.math.BigDecimal;
+import java.text.DateFormat;
+import java.text.ParseException;
+import java.text.SimpleDateFormat;
+import java.util.ArrayList;
+import java.util.Calendar;
+import java.util.Date;
+import java.util.List;
+
+public class StartAnalysis {
+
+	public static void main(String[] args) throws IOException{ 
+		
+		// Create list of file names in analysis/input folder
+
+		File dir1 = new File(".");
+		File file = new File(dir1.getCanonicalPath() + "/analysis/input" );
+
+	    File[] listOfFiles = file.listFiles();
+
+	    List<ExtractedInformationOfFile> extractedInformation = new ArrayList();
+	    
+    	// Import and analyze each existing file step by step, save results in object
+	    for (int i = 0; i < listOfFiles.length; i++) {
+	    	String thisFile = fileToString(listOfFiles[i]);
+	    	ExtractedInformationOfFile exFile = new ExtractedInformationOfFile();
+	    	exFile.setId(i);
+	    	
+	    	// Find all DBPedia links in current document
+	    	List<String> dbpedialinks = new ArrayList<String>();
+	    	String[] links = getStringBetweenString(thisFile, "<rdfs:seeAlso xmlns:rdfs=\"http://www.w3.org/2000/01/rdf-schema#\" rdf:resource=\"", "\"/>");
+	    	for(String link:links){
+	    		dbpedialinks.add(link);
+	    	}
+	    	exFile.setDbpedialinks(dbpedialinks);
+	    	
+	    	// Calculate avgTimeBetweenTweets in current document
+	    	String[] dates = getStringBetweenString(thisFile, "<dc:date xmlns:dc=\"http://purl.org/dc/elements/1.1/\">", "</dc:date>");
+	    	Long[] dateIntervalls = new Long[dates.length-1];
+	    	
+	        DateFormat rfcDateTimeUTCTZFormat = new SimpleDateFormat("yyyy'-'MM'-'dd'T'HH':'mm':'ss'Z'");
+    	    	    	
+	    	for(int j = 0; j < dates.length-1; j++){
+				try {
+					Date date1 = rfcDateTimeUTCTZFormat.parse(dates[j]);
[…]

### 2011-03-08 lids/twittersearchwrap/paper/paper.tex

@@
 
+\myremark{todo}{warum kein direktes Mapping auf dbpedia-Entitäten?}
+
 Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
@@
 
+\myremark{todo}{ergänzen: abkürzungen, verschmelzen von Wörtern}
+
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
@@
 \label{sect:relWork}
+
+\myremark{todo}{aufräumen!}
 
@@
 The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
-%uhe: System beschreiben
+
 Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
@@
 Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
-the message has been posted be furthermore known.
+the message has been posted are furthermore known.
 
@@
 
+  \myremark{todo}{ausführen}
 In our example, the message contains a link to
@@
 \end{enumerate}
-\myremark{Uta}{Gibt es was, was man zu Dublin Core zitieren kann?}
 
 \section{Implementation}
+
+\myremark{todo}{Wo ist das System zugreifbar?}
 
@@
 The optional step of dereferencing URLs which are posted in messages contained
-in the result set can be triggered using the option \texttt{extern=true}.
+in the result set can be triggered using the option \texttt{extern=true} in our system.
 To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first 50 words.
@@
 
-Topics trending worldwide and in Germany at Twitter retrieved on February 24th
+Topics trending worldwide and in Germany on Twitter retrieved on February 24th
 17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
@@
 
+\myremark{todo}{Deutsche Themen nicht ausgewertet wegen Sprachproblem}
+
 \subsection{Measures}
@@
 monitoring of recently posted messages matching the search term.
+\myremark{todo}{Nicht genau machbar wegen Zeitpunkt, wann Lookup gemacht werden soll, nicht bekannt}
 \end{itemize}
@@
 \begin{definition}[Evaluation Measures]
-Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, we define:
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, where each result set $R_i$ consists of twitter messages $r_i1,\ldots,r_iK$ with time stamps $t_i1,\ldots,t_iK$ we define:
 \begin{itemize}
-	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
-	A high $adt(q)$ means that new messages that match the query $q$ are not generated very often. If new messages matching the query $q$ are frequently published, then the $adt(q)$ is low.
-	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
-	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
+	\item The average update time within a result set $aut(R_i)$ for a query is the average time that lies between messages that match the query which produced the search result: $$aut(R_i)=\frac{\sum_{j=1}^{n}t_{i,j+1}-t_{i,j}}{K-1}$$
+	A high $aut(R)$ means that new messages that match the query are not generated very often. If new messages matching the query are frequently published, then the $adt(R)$ is low.
+
+	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query.
+E.g.
+if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
+%	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
+%	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
 On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
+	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
+$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
 	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
@@
 														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
-	Here again, a value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.
-	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
-$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
-	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
+	A value of $1$ means that the two sets of entities are identical, a value of $0$ means they are disjoint.
+
+	The variance of time stabilities $ts(q,t_i)$ over all $t_i$ helps to determine whether the rate at which the found entities change is rather stable or whether it is changing a lot over time.
 \end{itemize}
@@
 \myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+\myremark{todo}{Hypothesis: high average update time leads to stable results}
 

### 2011-03-08 trunk/lids/twittersearchwrap/paper/paper.tex
added list of hashtags

@@
 
-%\newcommand{\nop}[1]{}
+\newcommand{\nop}[1]{}
 
@@
 
+\nop{
+http://tagdef.com/ has a list of popular tags
+}
+
 \section{Introduction}
+
+\myremark{todo}{warum kein direktes Mapping auf dbpedia-Entitäten?}
 
@@
 Search Wrapper.
+
+We have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to
+2011-03-06.
+The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
+We then recorded search results for these 50 hashtags during the course of 24 hours (2011-03-07).
+
+\begin{table}[ht*]
+\centering
+\begin{tabular}{ l|l }
+Hashtag & Count  \\
+\hline
+ff &     460 \\
+np &     172 \\
+nowplaying &     144 \\
+winning &     134 \\
+fb &     105 \\
+rt &      83 \\
+mentionke &      61 \\
+blackpeoplemovies &      57 \\
+tigerblood &      56 \\
+thataintwinning &      53 \\
+fail &      53 \\
+teamfollowback &      52 \\
+iftwitterwashighschool &      51 \\
+bieberfact &      51 \\
+news &      46 \\
+jobs &      45 \\
+libya &      44 \\
+followmejp &      44 \\
+partiu &      41 \\
+sougofollow &      39 \\
+damnitstrue &      39 \\
+tilltheworldends &      37 \\
+soalcinta &      35 \\
+nicovideo &      35 \\
+quran &      33 
+\end{tabular}
+\begin{tabular}{ l|l }
+Hashtag & Count  \\
+\hline
+nw &      32 \\
+quote &      31 \\
+shoutout &      30 \\
+jfb &      30 \\
+carnaval &      27 \\
+tfb &      26 \\
+followme &      26 \\
+followfriday &      25 \\
+follow &      24 \\
+egypt &      23 \\
+retweet &      22 \\
+fact &      22 \\
+win &      20 \\
+tweetmyjobs &      20 \\
+music &      20 \\
+in &      20 \\
+imagine &      20 \\
+nowwatching &      19 \\
+cumannanyaindonesia &      19 \\
+twexit &      18 \\
+lcv &      18 \\
+fui &      18 \\
+bot &      18 \\
+nemuritsuzuketeshinu &      17 \\
+fato &      17 \\
+\end{tabular}
+\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
+\end{table}
 
@@
 \begin{itemize}
-\item Temporal Sliding Window: The query is executed and the n most
-recent results are retrieved every t minutes. The Temporal Sliding Window method
-may lead to duplicate messages in the retrieved documents, but needs to handle much less data and
-allows for an analysis over larger time frames.
-\item k-item Sliding Window: The k-item Sliding Window methods retrieves all
-messages that match the query exactly one time. Each time k new messages are
+\item {\bf Temporal Sliding Window}\newline The query is executed and the n
+most recent results are retrieved every t minutes. The Temporal Sliding Window
+method may lead to duplicate messages in the retrieved documents, but needs to
+handle much less data and allows for an analysis over larger time frames.
+\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
+retrieves all messages that match the query exactly one time. Each time k new messages are
 available matching the given query a document containing those k messages
@@
 
-Using the retrieved trending topics given in Table \ref{tbl:terms}
-as input queries for the evaluation, the set of queries was executed twice
-per hour using the Temporal Sliding Window method for data acquisition in a 24
-hour time frame starting from the moment the topics were identified as trending topics.  We have then evaluated the results with respect to several measures:
+We considered the trending topics on Twitter a good set of input queries for
+our evaluation approach. Trending topics often cover a variety of recently
+talked about topics which due to its recent nature may be of high interest for
+further processing. Using the retrieved trending topics given in Table
+\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics.
+We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach.
+We have then evaluated the results
+with respect to several measures:
 
 \begin{definition}[Evaluation Measures]
-Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, we define:
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, where each result set $R_i$ consists of twitter messages $r_i1,\ldots,r_iK$ with time stamps $t_i1,\ldots,t_iK$ we define:
 \begin{itemize}
-	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
-	A high $adt(q)$ means that new messages that match the query $q$ are not generated very often. If new messages matching the query $q$ are frequently published, then the $adt(q)$ is low.
-	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
-	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
+	\item The average update time within a result set $aut(R_i)$ for a query is the average time that lies between messages that match the query which produced the search result: $$aut(R_i)=\frac{\sum_{j=1}^{n}t_{i,j+1}-t_{i,j}}{K-1}$$
+	A high $aut(R)$ means that new messages that match the query are not generated very often. If new messages matching the query are frequently published, then the $adt(R)$ is low.
+
+	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query.
+E.g.
+if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
+%	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
+%	A value of $gs(q)$ of $1$ means that the set of entities is the same at each point in time $t_i$.
 On the other hand, a value of $0$ means that at least two of the sets of entities, with which the results were annotated, are disjoint.
+	\item The stability for a single term is defined as the fraction of result sets for a query $q$ in which it occurs: 
+$$sts(q,t)=\frac{|\{i|t\in E_i\}|}{n}$$
+	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
 	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:

### 2011-03-09 lids/twittersearchwrap/paper/paper.tex

@@
 
-\usepackage{fullpage}
+%\usepackage{fullpage}
 \usepackage{setspace}
@@
 
-\onehalfspacing
+%\onehalfspacing
 
@@
 In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e.
-when executing the same search at different times, the same entities are returned.
+when executing the same search at different times, the same encyclopedia entities are returned.
 \end{abstract}
@@
 
+\nop{
+http://tagdef.com/ has a list of popular tags
+}
+
 \section{Introduction}
-
-\myremark{todo}{warum kein direktes Mapping auf dbpedia-Entitäten?}
 
@@
 
-On Twitter it is possible to search for messages containing a specific term or hash tag.
-This search returns a fixed number of most recent messages containing the search term.
+On Twitter it is possible to search for messages containing a specific hash tag.
+This search returns a fixed number of most recent messages containing the tag.
 However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
@@
 
-\myremark{todo}{ergänzen: abkürzungen, verschmelzen von Wörtern}
-
 In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
@@
 Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
+Note however that a direct mapping of hash tags to entities is not possible in many cases: e.g.
+there is no entity in dbpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.
 
@@
 
-  \myremark{todo}{ausführen}
 In our example, the message contains a link to
@@
 \section{Implementation}
-
-\myremark{todo}{Wo ist das System zugreifbar?}
 
@@
 
+We have evaluated our approach to assess whether the entities which are found as related to a specific hash tag are useful and stable over time.
+
 \subsection{Setup}
 
-Topics trending worldwide and in Germany on Twitter retrieved on February 24th
-17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
-constitute a basis of input search terms for our evaluation of the Twitter
-Search Wrapper.
+We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}.
+Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.
 
@@
 \centering
-\begin{tabular}{ |l|l| }
+\begin{tabular}{ l }
+Trending Topics Worldwide  \\
 \hline
-\textsc{Trending Topic} & \textsc{Location}  \\
+\#goodlucknickj  \\
+\#smalljoys \\
+\#thingsthedevilinvented \\
+Adam Wainwright  \\
+CatchPetrovaFire \\
+Gadafi  \\
+Libia \\
+Precious Minaj \\
+Tommy John  \\
+\end{tabular}
+\begin{tabular}{l}
+Trending Topics Germany \\
 \hline
-\#goodlucknickj & Worldwide \\
-\#smalljoys & Worldwide \\
-\#thingsthedevilinvented & Worldwide \\
-Adam Wainwright & Worldwide \\
-CatchPetrovaFire & Worldwide \\
-Gadafi & Worldwide \\
-Libia & Worldwide \\
-Precious Minaj & Worldwide \\
-Tommy John & Worldwide \\
-\hline
-\#gaddafi & Germany \\
-\#guttenberg & Germany \\
-\#libya & Germany \\
-Doktorarbeit & Germany \\
-Gef\"{u}hl & Germany \\
-Lion & Germany \\
-MBP & Germany \\
-Thunderbolt & Germany \\
-Vorratsdatenspeicherung & Germany \\
-\hline
+\#gaddafi \\
+\#guttenberg  \\
+\#libya  \\
+Doktorarbeit \\
+Gef\"{u}hl  \\
+Lion  \\
+MBP \\
+Thunderbolt \\
+Vorratsdatenspeicherung \\
 \end{tabular}
@@
 
-\myremark{todo}{Deutsche Themen nicht ausgewertet wegen Sprachproblem}
+The second query set consists of hash tags that are frequently used on Twitter.
+To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06.
+The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
 
-\subsection{Measures}
+\begin{table}[ht*]
+\centering
+\begin{tabular}{ l|l }
+Hashtag & Count  \\
+\hline
+ff &     460 \\
+np &     172 \\
+nowplaying &     144 \\
+winning &     134 \\
+fb &     105 \\
+rt &      83 \\
+mentionke &      61 \\
+blackpeoplemovies &      57 \\
+tigerblood &      56 \\
+thataintwinning &      53 \\
+fail &      53 \\
+teamfollowback &      52 \\
+iftwitterwashighschool &      51 \\
+bieberfact &      51 \\
+news &      46 \\
+jobs &      45 \\
+libya &      44 \\
+followmejp &      44 \\
+partiu &      41 \\
+sougofollow &      39 \\
+damnitstrue &      39 \\
+tilltheworldends &      37 \\
+soalcinta &      35 \\
+nicovideo &      35 \\
+quran &      33 
+\end{tabular}
+\begin{tabular}{ l|l }
+Hashtag & Count  \\
+\hline
+nw &      32 \\
+quote &      31 \\
+shoutout &      30 \\
+jfb &      30 \\
+carnaval &      27 \\
+tfb &      26 \\
+followme &      26 \\
+followfriday &      25 \\
+follow &      24 \\
+egypt &      23 \\
+retweet &      22 \\
+fact &      22 \\
+win &      20 \\
+tweetmyjobs &      20 \\
+music &      20 \\
+in &      20 \\
+imagine &      20 \\
+nowwatching &      19 \\
+cumannanyaindonesia &      19 \\
+twexit &      18 \\
+lcv &      18 \\
+fui &      18 \\
+bot &      18 \\
+nemuritsuzuketeshinu &      17 \\
+fato &      17 \\
+\end{tabular}
+\caption{Popular hashtags sampled during a three-day period.}\label{tbl:hashtags}
+\end{table}
 
-The goal of our evaluation was to examine the stability of the entity
-annotations over time. To achieve this, we have repeatedly executed the same set
-of queries and saved the returned data. Two methods for this data acquisition
-were identified: \begin{definition}[Data Acquisition Methods]
+The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries and analysed the returned data.
+
+In principle, two methods for data acquisition were identified: \begin{definition}[Data Acquisition Methods]
 \begin{itemize}
@@
 handle much less data and allows for an analysis over larger time frames.
-\item {\bf k-item Sliding Window}\newline  The k-item Sliding Window methods
+\item {\bf $k$-item Sliding Window}\newline  The k-item Sliding Window methods
 retrieves all messages that match the query exactly one time. Each time k new messages are
@@
 monitoring of recently posted messages matching the search term.
-\myremark{todo}{Nicht genau machbar wegen Zeitpunkt, wann Lookup gemacht werden soll, nicht bekannt}
 \end{itemize}
@@
 
-We considered the trending topics on Twitter a good set of input queries for
-our evaluation approach. Trending topics often cover a variety of recently
-talked about topics which due to its recent nature may be of high interest for
-further processing. Using the retrieved trending topics given in Table
-\ref{tbl:terms} as input queries for the evaluation, the set of queries was executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame starting from the moment the topics were identified as trending topics.
-We chose the Temporal Sliding Window method for data acquisition because of the expected data volume generated by trending topics as search terms and the long term nature of our evaluation approach.
-We have then evaluated the results
-with respect to several measures:
+The disadvantage of the first method is that it is neither possible to guarantee that all messages matching the search are collected, nor is it possible to avoid overlaps between the search results.
+However, while the second method seems to overcome these problems, it does not: Using the $k$-item sliding window method, it is not clear when the next search result should be fetched: even when frequently querying for new messages, if updates are frequent it is likely to lack messages in the result set.
+
+For both data set queries were executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame.
+Data for the trending topics was collected on 2011-02-24, for the frequent hash tags data was collected on 2011-03-07.
+
+\subsection{Measures}
+
+For analysing the collected data, several measures were defined:
 

### 2011-03-09 trunk/lids/twittersearchwrap/src/com/ontologycentral/analysis/ExtractedInformationOfFile.java

@@ -1,0 +1,36 @@
+package analysis;
+
+import java.util.List;
+
+public class ExtractedInformationOfFile {
+int id;
+List<String> entities;
+double avgtimebetweentweets;
+double timestability;
+
+public int getId() {
+	return id;
+}
+public void setId(int id) {
+	this.id = id;
+}
+public double getAvgtimebetweentweets() {
+	return avgtimebetweentweets;
+}
+public void setAvgtimebetweentweets(double avgtimebetweentweets) {
+	this.avgtimebetweentweets = avgtimebetweentweets;
+}
+public double getTimestability() {
+	return timestability;
+}
+public void setTimestability(double timestability) {
+	this.timestability = timestability;
+}
+public List<String> getEntities() {
+	return entities;
+}
+public void setEntities(List<String> entities) {
+	this.entities = entities;
+}
+
+}

### 2011-03-09 trunk/lids/twittersearchwrap/src/com/ontologycentral/analysis/Start.java

@@ -1,0 +1,364 @@
+package analysis;
+
+import java.io.BufferedInputStream;
+import java.io.BufferedWriter;
+import java.io.File;
+import java.io.FileInputStream;
+import java.io.FileWriter;
+import java.io.IOException;
+import java.math.BigDecimal;
+import java.text.DateFormat;
+import java.text.ParseException;
+import java.text.SimpleDateFormat;
+import java.util.ArrayList;
+import java.util.Date;
+import java.util.HashSet;
+import java.util.Iterator;
+import java.util.List;
+
+public class Start {
+	public static void main(String[] args) throws Exception {
+
+		List<Hashtag> hashtags = new ArrayList();
+		
+		// Read all URIs - Saved in textfile in input folder
+		File dir = new File(".");
+		File file0 = new File(dir.getCanonicalPath() + "/analysis/input/uris.txt" );
+	    String uristxt = fileToString(file0);
+		String[] uri = uristxt.split(";");
+		//
+		
+		// Create list of file names in analysis/input folder
+		File file = new File(dir.getCanonicalPath() + "/analysis/input" );
+	    File[] listOfFiles = file.listFiles();
+	    
+		for(int i = 0; i<uri.length; i++){
+			
+			// Find documents for URI
+			List<File> listOfFilesHashtag = new ArrayList();
+			List<File> listOfFilesHashtagExtern = new ArrayList();
+			
+			for(int j = 0; j<listOfFiles.length;j++){
+				if (listOfFiles[j].getAbsolutePath().contains(uri[i])){
+					if(listOfFiles[j].getAbsolutePath().contains("extern=true")) {
+						listOfFilesHashtagExtern.add(listOfFiles[j]);
+						}else{
+							listOfFilesHashtag.add(listOfFiles[j]);
+					}
+				}
+			}
+
+			// Split analysis in extern=true and extern=false
+			// Analysis for extern=false
+			Iterator fileIt = listOfFilesHashtag.iterator();
+			ExtractedInformationOfFile[] exFiles = new ExtractedInformationOfFile[listOfFilesHashtag.size()];
+			int count = 0;
+			while(fileIt.hasNext()){
+				try{
+				String thisFile = fileToString((File) fileIt.next());
[…]

### 2011-03-09 lids/twittersearchwrap/src/com/ontologycentral/analysis/Entities.java

@@ -1,0 +1,5 @@
+package analysis;
+
+public class Entities {
+
+}

### 2011-03-09 lids/twittersearchwrap/src/com/ontologycentral/analysis/Entity.java

@@ -1,0 +1,19 @@
+package analysis;
+
+public class Entity {
+String name;
+double prob;
+
+public String getName() {
+	return name;
+}
+public void setName(String name) {
+	this.name = name;
+}
+public double getProb() {
+	return prob;
+}
+public void setProb(double prob) {
+	this.prob = prob;
+}
+}

### 2011-03-09 lids/twittersearchwrap/src/com/ontologycentral/analysis/Hashtag.java

@@ -1,0 +1,77 @@
+package analysis;
+
+import java.util.List;
+
+public class Hashtag {
+	String name;
+	List<ExtractedInformationOfFile> files;
+	double avgavgtimebetweentweets;
+	double varavgtimebetweentweets;
+	double avgtimestability;
+	double avgtimestabilityEXT;
+	double vartimestability;
+	double vartimestabilityEXT;
+	List<Entity> entities;
+	List<Entity> entitiesEXT;
+	
+	public String getName() {
+		return name;
+	}
+	public void setName(String name) {
+		this.name = name;
+	}
+	public List<ExtractedInformationOfFile> getFiles() {
+		return files;
+	}
+	public void setFiles(List<ExtractedInformationOfFile> files) {
+		this.files = files;
+	}
+	public double getAvgavgtimebetweentweets() {
+		return avgavgtimebetweentweets;
+	}
+	public void setAvgavgtimebetweentweets(double avgavgtimebetweentweets) {
+		this.avgavgtimebetweentweets = avgavgtimebetweentweets;
+	}
+	public double getAvgtimestability() {
+		return avgtimestability;
+	}
+	public void setAvgtimestability(double avgtimestability) {
+		this.avgtimestability = avgtimestability;
+	}
+	public List<Entity> getEntities() {
+		return entities;
+	}
+	public void setEntities(List<Entity> entities) {
+		this.entities = entities;
+	}
+	public double getAvgtimestabilityEXT() {
+		return avgtimestabilityEXT;
+	}
+	public void setAvgtimestabilityEXT(double avgtimestabilityEXT) {
+		this.avgtimestabilityEXT = avgtimestabilityEXT;
+	}
+	public List<Entity> getEntitiesEXT() {
+		return entitiesEXT;
+	}
+	public void setEntitiesEXT(List<Entity> entitiesEXT) {
+		this.entitiesEXT = entitiesEXT;
+	}
+	public double getVartimestability() {
+		return vartimestability;
+	}
+	public void setVartimestability(double vartimestability) {
+		this.vartimestability = vartimestability;
+	}
+	public double getVartimestabilityEXT() {
+		return vartimestabilityEXT;
+	}
+	public void setVartimestabilityEXT(double vartimestabilityEXT) {
+		this.vartimestabilityEXT = vartimestabilityEXT;
+	}
+	public double getVaravgtimebetweentweets() {
+		return varavgtimebetweentweets;
+	}
[…]

### 2011-03-09 trunk/lids/twittersearchwrap/src/com/ontologycentral/analysis/Start.java

@@ -118,12 +118,16 @@ public class Start {
 		    		while(entityItOld.hasNext()){
 		    			allEntities.add((String)entityItOld.next());
 		    		}
-		    		timestability = helpersum/allEntities.size();
-			    	// Delete decimals
-			    	int decimalPlace3 = 3;
-			    	BigDecimal bd2 = new BigDecimal(timestability);
-			    	bd2 = bd2.setScale(decimalPlace3,BigDecimal.ROUND_HALF_UP);
-			    	timestability = bd2.doubleValue();
+		    		if(allEntities.size()!=0){
+		    			timestability = helpersum/Double.valueOf(allEntities.size());
+			    		// Delete decimals
+			    		int decimalPlace3 = 3;
+			    		BigDecimal bd2 = new BigDecimal(timestability);
+			    		bd2 = bd2.setScale(decimalPlace3,BigDecimal.ROUND_HALF_UP);
+			    		timestability = bd2.doubleValue();
+		    		}else{
+		    			timestability=0;
+		    		}
 			    	
 			    	exFile.setTimestability(timestability);
 		    	}
@@ -172,12 +176,16 @@ public class Start {
 		    		while(entityItOld.hasNext()){
 		    			allEntities.add((String)entityItOld.next());
 		    		}
-		    		timestability = helpersum/allEntities.size();
-			    	// Delete decimals
-			    	int decimalPlace3 = 3;
-			    	BigDecimal bd2 = new BigDecimal(timestability);
-			    	bd2 = bd2.setScale(decimalPlace3,BigDecimal.ROUND_HALF_UP);
-			    	timestability = bd2.doubleValue();
+		    		if(allEntities.size()!=0){
+		    			timestability = helpersum/Double.valueOf(allEntities.size());
+			    		// Delete decimals
+			    		int decimalPlace3 = 3;
+			    		BigDecimal bd2 = new BigDecimal(timestability);
+			    		bd2 = bd2.setScale(decimalPlace3,BigDecimal.ROUND_HALF_UP);
+			    		timestability = bd2.doubleValue();
+		    		}else{
+		    			timestability=0;
+		    		}
 			    	
 			    	exFileEXT.setTimestability(timestability);
 		    	}

### 2011-03-10 lids/twittersearchwrap/src/com/ontologycentral/analysis/Entities.java

@@ -1,5 +1,0 @@
-package analysis;
-
-public class Entities {
-
-}

### 2011-03-10 lids/twittersearchwrap/src/com/ontologycentral/analysis/Hashtag.java

@@ -11,6 +11,8 @@ public class Hashtag {
 	double avgtimestabilityEXT;
 	double vartimestability;
 	double vartimestabilityEXT;
+	int n;
+	int nEXT;
 	List<Entity> entities;
 	List<Entity> entitiesEXT;
 	
@@ -73,5 +75,17 @@ public class Hashtag {
 	}
 	public void setVaravgtimebetweentweets(double varavgtimebetweentweets) {
 		this.varavgtimebetweentweets = varavgtimebetweentweets;
+	}
+	public int getN() {
+		return n;
+	}
+	public void setN(int n) {
+		this.n = n;
+	}
+	public int getnEXT() {
+		return nEXT;
+	}
+	public void setnEXT(int nEXT) {
+		this.nEXT = nEXT;
 	}
 }

### 2011-03-10 lids/twittersearchwrap/src/com/ontologycentral/analysis/Start.java

@@ -32,6 +32,15 @@ public class Start {
 		File file = new File(dir.getCanonicalPath() + "/analysis/input" );
 	    File[] listOfFiles = file.listFiles();
 	    
+		StringBuffer csvString = new StringBuffer();
+		csvString.append("Hashtag;N;N[EXT];E(aut);VAR(aut);E(ts);VAR(ts);E(ts)[EXT];VAR(ts)[EXT];");
+		csvString.append("Entity 1; sts(Entity 1);Entity 2; sts(Entity 2);Entity 3; sts(Entity 3);Entity 4; sts(Entity 4);Entity 5; sts(Entity 5);");
+		csvString.append("Entity 1[EXT]; sts(Entity 1)[EXT];Entity 2[EXT]; sts(Entity 2)[EXT];Entity 3[EXT]; sts(Entity 3)[EXT];Entity 4[EXT]; sts(Entity 4)[EXT];Entity 5[EXT]; sts(Entity 5)[EXT];");
+		csvString.append("\n");
+    	BufferedWriter out = new BufferedWriter(new FileWriter(dir.getCanonicalPath() + "/analysis/analysis.csv"));
+    	out.write(csvString.toString().replace(".", ","));
+    	out.close();
+    	
 		for(int i = 0; i<uri.length; i++){
 			
 			// Find documents for URI
@@ -39,7 +48,7 @@ public class Start {
 			List<File> listOfFilesHashtagExtern = new ArrayList();
 			
 			for(int j = 0; j<listOfFiles.length;j++){
-				if (listOfFiles[j].getAbsolutePath().contains(uri[i])){
+				if (listOfFiles[j].getAbsolutePath().contains(uri[i]+".")||listOfFiles[j].getAbsolutePath().contains(uri[i]+"&extern")){
 					if(listOfFiles[j].getAbsolutePath().contains("extern=true")) {
 						listOfFilesHashtagExtern.add(listOfFiles[j]);
 						}else{
@@ -55,7 +64,7 @@ public class Start {
 			int count = 0;
 			while(fileIt.hasNext()){
 				try{
-				String thisFile = fileToString((File) fileIt.next());
+				String thisFile = new String(fileToString((File) fileIt.next()));
 				ExtractedInformationOfFile exFile = new ExtractedInformationOfFile();
 		    	// Find all DBPedia links in current document
 		    	List<String> entities = new ArrayList<String>();
@@ -66,6 +75,11 @@ public class Start {
 		    	exFile.setEntities(entities);
[…]

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 
-\myremark{todo}{warum kein direktes Mapping auf dbpedia-Entitäten?}
-
 Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
@@
 
-The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
-The corpus contains evaluation results solicited via Mechanical Turk.
-In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
-@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?
-
-Softic et al \cite{key:softic} have developed a framework and system for mining
-data from social networks.
-They have instantiated their system to analyze data from Twitter.
-In their system, they collect data from one or several users.
-The system by Passant et al.
-\cite{key:smob} is used for transforming twitter data to semantic data.
-The triplified data can then be analysed using SPARQL.
-They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
-Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
-As such, our approach is closely related.
-Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
-% from stakovic et al.
-%In order to make tweets more searchable and make them useful for the described
-%scenario one would need to have represent them in a structured format and associate
-%those tweets with the topics that refer to. As a basic approach we process the text of
-%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
-%concepts related to a tweet, but is useful only on a limited number of tweets directly
-%mentioning a particular topic. In the example data set we produced from ESWC2010,
-%tweet topics are represented using dc:subject property.
-
-Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
-The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
-The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
-
-Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
-We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
-
 Passant et al.
@@
 The system by Passant et al.
-\cite{key:smob} is used for transforming Twitter data to semantic data.
+\cite{key:smob} is used for transforming twitter data to semantic data.
 The triplified data can then be analysed using SPARQL.
-They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
+They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
+
+Relating semantic concepts with twitter messages has been attempted by various authors:
+Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
+% from stakovic et al.
+%In order to make tweets more searchable and make them useful for the described
+%scenario one would need to have represent them in a structured format and associate
+%those tweets with the topics that refer to. As a basic approach we process the text of
+%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+%concepts related to a tweet, but is useful only on a limited number of tweets directly
+%mentioning a particular topic. In the example data set we produced from ESWC2010,
+%tweet topics are represented using dc:subject property.
+Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
+
+Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.
+
+Kinsella et al.
+\cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
+We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
+
+The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
+The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
 
@@
 
+We have evaluated our approach to assess whether the entities which are found as related to a specific hash tag are useful and stable over time.
+
 \subsection{Setup}
 
-Topics trending worldwide and in Germany on Twitter retrieved on February 24th
-17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
-constitute a basis of input search terms for our evaluation of the Twitter
-Search Wrapper.
+We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}.
+Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.
 
-We have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to
-2011-03-06.
+\begin{table}[ht*]
+\centering
+\begin{tabular}{ l }
+Trending Topics Worldwide  \\
+\hline
+\#goodlucknickj  \\
+\#smalljoys \\
+\#thingsthedevilinvented \\
+Adam Wainwright  \\
+CatchPetrovaFire \\
+Gadafi  \\
+Libia \\
+Precious Minaj \\
+Tommy John  \\
+\end{tabular}
+\begin{tabular}{l}
+Trending Topics Germany \\
+\hline
+\#gaddafi \\
+\#guttenberg  \\
+\#libya  \\
+Doktorarbeit \\
+Gef\"{u}hl  \\
+Lion  \\
+MBP \\
+Thunderbolt \\
+Vorratsdatenspeicherung \\
+\end{tabular}
+\caption{Search terms}\label{tbl:terms}
+\end{table}
+
+The second query set consists of hash tags that are frequently used on Twitter.
+To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06.
 The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
-We then recorded search results for these 50 hashtags during the course of 24 hours (2011-03-07).
 
@@
 
-\begin{table}[ht*]
-\centering
-\begin{tabular}{ |l|l| }
-\hline
-\textsc{Trending Topic} & \textsc{Location}  \\
-\hline
-\#goodlucknickj & Worldwide \\
-\#smalljoys & Worldwide \\
-\#thingsthedevilinvented & Worldwide \\
-Adam Wainwright & Worldwide \\
-CatchPetrovaFire & Worldwide \\
-Gadafi & Worldwide \\
-Libia & Worldwide \\
-Precious Minaj & Worldwide \\
-Tommy John & Worldwide \\
-\hline
-\#gaddafi & Germany \\
-\#guttenberg & Germany \\
-\#libya & Germany \\
-Doktorarbeit & Germany \\
-Gef\"{u}hl & Germany \\
-Lion & Germany \\
-MBP & Germany \\
-Thunderbolt & Germany \\
-Vorratsdatenspeicherung & Germany \\
-\hline
-\end{tabular}
-\caption{Search terms}\label{tbl:terms}
-\end{table}
+The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries and analysed the returned data.
 
-\myremark{todo}{Deutsche Themen nicht ausgewertet wegen Sprachproblem}
-
-\subsection{Measures}
-
-The goal of our evaluation was to examine the stability of the entity
-annotations over time. To achieve this, we have repeatedly executed the same set
-of queries and saved the returned data. Two methods for this data acquisition
-were identified: \begin{definition}[Data Acquisition Methods]
+In principle, two methods for data acquisition were identified: \begin{definition}[Data Acquisition Methods]
 \begin{itemize}

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 \centering
-\begin{tabular}{ l|l }
-Hashtag & Count  \\
+\begin{tabular}{ l|l|l|l|l|l|l|l|l }
+Hashtag & Count & $N_{ext}$ & $E(aut)$ & $Var(aut)$ & $E(ts)$ & $Var(ts)$ & $E(ts_{ext}$ & $Var(ts_{ext})$\\
 \hline
-ff &     460 \\
-np &     172 \\
-nowplaying &     144 \\
-winning &     134 \\
-fb &     105 \\
-rt &      83 \\
-mentionke &      61 \\
-blackpeoplemovies &      57 \\
-tigerblood &      56 \\
-thataintwinning &      53 \\
-fail &      53 \\
-teamfollowback &      52 \\
-iftwitterwashighschool &      51 \\
-bieberfact &      51 \\
-news &      46 \\
-jobs &      45 \\
-libya &      44 \\
-followmejp &      44 \\
-partiu &      41 \\
-sougofollow &      39 \\
-damnitstrue &      39 \\
-tilltheworldends &      37 \\
-soalcinta &      35 \\
-nicovideo &      35 \\
-quran &      33 
-\end{tabular}
-\begin{tabular}{ l|l }
-Hashtag & Count  \\
-\hline
-nw &      32 \\
-quote &      31 \\
-shoutout &      30 \\
-jfb &      30 \\
-carnaval &      27 \\
-tfb &      26 \\
-followme &      26 \\
-followfriday &      25 \\
-follow &      24 \\
-egypt &      23 \\
-retweet &      22 \\
-fact &      22 \\
-win &      20 \\
-tweetmyjobs &      20 \\
-music &      20 \\
-in &      20 \\
-imagine &      20 \\
-nowwatching &      19 \\
-cumannanyaindonesia &      19 \\
-twexit &      18 \\
-lcv &      18 \\
-fui &      18 \\
-bot &      18 \\
-nemuritsuzuketeshinu &      17 \\
-fato &      17 \\
+ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
+np &     172 & 48 & 0,4737 & 0,0287 & 0,0655 & 0,0196 & 0,0717 & 0,0195\\
+nowplaying & 144 & 17 & 0,4514 & 0,0251 & 0,0565 & 0,0198 & 0,0458 & 0,0212 \\
+winning &     134 & 48 & 0,8236 & 0,2365 & 0,1101 & 0,0666 & 0,1816 & 0,0272 \\
+fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & 0.0208 & 0.0204 \\
+rt & 83 & 48 & 1,7980 & 3,7309 & 0,0979 & 0,0763 & 0,1487 & 0,0267 \\
+mentionke & 61 & 48 & 7,5459 & 195,6829 & 0,1406 & 0,0921 & 0,2215 & 0,0408 \\
+blackpeoplemovies & 57 & 90,6195 & 2007,5551 & 0,3327 & 0,0606 & 0,0349 & 0,0244\\
+tigerblood & 56 & 48 & 3,4029 & 4,8740 & 0,1497 & 0,0692 & 0,2330 & 0,0278 \\
+thataintwinning & 53 & 48 & 16,8075 & 236,8694 & 0,0768 & 0,0435 & 0,1668 & 0,0387 \\
+fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
+teamfollowback & 52 & 48 & 0,9269 & 0,4871 & 0,1912 & 0,0932 & 0,1813 & 0,0245 \\
+iftwitterwashighschool & 51 & 48 & 114,8342 & 1771,4564 & 0,5113 & 0,0405 & 0,5144 & 0,0352 \\
+bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765\\
+news & 46 & 0 & 1,8696 & 0,1943 & 0,1024 & 0,0210 & 0,0000 & 0,0000  \\
+jobs & 45 & 0 & 1,3866 & 0,4198 & 0,1006 & 0,0192 & 0,0000 & 0,0000 \\
+libya & 44 & 1 & 16,0309 & 117,2024 & 0,2701 & 0,0427 & 0,0208 & 0,0204 \\
+followmejp & 44 & 0	& 1,5398 & 0,1255 & 0,0688 & 0,0410 & 0,0000 & 0,0000\\
+partiu & 41 & 48 & 7,5809 & 84,0531 & 0,6042 & 0,2391 & 0,5313 & 0,2438 \\
+sougofollow & 39 & 0 & 2,1010 & 0,1820 & 0,0720 & 0,0427 & 0,0000 & 0,0000 \\
+damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
+tilltheworldends & 37 & 48 & 85,4526 & 1366,8588 & 0,5682 & 0,0709 & 0,5116 & 0,0324 \\
+soalcinta & 35 & 48 & 8,4143 & 103,7817 & 0,3451 & 0,1987 & 0,3120 & 0,2014 \\
+nicovideo & 35 & 0	51,0720 & 5521,3529 & 0,3604 & 0,1893 & 0,0000 & 0,0000 \\
+quran & 33 & 48 & 45,8290 & 90,4157 & 0,4271 & 0,0501 & 0,4188 & 0,0387 \\
+%\end{tabular}
+%\begin{tabular}{ l|l|l|l|l|l|l|l|l }
+%Hashtag & Count  \\
+%\hline
+nw & 32 & 48 & 2,6054 & 2,1094 & 0,0672 & 0,0231 & 0,0901 & 0,0418 \\
+quote & 31 & 48 & 4,3007 & 0,5706 & 0,1074 & 0,0197 & 0,1012 & 0,0212 \\
+shoutout & 30 & 48 & 2,6030 & 3,3256 & 0,2347 & 0,0987 & 0,2526 & 0,0488 \\
+jfb & 30 & 48 & 23,9911 & 1453,3113 & 0,2483 & 0,1654 & 0,2158 & 0,1379 \\
+carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
+tfb & 26 & 48 & 2,5994 & 0,8777 & 0,2292 & 0,1766 & 0,1760 & 0,0319 \\
+followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	0.0000 &	0.0000 \\
+followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
+follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
+egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
+retweet & 22 & 48	4,6991 & 13,4434 & 0,1570 & 0,1232 & 0,1353 & 0,0306 \\
+fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
+win & 20 & 0 & 4,2949 & 5,1856 & 0,0347 & 0,0221 & 0,0000 & 0,0000 \\
+tweetmyjobs & 20 & 0 & 35,5697 & 1590,6997 & 0,3244 & 0,0621 & 0,0000 & 0,0000 \\
+music & 20 & 1 & 4,4665 & 4,6392 & 0,0833 & 0,0196 & 0,0208 & 0,0204 \\
+in & 20 & 3	8,2367 & 6,8944 & 0,0649 & 0,0236 & 0,0251 & 0,0206 \\
+imagine & 20 & 48	& 8,3378 & 30,4317 & 0,2465 & 0,1759 & 0,1813 & 0,1375 \\
+nowwatching & 19 & 48 & 7,9110 & 8,6833 & 0,0672 & 0,0214 & 0,1293 & 0,0211 \\
+cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
+twexit & 18 & 48 & 12,5672 & 255,8178 & 0,3125 & 0,2148 & 0,2417 & 0,1783 \\
+lcv & 18 & 48 & 28,6309 & 477,9193 & 0,4236 & 0,2395 & 0,2813 & 0,1969 \\
+fui & 18 & 48 & 11,5515 & 165,3850 & 0,4896 & 0,2447 & 0,4635 & 0,2448 \\
+bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & 0.0208 & 0.0204  \\
+nemuritsuzuketeshinu & 17 & 48 & 314,1120 & 25053,5657 & 1,0000 & 0,0000 & 1,0000 & 0,0000 \\
+fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
 \end{tabular}

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

--- 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex
@@
 \label{sect:relWork}
-
-\myremark{todo}{aufräumen!}
 
@@
 To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06.
-The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}.
+The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}, count is the number of times we encountered them during the collection period.
 
@@
 \centering
-\begin{tabular}{ l|l }
-Hashtag & Count  \\
+\begin{tabular}{ l|l|l|l|l|l|l|l|l }
+Hashtag & Count & $N_{ext}$ & $E(aut)$ & $Var(aut)$ & $E(ts)$ & $Var(ts)$ & $E(ts_{ext})$ & $Var(ts_{ext})$\\
 \hline
-ff &     460 \\
-np &     172 \\
-nowplaying &     144 \\
-winning &     134 \\
-fb &     105 \\
-rt &      83 \\
-mentionke &      61 \\
-blackpeoplemovies &      57 \\
-tigerblood &      56 \\
-thataintwinning &      53 \\
-fail &      53 \\
-teamfollowback &      52 \\
-iftwitterwashighschool &      51 \\
-bieberfact &      51 \\
-news &      46 \\
-jobs &      45 \\
-libya &      44 \\
-followmejp &      44 \\
-partiu &      41 \\
-sougofollow &      39 \\
-damnitstrue &      39 \\
-tilltheworldends &      37 \\
-soalcinta &      35 \\
-nicovideo &      35 \\
-quran &      33 
-\end{tabular}
-\begin{tabular}{ l|l }
-Hashtag & Count  \\
-\hline
-nw &      32 \\
-quote &      31 \\
-shoutout &      30 \\
-jfb &      30 \\
-carnaval &      27 \\
-tfb &      26 \\
-followme &      26 \\
-followfriday &      25 \\
-follow &      24 \\
-egypt &      23 \\
-retweet &      22 \\
-fact &      22 \\
-win &      20 \\
-tweetmyjobs &      20 \\
-music &      20 \\
-in &      20 \\
-imagine &      20 \\
-nowwatching &      19 \\
-cumannanyaindonesia &      19 \\
-twexit &      18 \\
-lcv &      18 \\
-fui &      18 \\
-bot &      18 \\
-nemuritsuzuketeshinu &      17 \\
-fato &      17 \\
+ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
+np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
+nowplaying & 144 & 17 & 0.4514 & 0.0251 & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
+winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
+fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & 0.0208 & 0.0204 \\
+rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
+mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
+blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
+tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
+thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
+fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
+teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
+iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
+bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
+news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & 0.0000 & 0.0000  \\
+jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & 0.0000 & 0.0000 \\
+libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & 0.0208 & 0.0204 \\
+followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & 0.0000 & 0.0000\\
+partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
+sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & 0.0000 & 0.0000 \\
+damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
+tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
+soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
+nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & 0.0000 & 0.0000 \\
+quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
+%\end{tabular}
+%\begin{tabular}{ l|l|l|l|l|l|l|l|l }
+%Hashtag & Count  \\
+%\hline
+nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
+quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
+shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
+jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
+carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
+tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
+followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	0.0000 &	0.0000 \\
+followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
+follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
+egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
+retweet & 22 & 48 & 4.6991 & 13.4434 & 0.1570 & 0.1232 & 0.1353 & 0.0306 \\
+fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
+win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & 0.0000 & 0.0000 \\
+tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & 0.0000 & 0.0000 \\
+music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & 0.0208 & 0.0204 \\
+in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & 0.0251 & 0.0206 \\
+imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
+nowwatching & 19 & 48 & 7.9110 & 8.6833 & 0.0672 & 0.0214 & 0.1293 & 0.0211 \\
+cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
+twexit & 18 & 48 & 12.5672 & 255.8178 & 0.3125 & 0.2148 & 0.2417 & 0.1783 \\
+lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
+fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & 0.2447 & 0.4635 & 0.2448 \\
+bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & 0.0208 & 0.0204  \\
+nemuritsuzuketeshinu & 17 & 48 & 314.1120 & 25053.5657 & 1.0000 & 0.0000 & 1.0000 & 0.0000 \\
+fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
 \end{tabular}
@@
 	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
-	$$ts(q,t_i)=\begin{cases} |E_i| & i=1 \\
+	$$ts(q,t_i)=\begin{cases} 1 & i=1 \\
 														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
@@
 
-\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}.
+In total, we have analysed 48 result sets for each of the query tags.
+However, in some cases, the analysis which includes the content of external web pages led to a timeout of the Wikifier.
+$N_{ext}$ gives the number of result sets which we could analyse when the external content is included.
+$E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets.
+A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent.
+In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e.
+approximately $5$ minutes.
+In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed.
+Note that this value is only an average and does not guarantee disjointness of the result sets, as high update frequencies in one result set may outweigh low update frequencies in other result sets.
+Thus, we have additionally analysed the variance of the $aut$s.
+A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly.
+In general, higher average update times are associated with a higher variance in the update times.
+In some cases however, the variance of the average update time is surprisingly low when the mean average update time is rather high: this is e.g.
+the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$.
+For these tags updates came at a relatively regular level.
+
+We also report the average time stability over all time points as well as the variance for each hash tag.
+A high time stability indicates that more or less the same entities were used for annotation at all times.
+The high stability of $1$ was achieved for the tag $\#nemuritsuzuketeshinu$, because no entities could be associated with the results of this search.
+This can be explained as the tag is only used by Japanese twitter users in Japanese twitter messages.
+However, the Wikifier analyses the content of the results as being English text.
+A similar problem was encountered when analysing the trending topics in Germany.
+We assumed that these topics would mostly be tweeted about in German and thus called the German version of the Wikifier when analysing the results.
+However, it turned out that although the topics were trending in Germany, the tags were also used in messages in other languages.
+
+Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages.
+
+The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
+Accordingly, the entities which were most frequently used for annotation are "Britney Spears" ($95.83\%$), "iTunes" ($68.75\%$), "itunes" ($62.5\%$), "Itunes" ($31.25\%$), "Madonna\_(entertainer)" ($16.6\%$).
+The values in brackets indicate the single term stabilities for each of the terms.
+\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt?}
+
+%\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
 \myremark{todo}{Hypothesis: high average update time leads to stable results}

### 2011-03-10 lids/twittersearchwrap/paper/paper.tex

@@
 
-\myremark{todo}{aufräumen!}
-
 Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
@@
 Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
-
-The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
-The corpus contains evaluation results solicited via Mechanical Turk.
-In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
-@@@even with hashtags we have ambiguity, how would be map Twitter message containing the keyword ``apple''?
-
-Softic et al \cite{key:softic} have developed a framework and system for mining
-data from social networks.
-They have instantiated their system to analyze data from Twitter.
-In their system, they collect data from one or several users.
-The system by Passant et al.
-\cite{key:smob} is used for transforming twitter data to semantic data.
-The triplified data can then be analysed using SPARQL.
-They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
-Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
-As such, our approach is closely related.
-Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
-% from stakovic et al.
-%In order to make tweets more searchable and make them useful for the described
-%scenario one would need to have represent them in a structured format and associate
-%those tweets with the topics that refer to. As a basic approach we process the text of
-%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
-%concepts related to a tweet, but is useful only on a limited number of tweets directly
-%mentioning a particular topic. In the example data set we produced from ESWC2010,
-%tweet topics are represented using dc:subject property.
-
-Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
-The system we use for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
-The so-called Wikifier maps text to Wikipedia pages, which in turn directly map to DBpedia URIs.
-
-Kinsella et al. \cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
-We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
 
@@
 
-\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}.
+In total, we have analysed 48 result sets for each of the query tags.
+However, in some cases, the analysis which includes the content of external web pages led to a timeout of the Wikifier.
+$N_{ext}$ gives the number of result sets which we could analyse when the external content is included.
+$E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets.
+A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent.
+In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e.
+approximately $5$ minutes.
+In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed.
+Note that this value is only an average and does not guarantee disjointness of the result sets, as high update frequencies in one result set may outweigh low update frequencies in other result sets.
+Thus, we have additionally analysed the variance of the $aut$s.
+A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly.
+In general, higher average update times are associated with a higher variance in the update times.
+In some cases however, the variance of the average update time is surprisingly low when the mean average update time is rather high: this is e.g.
+the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$.
+For these tags updates came at a relatively regular level.
+
+We also report the average time stability over all time points as well as the variance for each hash tag.
+A high time stability indicates that more or less the same entities were used for annotation at all times.
+The high stability of $1$ was achieved for the tag $\#nemuritsuzuketeshinu$, because no entities could be associated with the results of this search.
+This can be explained as the tag is only used by Japanese twitter users in Japanese twitter messages.
+However, the Wikifier analyses the content of the results as being English text.
+A similar problem was encountered when analysing the trending topics in Germany.
+We assumed that these topics would mostly be tweeted about in German and thus called the German version of the Wikifier when analysing the results.
+However, it turned out that although the topics were trending in Germany, the tags were also used in messages in other languages.
+
+Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages.
+
+The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
+Accordingly, the entities which were most frequently used for annotation are "Britney Spears" ($95.83\%$), "iTunes" ($68.75\%$), "itunes" ($62.5\%$), "Itunes" ($31.25\%$), "Madonna\_(entertainer)" ($16.6\%$).
+The values in brackets indicate the single term stabilities for each of the terms.
+\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes?}
+
+Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$).
+As these messages contain all kinds of artist names and songs names.
+It is thus expected that the entities which are found vary between the result sets.
+In this case the most frequent entities were "iTunes" ($52.08\%$), "Michael Jackson" ($33.3\%$), "Lady Gaga" ($33.3\%$), "Lil Wayne" ($29.16\%$), "Katy Perry" ($22.92\%$).
+%\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+
+The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing. 
+\myremark{Uta}{Meine Hypothese wäre, dass es in Fällen, wo auf sehr unterschiedliche Quellen verwiesen wird, destabilisierend wirkt, in Fällen wo auf die gleichen/ähnliche Seiten verwiesen wird, stabilisierend - habe aber keine Daten, um das zu überprüfen.}
 \myremark{todo}{Hypothesis: high average update time leads to stable results}

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages. 
+\myremark{Uta}{Liegt auch an nichtgefundenen Entitäten}
 
@@
 The values in brackets indicate the single term stabilities for each of the terms.
-\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt?}
+\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes? JA, liegt am Wikifier der keine normalisierten URIs zurückliefert}
 
+Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$).
+As these messages contain all kinds of artist names and songs names.
+It is thus expected that the entities which are found vary between the result sets.
+In this case the most frequent entities were "iTunes" ($52.08\%$), "Michael Jackson" ($33.3\%$), "Lady Gaga" ($33.3\%$), "Lil Wayne" ($29.16\%$), "Katy Perry" ($22.92\%$).
 %\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+
+The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing. 
+\myremark{Uta}{Meine Hypothese wäre, dass es in Fällen, wo auf sehr unterschiedliche Quellen verwiesen wird, destabilisierend wirkt, in Fällen wo auf die gleichen/ähnliche Seiten verwiesen wird, stabilisierend - habe aber keine Daten, um das zu überprüfen.}
 \myremark{todo}{Hypothesis: high average update time leads to stable results}

### 2011-03-10 trunk/lids/twittersearchwrap/paper/paper.tex

@@
   \centering
-  \includegraphics[width=.6\linewidth]{architecture}
+  \includegraphics[width=.7\linewidth]{architecture}
   \caption{System Architecture}
@@
 
-An example for a single retrieved post is the following: ''\texttt{Just
+An example for a single retrieved post is the following: \begin{sloppypar}
+''\texttt{Just
 returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}'', posted by
-Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
-the message has been posted are furthermore known.
+\url{http://www.karlsruhe.de/stadt/tourismus.en}
+@KarlsruheTweets}'',\end{sloppypar} posted by Twitter user
+\texttt{sample\_user\_12345}; geo coordinates and the date the message has been posted are furthermore known.
 
@@
 tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
-text found at the link gives us the following text: ''\texttt{Karlsruhe, where
-paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
-
-	\item In a third step entities matching the search result are retrieved.
-The content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
+text found at the link gives us the following text:
+\begin{sloppypar}''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
+\end{sloppypar}	
+	\item In a third step entities matching the search result are retrieved. The
+	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
 The result of this step is a list of matching articles of the English Wikipedia.
 
-In our example, the contents of all posts related to the search term '\#ka' are merged with the retrieved external website content.
-Thus, the post obtained from step 1 would be matched with the website content obtained in step 2 into a single input stream: \texttt{Just returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets.
-Karlsruhe, where paths \newline converge - a legendary city in the sunny south-west of Germany, famed for its \newline fan-shaped historic street plan, where margraves reigned in times past, and German \newline joie de vivre reigns today.}
-This string is appended to the Twitter content and the external content of all other posts in the result.
+In our example, the contents of all posts related to the search term '\#ka' are
+merged with the retrieved external website content. Thus, the post obtained from
+step 1 would be matched with the website content obtained in step 2 into a
+single input stream: \begin{sloppypar}"\texttt{Just returned from a wonderful
+holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en}
+@KarlsruheTweets. Karlsruhe, where paths converge - a legendary city in the
+sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}"\end{sloppypar}This string is appended to the Twitter content and the external content of all other posts in the result.
 
@@
 
-	Continuing our example, the output RDF document contains the following triples
-	to reference the DBPedia mappings:\newline
-	\texttt{<rdf:Description rdf:about=""/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-	Karlsruhe\_Institute\_of\_Technology"/>}\newline
-	\texttt{</rdf:Description>}\newline
-	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
+	Continuing our example, the output RDF document should contain the following
+	triples to reference the DBPedia mappings:
+    \begin{enumerate}
+      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Karlsruhe.}
+      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Germany.}
+      \item \texttt{\#ka rdfs:seeAlso\newline
+      http://dbpedia.org/resource/Karlsruhe\_Institute\_of\_Technology.}
+    \end{enumerate}
 
-	\texttt{<rdf:Description rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
-	show/1234567890\#id">\newline
-	<foaf:page rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
-	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
-	<geo:lat>49.010239</geo:lat>\newline 
-	<geo:long>8.411879</geo:long>\newline
-	<foaf:maker rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-	show?screen\_name=sample\_user\_12345\#id"/>\newline 
-	<dc:description>\newline
-	Just returned from a wonderful holiday in \#ka.
-	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
-	</dc:description>\newline
-	</rdf:Description>\newline}
+	The Twitter posts matching the search term \#ka are likewise all described in
+	the output document. Here, the description for the initially given post
+	abbreviated \texttt{m} results in the following
+	triples:
+	\begin{enumerate}
+      \item \texttt{twitter:m foaf:page\newline
+      ``http://twitter.com/sample\_user\_12345/statuses/1234567890.''}
+      \item \texttt{twitter:m dc:date ``2011-02-23T12:00:00Z''.}
+      \item \texttt{twitter:m geo:lat ``49.010239''.}
+      \item \texttt{twitter:m geo:long ``8.411879''.}
+      \item \texttt{twitter:m foaf:maker twitter:sample\_user\_12345}
+      \item \texttt{twitter:m dc:description ``Just returned from a
+      wonderful\newline holiday in
+      \#ka.\url{http://www.karlsruhe.de/stadt/tourismus.en}\newline @KarlsruheTweets''.}
+    \end{enumerate}
 \end{enumerate}
@@
 The optional step of dereferencing URLs which are posted in messages contained
-in the result set can be triggered using the option \texttt{extern=true} in our system.
-To keep the input size for the next steps manageable, we do not use the whole content of the referenced sites but only the first 50 words.
+in the result set can be triggered using the option \texttt{extern=true} in our
+system. To keep the input size for the next steps manageable, we do not use the
+whole content of the referenced sites but only the first 50 words. The content
+retrieved from external websites is beautified for our purpose removing
+HTML-tags and scripting elements using the CyberNeko Java HTML Parser
+Library\footnote{\url{http://sourceforge.net/projects/nekohtml/}}.
 
@@
 
-The RDF document describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+The system generates and outputs an RDF document containing a
+semantic description of the retrieved messages matching the search query for the
+given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
+the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
 The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs.
@@
 
-\myremark{Uta}{David, kannst Du das Ausgabeformat noch etwas ausführlicher beschreiben? Welche Informationen werden genau dargestellt, welche Relationen werden wofür verwendet?}
-
-%The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
-%the Twitter search term and returns a RDF}
-%document semantically describing the most recent Twitter messages matching the
-%given query. The returned RDF document furthermore contains a mapping of the
-%query to Encyclopedia articles which based on the content published by users that most recently used the search
-%term in their posts maps to articles best describing the content of Twitter
-%messages related to the term. An overview of the System Architecture is given in Figure
-%\ref{fig:arch}.\newline 
-%Taking a more detailed look, methods performed by the
-%Twitter Search Wrapper can be grouped into five sequential steps (see Figure
-%\ref{fig:arch}). We will follow those steps along a simple example, using
-%\#ka (a hashtag frequently used to describe posts related to the city of
-%Karlsruhe, Germany) as search term for the Twitter Search wrapper.
-
-%\begin{enumerate}
-%  \item 
-%In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
-%generated by the Twitter Search
-%API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
-%search query. The generated feed contains the data of the 100 most recently published
-%publicly visible Twitter messages and their authors which match the search query.
-%The messages themselves are described by their content, publishing date, authors
-%and optionally a geographic location.\linebreak\linebreak
-%In the given example, calling the Wrapper with query '\#ka' will return a
-%document containing all most recent Twitter posts and their meta information
-%whose content matched the search string '\#ka'. Taking a closer look, a single
-%retrieved post might have the following content: \newline\linebreak 
-%\texttt{Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
-%\linebreak
-%\item
-%In a second (optional) step hyperlinks posted in messages of the fetched
-%feed are followed, content of the referenced website's body is fetched and
-%processed to the Wrapper. This option is triggered calling the Twitter Search
-%Wrapper with attribute extern=true.\newline
-%\linebreak
-%Following the initial example, the given sample post contained a link to
-%\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
-%text:\newline
-%\linebreak
-%''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
-%south-west of Germany,\newline famed for its fan-shaped historic street plan,
-%where margraves reigned in times past,\newline and German joie de vivre reigns
-%today.}''\newline\linebreak
-%The text is fetched and returned to the Wrapper. The same accounts for
-%content of all other websites that were referenced in the list of posts matching
-%the query \#ka.\newline
-%\item
-%The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
-%the Twitter messages that matched the search query and optional content of their
-%referenced websites is merged to a single input string which is used as input for the Wikifier. The service
-%returns a list of matching articles of the English
-%Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
-%to trigger mapping to the German Wikipedia.\newline\linebreak
-%In the given example, content of all posts related to the search term '\#ka' is
-%merged with retrieved external website content. Taking a closer look at the
-%single post we merge its content and content of its referenced website to
-%a single string:\newline\linebreak
-%\texttt{Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
-%where paths converge - a legendary city in the sunny\newline south-west of
-%Germany, famed for its fan-shaped historic street plan, where margraves\newline
-%reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
-%This string is appended to Twitter content and external content of all other
-%posts that have been retrieved in this way matching the initial query \#ka and
-%used as input for the Wikifier.\newline
-%  \item
-%The Wikifier now maps the input string to relevant Wikipedia articles. A
-%detailed description of this process can be found under \cite{key:wikifier}. 
-%The list of matching Wikipedia articles is finally returned to the
-%Wrapper.\newline\linebreak
-%In the given example, a desired mapping of the contents of posts related to the
-%hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
-%mapping to Wikipedia articles describing content related to Karlsruhe. We just
-%assume this results in mappings to the articles for Karlsruhe, Germany and the
-%Karlsruhe\_Institute\_of\_Technology.\newline
-%  \item
-%The Wrapper finally generates a RDF document using popular ontologies
-%(foaf\footnote{http://xmlns.com/foaf/spec/},
-%dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
-%returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
-%the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
-%output of the Wikifier) that have been mapped to the documents content.
-%At this point DBPedia is chosen as referenced encyclopedia, because its
-%semantic nature and description of Wikipedia article content contributes to a
-%coherent semantic description in the RDF document. \newline\linebreak Coming
-%back to the example, the output RDF document contains the following triples to reference the
-%DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
-%rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-%\texttt{<rdfs:seeAlso
-%rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
-%\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-%Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
-%The twitter posts matching the search term \#ka are all described in the output
-%document. As an example, the description for the initially given post might
-%result in the following RDF output:\newline\linebreak
-%\texttt{<rdf:Description
-%rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
-%show/1234567890\#id">\newline <foaf:page
-%rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
-%<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
-%<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
-%<foaf:maker
-%rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-%show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
-%Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
-%</dc:description>\newline
-%</rdf:Description>\newline}
-%\end{enumerate}
+The example twitter message given in the previous section is represented in
+the output of the Twitter Search Wrapper as follows:\newline
+\linebreak
+\texttt{<rdf:Description
+rdf:about="http://km.aifb.kit.edu/services/\newline
+twitterwrap/statuses/show/1234567890\#id">\newline
+	<foaf:page
+	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
+	statuses/1234567890"/>\newline
+	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline <geo:lat>49.010239</geo:lat>\newline 
+	<geo:long>8.411879</geo:long>\newline
+	<foaf:maker
+	rdf:resource="http://km.aifb.kit.edu/services/\newline
+	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
+	Just returned from a wonderful holiday in \#ka.
+	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+	</dc:description>\newline
+	</rdf:Description>\newline}
+	\linebreak
+Furthermore the mappings to DBpedia articles returned by the Wikifier
+are represented in the output document. In the Twitter Search Wrapper the
+representation is done the following way, again using the introductory
+example from the previous section:\newline
+\linebreak
+	\texttt{<rdf:Description rdf:about=""/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+	Karlsruhe\_Institute\_of\_Technology"/>}\newline
+	\texttt{</rdf:Description>}\newline
 
@@
 winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
-fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & 0.0208 & 0.0204 \\
+fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\
 rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
@@
 bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
-news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & 0.0000 & 0.0000  \\
-jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & 0.0000 & 0.0000 \\
-libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & 0.0208 & 0.0204 \\
-followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & 0.0000 & 0.0000\\
+news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
+jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
+libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
+followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\
 partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
-sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & 0.0000 & 0.0000 \\
+sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\
 damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
@@
 soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
-nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & 0.0000 & 0.0000 \\
+nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\
 quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
@@
 tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
-followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	0.0000 &	0.0000 \\
+followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	- &	- \\
 followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
@@
 fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
-win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & 0.0000 & 0.0000 \\
-tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & 0.0000 & 0.0000 \\
-music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & 0.0208 & 0.0204 \\
+win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & - & - \\
+tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & - & - \\
+music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & - & - \\
 in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & 0.0251 & 0.0206 \\
@@
 fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & 0.2447 & 0.4635 & 0.2448 \\
-bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & 0.0208 & 0.0204  \\
+bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & - & -  \\
 nemuritsuzuketeshinu & 17 & 48 & 314.1120 & 25053.5657 & 1.0000 & 0.0000 & 1.0000 & 0.0000 \\
@@
 	If the value of $sts$ is $1$ the term occurs in all of the result sets for the query, if it is close to $0$ it occurs in few result sets.
-	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of entities which are unchanged between the result set at $t_{i-1}$ and $t_i$:
-	$$ts(q,t_i)=\begin{cases} 1 & i=1 \\
+	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of
+	entities which are unchanged between the result set at $t_{i-1}$ and $t_i$: $$ts(q,t_i)=\begin{cases} 1 & i=1 \\
 														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$

### 2011-03-11 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 
-Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years.
+Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential over the last years.
 The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters.
@@
 
-On Twitter it is possible to search for messages containing a specific hash tag.
+On microblogging platforms it is possible to search for messages containing a specific hash tag.
 This search returns a fixed number of most recent messages containing the tag.
 However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
-As each single Twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
 
@@
 Furthermore, this annotation will help to understand hash tags.
-Hash tags are frequently used to associate messages with a specific topic, place, person or event on Twitter.
+Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms.
 For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
-If a user encounters this hash tag and does not understand it, he can search for it on Twitter.
+If a user encounters this hash tag and does not understand it, he can search for it on the microblogging platform.
 However, as discussed before, to understand a search result is difficult and time-consuming.
@@
 These entities will help the user to gain an understanding in which context the hash tag is used and what it may mean.
+If a hash tag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hash tag.
+A system may be envisioned which automatically finds entitities which are equivalent to a hash tag.
+Thus, these hash tag-entity pairs may be used similarly to systems in which hash tags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.
 
@@
 The tag $\#ka$ is however also used in the context of the car type Ford Ka.
-Thus, when searching for $\#ka$ on Twitter, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
+Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
 An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.
 
-In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities.
-While it would be more interesting to annotate each single Twitter message with relevant entities, Twitter messages are too short to contain much relevant information which could be used as input for the annotation tool.
+In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities.
+While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for the annotation tool.
 Thus, we chose to generate annotations for the whole search result.
 
+The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia.
 The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
@@
 
-Annotations should be stable over time, unless the topics discussed in the Twitter messages containing the search term change.
+Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
 In an evaluation of our approach we have tried to analyze the stability of the result.
@@
 \begin{itemize}
-	\item an approach for finding entities which are related to a search on Twitter
+	\item an approach for finding entities which are related to a search on microblogging platforms
+	\item a formatting of microblogging messages as RDF
 	\item an implementation of our approach
@@
 
-The rest of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
+The remainder of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
 

### 2011-03-12 lids/twittersearchwrap/paper/paper.tex

@@
 \newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
+\newcommand*\justify{%
+  \fontdimen2\font=0.4em% interword space
+  \fontdimen3\font=0.2em% interword stretch
+  \fontdimen4\font=0.1em% interword shrink
+  \fontdimen7\font=0.1em% extra space
+}
 
@@
 
-The architecture of our proposed system is shown in Figure~\ref{fig:arch}.
-Upon receipt of a query four steps are performed.
-In the following we will illustrate these steps using the example of a search for the hash tag $\#ka$, a hashtag which is frequently used to describe posts related to the city of Karlsruhe, Germany.
+The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
+receipt of a query four steps are performed. In the following we will illustrate
+these steps using the example of a search for the hash tag $\#Libya$, a hashtag
+which is frequently used to describe posts related to the country of Libya.
 
@@
 	\item In a first step, the most recent search results for the query are
-	obtained.\newline In our example, calling the Wrapper with query $\#ka$ will
-	return a document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
-
-An example for a single retrieved post is the following: ''\texttt{Just
-returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}'', posted by
-Twitter user \texttt{sample\_user\_12345}; geo coordinates and the date
-the message has been posted are furthermore known.
+	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
+	return a document containing all most recent Twitter posts whose content
+	matched the search string $\#Libya$ and their meta information. 
+	\newline
+	An
+example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
+for a single retrieved post is the following:\newline\texttt{\justify{"Arab
+League calls for no-fly zone in \#Libya http://t.co/ZsLNIWa"}},\newline posted
+by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
 
@@
 In our example, the message contains a link to
-\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
-tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
-text found at the link gives us the following text: ''\texttt{Karlsruhe, where
-paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
-
-	\item In a third step entities matching the search result are retrieved.
-The content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
+\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
+Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
+the text found at the link should return the following text:\newline
+\texttt{\justify{"Arab League calls for Libya no-fly zone-state TV
+- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
+Security Council to impose a no-fly zone on Libya, Egyptian state television
+reported, a decision that would give a regional seal of approval that NATO has
+said is needed for any military action."}}
+	\item In a third step entities matching the search result are retrieved. The
+	content of the Twitter messages that matched the search query and, if available, the content of referenced websites is merged to a single input string and used as input for the annotation.
 The result of this step is a list of matching articles of the English Wikipedia.
 
-In our example, the contents of all posts related to the search term '\#ka' are merged with the retrieved external website content.
-Thus, the post obtained from step 1 would be matched with the website content obtained in step 2 into a single input stream: \texttt{Just returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets.
-Karlsruhe, where paths \newline converge - a legendary city in the sunny south-west of Germany, famed for its \newline fan-shaped historic street plan, where margraves reigned in times past, and German \newline joie de vivre reigns today.}
-This string is appended to the Twitter content and the external content of all other posts in the result.
+In our example, the contents of all posts related to the search term '\#Libya'
+are merged with the retrieved external website content. Thus, the post obtained from
+step 1 would be matched with the website content obtained in step 2 into a
+single input stream:\newline\texttt{\justify{"Arab
+League calls for no-fly zone in \#Libya Arab League calls for Libya no-fly zone-state TV
+- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
+Security Council to impose a no-fly zone on Libya, Egyptian state television
+reported, a decision that would give a regional seal of approval that NATO has
+said is needed for any military action."}}\newline This string is appended to
+the Twitter content and the external content of all other posts in the result.
 
-In the example, we would expect to find entities which are related to Karlsruhe, like Karlsruhe, Germany or the Karlsruhe\_Institute\_of\_Technology.
+In the example, we would expect to find entities which are related to Libya,
+like Libya, Gaddafi or the Arab\_League.
 
-	\item	Finally, an RDF document is generated representing the search results and the annotations.
+	\item	Finally, an RDF document is generated representing the search results and
+	the annotations. \newline
+	Continuing our example, the output RDF document should contain the following
+	triples to reference the DBPedia mappings:\newline
+    \texttt{\justify{<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap?q\newline=\%23lybia>
+    rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,\newline
+    <http://dbpedia.org/resource/Gaddafi> ,\newline
+    <http://dbpedia.org/resource/Arab\_League> .}}\newline
+	The Twitter posts matching the search term \#Libya are likewise all described
+	in the output document. Here, the description for the initially given post
+	abbreviated \texttt{m} results in the following
+	triples:\newline
+	\texttt{\justify{<http://km.aifb.kit.edu/services/twitterwrap/statuses/show/4661\newline
+	9460060196865\#id> foaf:page
+	<http://twitter.com/SenJohnMcCain/\newline statuses/46619460060196865>
+	;\newline dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;\newline geo:long "8.411879" ;\newline foaf:maker
+	<http://km.aifb.kit.edu/services/twitterwrap/users/\newline
+	 show?screen\_name=SenJohnMcCain\#id> ;\newline dc:description "Arab League
+	calls for no-fly zone in \#Libya http://\newline t.co/ZsLNIWa" . }}
 
-	Continuing our example, the output RDF document contains the following triples
-	to reference the DBPedia mappings:\newline
-	\texttt{<rdf:Description rdf:about=""/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-	Karlsruhe\_Institute\_of\_Technology"/>}\newline
-	\texttt{</rdf:Description>}\newline
-	The Twitter posts matching the search term \#ka are all described in the output document. As an example, the description for the initially given post results in the following RDF output:
-
-	\texttt{<rdf:Description rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
-	show/1234567890\#id">\newline
-	<foaf:page rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
-	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
-	<geo:lat>49.010239</geo:lat>\newline 
-	<geo:long>8.411879</geo:long>\newline
-	<foaf:maker rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-	show?screen\_name=sample\_user\_12345\#id"/>\newline 
-	<dc:description>\newline
-	Just returned from a wonderful holiday in \#ka.
-	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
-	</dc:description>\newline
-	</rdf:Description>\newline}
 \end{enumerate}
@@
 
-The RDF document describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+The system generates and outputs an RDF document in RDF/XML Syntax containing a
+description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
+the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
+Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
+Vocabulary \cite{key:geo}. A single twitter message is described by its
+individual page using \texttt{foaf:page} predicate. The date and time the
+message has been posted is specified using \texttt{dc:date} predicate. The messages content
+is annotated using \texttt{dc:description}, while the geographic location of the
+message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
+creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
+uses RDF to describe information related to a Twitter user which has previously
+been implemented here at the institute as the message creators URI.
+
 The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs.
@@
 
-\myremark{Uta}{David, kannst Du das Ausgabeformat noch etwas ausführlicher beschreiben? Welche Informationen werden genau dargestellt, welche Relationen werden wofür verwendet?}
-
-%The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
-%the Twitter search term and returns a RDF}
-%document semantically describing the most recent Twitter messages matching the
-%given query. The returned RDF document furthermore contains a mapping of the
-%query to Encyclopedia articles which based on the content published by users that most recently used the search
-%term in their posts maps to articles best describing the content of Twitter
-%messages related to the term. An overview of the System Architecture is given in Figure
-%\ref{fig:arch}.\newline 
-%Taking a more detailed look, methods performed by the
-%Twitter Search Wrapper can be grouped into five sequential steps (see Figure
-%\ref{fig:arch}). We will follow those steps along a simple example, using
-%\#ka (a hashtag frequently used to describe posts related to the city of
-%Karlsruhe, Germany) as search term for the Twitter Search wrapper.
-
-%\begin{enumerate}
-%  \item 
-%In a first step the Twitter Search Wrapper fetches the atom feed (XML Data)
-%generated by the Twitter Search
-%API\footnote{\url{http://dev.twitter.com/doc/get/search}} for a given
-%search query. The generated feed contains the data of the 100 most recently published
-%publicly visible Twitter messages and their authors which match the search query.
-%The messages themselves are described by their content, publishing date, authors
-%and optionally a geographic location.\linebreak\linebreak
-%In the given example, calling the Wrapper with query '\#ka' will return a
-%document containing all most recent Twitter posts and their meta information
-%whose content matched the search string '\#ka'. Taking a closer look, a single
-%retrieved post might have the following content: \newline\linebreak 
-%\texttt{Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets}
+%The example twitter message given in the previous section is represented in
+%the output of the Twitter Search Wrapper as follows:\newline
 %\linebreak
-%\item
-%In a second (optional) step hyperlinks posted in messages of the fetched
-%feed are followed, content of the referenced website's body is fetched and
-%processed to the Wrapper. This option is triggered calling the Twitter Search
-%Wrapper with attribute extern=true.\newline
+%\texttt{<rdf:Description
+%rdf:about="http://km.aifb.kit.edu/services/\newline
+%twitterwrap/statuses/show/1234567890\#id">\newline
+%	<foaf:page
+%	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
+%	statuses/1234567890"/>\newline
+%	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+%	<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+%	<foaf:maker
+%	rdf:resource="http://km.aifb.kit.edu/services/\newline
+%	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline
+%	<dc:description>\newline Just returned from a wonderful holiday in \#ka.
+%	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+%	</dc:description>\newline
+%	</rdf:Description>\newline}
+%	\linebreak
+%Furthermore the mappings to DBpedia articles returned by the Wikifier
+%are represented in the output document. In the Twitter Search Wrapper the
+%representation is done the following way, again using the introductory
+%example from the previous section:\newline
 %\linebreak
-%Following the initial example, the given sample post contained a link to
-%\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the tourist office of the city of Karlsruhe, which contains the following
-%text:\newline
-%\linebreak
-%''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny
-%south-west of Germany,\newline famed for its fan-shaped historic street plan,
-%where margraves reigned in times past,\newline and German joie de vivre reigns
-%today.}''\newline\linebreak
-%The text is fetched and returned to the Wrapper. The same accounts for
-%content of all other websites that were referenced in the list of posts matching
-%the query \#ka.\newline
-%\item
-%The Wrapper now calls the Wikifier (see \cite{key:wikifier}). Content of
-%the Twitter messages that matched the search query and optional content of their
-%referenced websites is merged to a single input string which is used as input for the Wikifier. The service
-%returns a list of matching articles of the English
-%Wikipedia. Optionally the wrapper can be initially called with attribute lang=de
-%to trigger mapping to the German Wikipedia.\newline\linebreak
-%In the given example, content of all posts related to the search term '\#ka' is
-%merged with retrieved external website content. Taking a closer look at the
-%single post we merge its content and content of its referenced website to
-%a single string:\newline\linebreak
-%\texttt{Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets. Karlsruhe,
-%where paths converge - a legendary city in the sunny\newline south-west of
-%Germany, famed for its fan-shaped historic street plan, where margraves\newline
-%reigned in times past, and German joie de vivre reigns today.}\newline\linebreak
-%This string is appended to Twitter content and external content of all other
-%posts that have been retrieved in this way matching the initial query \#ka and
-%used as input for the Wikifier.\newline
-%  \item
-%The Wikifier now maps the input string to relevant Wikipedia articles. A
-%detailed description of this process can be found under \cite{key:wikifier}. 
-%The list of matching Wikipedia articles is finally returned to the
-%Wrapper.\newline\linebreak
-%In the given example, a desired mapping of the contents of posts related to the
-%hashtag \#ka and mapping for the hashtag \#ka as such, would preferably be a
-%mapping to Wikipedia articles describing content related to Karlsruhe. We just
-%assume this results in mappings to the articles for Karlsruhe, Germany and the
-%Karlsruhe\_Institute\_of\_Technology.\newline
-%  \item
-%The Wrapper finally generates a RDF document using popular ontologies
-%(foaf\footnote{http://xmlns.com/foaf/spec/},
-%dublincore\footnote{http://dublincore.org/documents/dcmi-terms/}, geo\footnote{http://www.w3.org/2003/01/geo}) to describe the data related to the
-%returned Twitter messages and their content using 'rdfs:seeAlso' triples to link
-%the document to DBPedia\footnote{\url{http://dbpedia.org/About}} URIs (converted
-%output of the Wikifier) that have been mapped to the documents content.
-%At this point DBPedia is chosen as referenced encyclopedia, because its
-%semantic nature and description of Wikipedia article content contributes to a
-%coherent semantic description in the RDF document. \newline\linebreak Coming
-%back to the example, the output RDF document contains the following triples to reference the
-%DBPedia mappings:\newline\linebreak \texttt{<rdfs:seeAlso
-%rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-%\texttt{<rdfs:seeAlso
-%rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
-%\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-%Karlsruhe\_Institute\_of\_Technology"/>}\newline\linebreak 
-%The twitter posts matching the search term \#ka are all described in the output
-%document. As an example, the description for the initially given post might
-%result in the following RDF output:\newline\linebreak
-%\texttt{<rdf:Description
-%rdf:about="http://km.aifb.kit.edu/services/twitterwrap/statuses/\newline
-%show/1234567890\#id">\newline <foaf:page
-%rdf:resource="http://twitter.com/sample\_user\_12345/statuses/1234567890"/>\newline
-%<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
-%<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
-%<foaf:maker
-%rdf:resource="http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-%show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
-%Just returned from a wonderful holiday in \#ka.
-%\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
-%</dc:description>\newline
-%</rdf:Description>\newline}
-%\end{enumerate}
+%	\texttt{<rdf:Description rdf:about=""/>}\newline
+%	\texttt{<rdfs:seeAlso
+%	rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+%	\texttt{<rdfs:seeAlso
+%	rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+%	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+%	Karlsruhe\_Institute\_of\_Technology"/>}\newline
+%	\texttt{</rdf:Description>}\newline
 
@@
 The second query set consists of hash tags that are frequently used on Twitter.
-To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06.
-The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}, count is the number of times we encountered them during the collection period.
+To obtain these, we have sampled the Twitter message feed using Twitter's
+Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
+top-50 hashtags dervied from the aggregate sample are listed in Table
+\ref{tbl:hashtags}, count is the number of times we encountered them during the
+collection period.
 
@@
 
-For both data set queries were executed twice per hour using the Temporal Sliding Window method for data acquisition in a 24 hour time frame.
-Data for the trending topics was collected on 2011-02-24, for the frequent hash tags data was collected on 2011-03-07.
+For both data set queries were executed twice per hour using the Temporal
+Sliding Window method for data acquisition in a 24 hour time frame. Data for the
+trending topics was collected on 2011-02-24, for the frequent hash tags data was
+collected on 2011-03-07\footnote{Collected data is available under
+\url{http://people.aifb.kit.edu/aha/2011/twittersearch/twittersearch-2011-03-10.zip}}.
 
@@
 The values in brackets indicate the single term stabilities for each of the terms.
-\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes?}
+\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes? JA, liegt am Wikifier der keine normalisierten URIs zurückliefert}
 

### 2011-03-14 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 \newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
+%\newcommand*\justify{%
+%  \fontdimen2\font=0.4em% interword space
+%  \fontdimen3\font=0.2em% interword stretch
+%  \fontdimen4\font=0.1em% interword shrink
+%  \fontdimen7\font=0.1em% extra space
+%}
 
@@
 
-The architecture of our proposed system is shown in Figure~\ref{fig:arch}.
-Upon receipt of a query four steps are performed.
-In the following we will illustrate these steps using the example of a search for the hash tag $\#ka$, a hashtag which is frequently used to describe posts related to the city of Karlsruhe, Germany.
+The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
+receipt of a query $q$ four steps are performed. In the following we will illustrate
+these steps using the example of a search for the hash tag $\#Libya$, a hashtag
+which is frequently used to describe posts related to the country of Libya.
 
@@
 \begin{enumerate}
-	\item In a first step, the most recent search results for the query are
-	obtained.\newline In our example, calling the Wrapper with query $\#ka$ will
-	return a document containing all most recent Twitter posts whose content matched the search string $\#ka$ and their meta information.
-
-An example for a single retrieved post is the following: \begin{sloppypar}
-''\texttt{Just
-returned from a wonderful holiday in \#ka.
-\url{http://www.karlsruhe.de/stadt/tourismus.en}
-@KarlsruheTweets}'',\end{sloppypar} posted by Twitter user
-\texttt{sample\_user\_12345}; geo coordinates and the date the message has been posted are furthermore known.
+	\item In a first step, the most recent search results $R$ for the query are
+	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
+	return a document containing all most recent Twitter posts whose content
+	matched the search string $\#Libya$ and their meta information. 
+	\newline
+	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
+for a single retrieved post is the following:
+\begin{verbatim}
+"Arab League calls for no-fly zone in \#Libya 
+http://t.co/ZsLNIWa"}}
+\end{verbatim}
+,posted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
 
@@
 In our example, the message contains a link to
-\url{http://www.karlsruhe.de/stadt/tourismus.en}, the official homepage of the
-tourist office of the city of Karlsruhe. Dereferencing this URL and grabbing the
-text found at the link gives us the following text:
-\begin{sloppypar}''\texttt{Karlsruhe, where paths converge - a legendary city in the sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}''
-\end{sloppypar}	
+\url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
+Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
+the text found at the link should return the following text:
+\begin{verbatim}
+"Arab League calls for Libya no-fly zone-state TV - CAIRO, 
+March 12 (Reuters) - The Arab League on Saturday called on the
+U.N. Security Council to impose a no-fly zone on Libya, 
+Egyptian state television reported, a decision that would give
+a regional seal of approval that NATO has said is needed for 
+any military action."
+\end{verbatim}
 	\item In a third step entities matching the search result are retrieved. The
@@
 
-In our example, the contents of all posts related to the search term '\#ka' are
-merged with the retrieved external website content. Thus, the post obtained from
+In our example, the contents of all posts related to the search term '\#Libya'
+are merged with the retrieved external website content. Thus, the post obtained from
 step 1 would be matched with the website content obtained in step 2 into a
-single input stream: \begin{sloppypar}"\texttt{Just returned from a wonderful
-holiday in \#ka. \url{http://www.karlsruhe.de/stadt/tourismus.en}
-@KarlsruheTweets. Karlsruhe, where paths converge - a legendary city in the
-sunny south-west of Germany, famed for its fan-shaped historic street plan, where margraves reigned in times past, and German joie de vivre reigns today.}"\end{sloppypar}This string is appended to the Twitter content and the external content of all other posts in the result.
+single input stream:
+\begin{verbatim}"Arab League calls for no-fly zone in #Libya
+Arab League calls for Libya no-fly zone-state TV - CAIRO, 
+March 12 (Reuters) - The Arab League on Saturday called on the 
+U.N. Security Council to impose a no-fly zone on Libya, 
+Egyptian state television reported, a decision that would give
+a regional seal of approval that NATO has said is needed for 
+any military action."}
+\end{verbatim}
+This string is appended to the Twitter content and the external content of all other posts in the result.
 
-In the example, we would expect to find entities which are related to Karlsruhe, like Karlsruhe, Germany or the Karlsruhe\_Institute\_of\_Technology.
+In the example, we would expect to find entities which are related to Libya,
+like Libya, Gaddafi or the Arab\_League.
 
-	\item	Finally, an RDF document is generated representing the search results and the annotations.
+	\item	Finally, an RDF document is generated representing the search results and
+	the annotations. Continuing our example, the output RDF document should contain the following
+	triples to reference the DBPedia mappings:
+	\begin{verbatim}
+	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
+	?q=\%23lybia>
+     rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,
+        <http://dbpedia.org/resource/Gaddafi> ,
+        <http://dbpedia.org/resource/Arab\_League> .
+  \end{verbatim}
+	The Twitter posts matching the search term \#Libya are likewise all described
+	in the output document. The description for the post from our example 
+	%abbreviated \texttt{m} 
+	results in the following triples:
+	\begin{verbatim}
+	<http://km.aifb.kit.edu/services/twitterwrap/statuses/
+	show/46619460060196865\#id> 
+		foaf:page <http://twitter.com/SenJohnMcCain/statuses/
+			46619460060196865>;
+		dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;
+		geo:long "8.411879" ;
+		foaf:maker <http://km.aifb.kit.edu/services/twitterwrap/users/
+			show?screen\_name=SenJohnMcCain\#id> ;
+		dc:description "Arab League calls for no-fly zone in \#Libya 
+			http://\newline t.co/ZsLNIWa" . 
+	\end{verbatim}
 
-	Continuing our example, the output RDF document should contain the following
-	triples to reference the DBPedia mappings:
-    \begin{enumerate}
-      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Karlsruhe.}
-      \item \texttt{\#ka rdfs:seeAlso http://dbpedia.org/resource/Germany.}
-      \item \texttt{\#ka rdfs:seeAlso\newline
-      http://dbpedia.org/resource/Karlsruhe\_Institute\_of\_Technology.}
-    \end{enumerate}
-
-	The Twitter posts matching the search term \#ka are likewise all described in
-	the output document. Here, the description for the initially given post
-	abbreviated \texttt{m} results in the following
-	triples:
-	\begin{enumerate}
-      \item \texttt{twitter:m foaf:page\newline
-      ``http://twitter.com/sample\_user\_12345/statuses/1234567890.''}
-      \item \texttt{twitter:m dc:date ``2011-02-23T12:00:00Z''.}
-      \item \texttt{twitter:m geo:lat ``49.010239''.}
-      \item \texttt{twitter:m geo:long ``8.411879''.}
-      \item \texttt{twitter:m foaf:maker twitter:sample\_user\_12345}
-      \item \texttt{twitter:m dc:description ``Just returned from a
-      wonderful\newline holiday in
-      \#ka.\url{http://www.karlsruhe.de/stadt/tourismus.en}\newline @KarlsruheTweets''.}
-    \end{enumerate}
 \end{enumerate}
@@
 
-In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
+In the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
 
-The implementation is based on a set of existing components: Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
+The implementation is based on a set of existing components: 
+\begin{itemize}
+\item Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}, a RESTful API which delivers search results in JSON.
 The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors.
@@
 
-The optional step of dereferencing URLs which are posted in messages contained
+\item The optional step of dereferencing URLs which are posted in messages contained
 in the result set can be triggered using the option \texttt{extern=true} in our
@@
 
-The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
+\item The Wikifier \cite{key:wikifier} is used for obtaining content annotations.
+This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
+It represents a state-of-the-art annotation tool.
+It was chosen as it allows for finding entities not from some tool-specific knowledge base but from dbpedia, which is one of the most widely used data sources within the Linked Open Data cloud.
 
-The system generates and outputs an RDF document containing a
-semantic description of the retrieved messages matching the search query for the
-given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
-the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+\item The system generates and outputs an RDF document in RDF/XML Syntax containing a
+description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
+the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
+Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
+Vocabulary \cite{key:geo}. A single twitter message is described by its
+individual page using \texttt{foaf:page} predicate. The date and time the
+message has been posted is specified using \texttt{dc:date} predicate. The messages content
+is annotated using \texttt{dc:description}, while the geographic location of the
+message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
+creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
+uses RDF to describe information related to a Twitter user which has previously
+been implemented here at the institute as the message creators URI.
+
+\end{itemize}
+
 The annotations are added to the search result using \texttt{rdf:seeAlso} links to DBpedia entities \cite{key:dbpedia} which are obtained by a direct transformation of the Wikipedia entities' URLs.
@@
 
-The example twitter message given in the previous section is represented in
-the output of the Twitter Search Wrapper as follows:\newline
-\linebreak
-\texttt{<rdf:Description
-rdf:about="http://km.aifb.kit.edu/services/\newline
-twitterwrap/statuses/show/1234567890\#id">\newline
-	<foaf:page
-	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
-	statuses/1234567890"/>\newline
-	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline <geo:lat>49.010239</geo:lat>\newline 
-	<geo:long>8.411879</geo:long>\newline
-	<foaf:maker
-	rdf:resource="http://km.aifb.kit.edu/services/\newline
-	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline <dc:description>\newline
-	Just returned from a wonderful holiday in \#ka.
-	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
-	</dc:description>\newline
-	</rdf:Description>\newline}
-	\linebreak
-Furthermore the mappings to DBpedia articles returned by the Wikifier
-are represented in the output document. In the Twitter Search Wrapper the
-representation is done the following way, again using the introductory
-example from the previous section:\newline
-\linebreak
-	\texttt{<rdf:Description rdf:about=""/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
-	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
-	Karlsruhe\_Institute\_of\_Technology"/>}\newline
-	\texttt{</rdf:Description>}\newline
+%The example twitter message given in the previous section is represented in
+%the output of the Twitter Search Wrapper as follows:\newline
+%\linebreak
+%\texttt{<rdf:Description
+%rdf:about="http://km.aifb.kit.edu/services/\newline
+%twitterwrap/statuses/show/1234567890\#id">\newline
+%	<foaf:page
+%	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
+%	statuses/1234567890"/>\newline
+%	<dc:date>2011-02-23T12:00:00Z</dc:date>\newline
+%	<geo:lat>49.010239</geo:lat>\newline <geo:long>8.411879</geo:long>\newline
+%	<foaf:maker
+%	rdf:resource="http://km.aifb.kit.edu/services/\newline
+%	twitterwrap/users/show?screen\_name=sample\_user\_12345\#id"/>\newline
+%	<dc:description>\newline Just returned from a wonderful holiday in \#ka.
+%	\url{http://www.karlsruhe.de/stadt/tourismus.en} @KarlsruheTweets\newline
+%	</dc:description>\newline
+%	</rdf:Description>\newline}
+%	\linebreak
+%Furthermore the mappings to DBpedia articles returned by the Wikifier
+%are represented in the output document. In the Twitter Search Wrapper the
+%representation is done the following way, again using the introductory
+%example from the previous section:\newline
+%\linebreak
+%	\texttt{<rdf:Description rdf:about=""/>}\newline
+%	\texttt{<rdfs:seeAlso
+%	rdf:resource="http://dbpedia.org/resource/Karlsruhe"/>}\newline
+%	\texttt{<rdfs:seeAlso
+%	rdf:resource="http://dbpedia.org/resource/Germany"/>}\newline
+%	\texttt{<rdfs:seeAlso rdf:resource="http://dbpedia.org/resource/\newline
+%	Karlsruhe\_Institute\_of\_Technology"/>}\newline
+%	\texttt{</rdf:Description>}\newline
 
@@
 
-We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}.
-Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.
-
-\begin{table}[ht*]
-\centering
-\begin{tabular}{ l }
-Trending Topics Worldwide  \\
-\hline
-\#goodlucknickj  \\
-\#smalljoys \\
-\#thingsthedevilinvented \\
-Adam Wainwright  \\
-CatchPetrovaFire \\
-Gadafi  \\
-Libia \\
-Precious Minaj \\
-Tommy John  \\
-\end{tabular}
-\begin{tabular}{l}
-Trending Topics Germany \\
-\hline
-\#gaddafi \\
-\#guttenberg  \\
-\#libya  \\
-Doktorarbeit \\
-Gef\"{u}hl  \\
-Lion  \\
-MBP \\
-Thunderbolt \\
-Vorratsdatenspeicherung \\
-\end{tabular}
-\caption{Search terms}\label{tbl:terms}
-\end{table}
-
-The second query set consists of hash tags that are frequently used on Twitter.
-To obtain these, we have sampled the Twitter message feed using Twitter's Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06.
-The top-50 hashtags dervied from the aggregate sample are listed in Table \ref{tbl:hashtags}, count is the number of times we encountered them during the collection period.
+We have conducted experiments on a set of queries which were identified to be hash tags which are frequently used on Twitter.
+To obtain these, we have sampled the Twitter message feed using Twitter's
+Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
+top-50 hashtags dervied from the aggregate sample are listed in Table
+\ref{tbl:hashtags}, count is the number of times we encountered them during the
+collection period.
 
@@
 np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
-nowplaying & 144 & 17 & 0.4514 & 0.0251 & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
+nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
 winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
-fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\
+fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\
 rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
@@
 bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
-news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
-jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
-libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
-followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\
+news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
+jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
+libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
+followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\
 partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
-sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\
+sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\
 damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
@@
 soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
-nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\
+nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\
 quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
@@
 tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
-followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	- &	- \\
+followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	-- &	-- \\
 followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
@@
 fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
-win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & - & - \\
-tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & - & - \\
-music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & - & - \\
-in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & 0.0251 & 0.0206 \\
+win & 20 & 0 & 4.2949 & 5.1856 & \textbf{0.0347} & 0.0221 & -- & -- \\
+tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & -- & -- \\
+music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & -- & -- \\
+in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & \textbf{0.0251} & 0.0206 \\
 imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
@@
 lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
-fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & 0.2447 & 0.4635 & 0.2448 \\
-bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & - & -  \\
-nemuritsuzuketeshinu & 17 & 48 & 314.1120 & 25053.5657 & 1.0000 & 0.0000 & 1.0000 & 0.0000 \\
+fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & \textbf{0.2447} & 0.4635 & \textbf{0.2448} \\
+bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & -- & --  \\
+nemuritsuzuketeshinu & 17 & 48 & \textbf{314.1120} & \textbf{25053.5657} & \textbf{1.0000} & \textbf{0.0000} & \textbf{1.0000} & \textbf{0.0000} \\
 fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
@@
 	\item The time stability $ts$ for a query $q$ at time $t_i$ is the fraction of
-	entities which are unchanged between the result set at $t_{i-1}$ and $t_i$: $$ts(q,t_i)=\begin{cases} 1 & i=1 \\
+	entities which are unchanged between the result set at $t_{i-1}$ and $t_i$: 
+	$$ts(q,t_i)=\begin{cases} 1 & i=1 \\
+														1 & E_{i-1}\cup E_i = \emptyset\\														
 														\frac{|E_{i-1}\cap E_i|}{|E_{i-1}\cup E_i|} & i>1\end{cases}$$
@@
 An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}.
+The most frequent entities for some of the tags are listed in Table~\ref{tbl:entities}.
 In total, we have analysed 48 result sets for each of the query tags.
@@
 In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed.
-Note that this value is only an average and does not guarantee disjointness of the result sets, as high update frequencies in one result set may outweigh low update frequencies in other result sets.
+Note that update times below this value do not guarantee disjointness of the result sets, as the value is only an average, and high update frequencies in one result set may outweigh low update frequencies in other result sets.
 Thus, we have additionally analysed the variance of the $aut$s.
@@
 
+\begin{table}[ht]
+\centering
+\begin{tabular}{l|l|l|l}
+Tag & extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
+\hline
+$\#tilltheworldends$ & false & Britney Spears .9583 \\
+& &  iTunes & .6875 \\
+& &  itunes & .625 \\ 
+$\#nowplaying$ & false & iTunes & .5208 \\
+& & Michael Jackson & .333 \\
+& & Lady Gaga & .333 \\
+$\#nowplaying$ & true & YouTube & .8235 \\
+& & Hip Hop Music & .6471 \\
+& & The Notorious B.I.G. & .5883 \\
+$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
+& & Usher & .3125 \\
+& & Lil Wayne & .2917 \\
+$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
+& & YouTube & .375 \\
+& & Ne-Yo & .315 \\
+$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
+& & Twitter & .2291 \\
+& & twitter & .1667 \\
+$\#thataintwinning$ & true & twitter & .5208 \\
+& & Twitter & .5 \\
+& & Two and a half men & .125 \\
+$\#blackpeoplemovies$ & false & Devil & .4791 \\
+& & Tyler Perry & .2708 \\
+& & Harry Potter & .2292 \\
+$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
+& & YouTube & 1 \\
+& & amazon.com & 1
+\end{tabular}
+\label{tbl:entities}
+\caption{Most frequent entities and their single term stabilities}
+\end{table}
+
 We also report the average time stability over all time points as well as the variance for each hash tag.
 A high time stability indicates that more or less the same entities were used for annotation at all times.
-The high stability of $1$ was achieved for the tag $\#nemuritsuzuketeshinu$, because no entities could be associated with the results of this search.
-This can be explained as the tag is only used by Japanese twitter users in Japanese twitter messages.
+The highest stabilities were achieved for the tags $\#nemuritsuzuketeshinu$ and $\#partiu$, because no (resp.
+very few) entities could be associated with the results of this search.
+This can be explained as the tags are only used in Japanese resp.
+Spanish twitter messages.
 However, the Wikifier analyses the content of the results as being English text.
-A similar problem was encountered when analysing the trending topics in Germany.
-We assumed that these topics would mostly be tweeted about in German and thus called the German version of the Wikifier when analysing the results.
-However, it turned out that although the topics were trending in Germany, the tags were also used in messages in other languages.
-
-Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages. 
-\myremark{Uta}{Liegt auch an nichtgefundenen Entitäten}
+A solution could be to search only for English messages, however, this is not possible as Twitter messages have no language tags and location attributes are no sufficient indicator for the language in which a user will write messages.
 
 The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
-Accordingly, the entities which were most frequently used for annotation are "Britney Spears" ($95.83\%$), "iTunes" ($68.75\%$), "itunes" ($62.5\%$), "Itunes" ($31.25\%$), "Madonna\_(entertainer)" ($16.6\%$).
-The values in brackets indicate the single term stabilities for each of the terms.
-\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes? JA, liegt am Wikifier der keine normalisierten URIs zurückliefert}
+The different URIs which are used for annotation are explained by the fact, that the Wikifier does not return normalized entities.
 
 Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$).
-As these messages contain all kinds of artist names and songs names.
-It is thus expected that the entities which are found vary between the result sets.
-In this case the most frequent entities were "iTunes" ($52.08\%$), "Michael Jackson" ($33.3\%$), "Lady Gaga" ($33.3\%$), "Lil Wayne" ($29.16\%$), "Katy Perry" ($22.92\%$).
-%\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+As these messages contain all kinds of artist names and songs names, it is thus expected that the entities which are found vary between the result sets.
 
 The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing.
-\myremark{Uta}{Meine Hypothese wäre, dass es in Fällen, wo auf sehr unterschiedliche Quellen verwiesen wird, destabilisierend wirkt, in Fällen wo auf die gleichen/ähnliche Seiten verwiesen wird, stabilisierend - habe aber keine Daten, um das zu überprüfen.}
-\myremark{todo}{Hypothesis: high average update time leads to stable results}
-
-\subsection{Discussion}
-
-@@@highlight the remarkable outcomes
-@@@what is did we learn from the results?
+The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$.
+Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hash tags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.
 
@@
 
-@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka
+We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities.
+Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases.
+One reason is the use of hashtags in different contexts, another reason is that hash tags do not necessarily describe an entity, but are rather used to describe contexts.
 
-@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages
+Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms.
+However, NLP techniques which are used to analyze the messages are language dependent.
 
-@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
+%@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
 

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex

@@
 \newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}
-\newcommand*\justify{%
-  \fontdimen2\font=0.4em% interword space
-  \fontdimen3\font=0.2em% interword stretch
-  \fontdimen4\font=0.1em% interword shrink
-  \fontdimen7\font=0.1em% extra space
-}
+%\newcommand*\justify{%
+%  \fontdimen2\font=0.4em% interword space
+%  \fontdimen3\font=0.2em% interword stretch
+%  \fontdimen4\font=0.1em% interword shrink
+%  \fontdimen7\font=0.1em% extra space
+%}
 
@@
 \begin{abstract}
-To facilitate understanding the meaning of a hash tag in the context of Twitter, we have developed a system which annotates hash tags based on Twitter search results with encyclopedia entities that best describe the hash tag, thus offering means of quickly grasping the meaning of the hash tag and at the same time providing starting points for further exploration of the hash tags' context.
-In an evaluation we show that the encyclopedia entities used for annotation represent the content in a suitable manner and that the annotations remain stable over time, i.e.
-when executing the same search at different times, the same encyclopedia entities are returned.
+Microblog messages contain so-called hashtags which are usedto mark keywords or topics.
+To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context.
+In an evaluation we analyse the stability of the related entities.
 \end{abstract}
@@
 
-On microblogging platforms it is possible to search for messages containing a specific hash tag.
+On microblogging platforms it is possible to search for messages containing a specific hashtag.
 This search returns a fixed number of most recent messages containing the tag.
@@
 
-Furthermore, this annotation will help to understand hash tags.
+Furthermore, this annotation will help to understand hashtags.
 Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms.
 For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
-If a user encounters this hash tag and does not understand it, he can search for it on the microblogging platform.
-However, as discussed before, to understand a search result is difficult and time-consuming.
+If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
+However, understanding a search result is difficult and time-consuming.
 Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
-These entities will help the user to gain an understanding in which context the hash tag is used and what it may mean.
-If a hash tag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hash tag.
-A system may be envisioned which automatically finds entitities which are equivalent to a hash tag.
-Thus, these hash tag-entity pairs may be used similarly to systems in which hash tags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.
+These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.
+If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag.
+A system may be envisioned which automatically finds entitities which are equivalent to a hashtag.
+Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.
 
-Finding entities matching a query, especially a query for a given hash tag is difficult due to synonyms and homonyms in the set of hash tags that are frequently used.
-For example, both the hash tags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
+Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
+Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used.
+For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
 The tag $\#ka$ is however also used in the context of the car type Ford Ka.
@@
 In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities.
-While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for the annotation tool.
+While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
 Thus, we chose to generate annotations for the whole search result.
@@
 Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
-Note however that a direct mapping of hash tags to entities is not possible in many cases: e.g.
-there is no entity in dbpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.
+External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible.
+Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g.
+there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.
 
 Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
-In an evaluation of our approach we have tried to analyze the stability of the result.
+In an evaluation of our approach we have tried to analyse the stability of the result.
 
@@
 \begin{itemize}
-	\item an approach for finding entities which are related to a search on microblogging platforms
-	\item a formatting of microblogging messages as RDF
-	\item an implementation of our approach
-	\item an evaluation of the stability and relevance of the entities found with our approach.
+	\item We present an approach for finding entities which are related to search results on microblogging platforms
+	\item We specify a formatting of microblogging messages as RDF
+	\item We evaluate the stability of the found entities.
 \end{itemize}
@@
 The remainder of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
-
-\section{Related Work}
-\label{sect:relWork}
-
-Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
-
-The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
-Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
-
-Passant et al.
-\cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web.
-They propose a data model which allows for the association of URIs with users, microblogs and microposts.
-To this end, SIOC and FOAF vocabularies are used and extended.
-Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced.
-Additionally, they propose the use of so-called semantic hash tags.
-The idea is to use URIs as hash tags (e.g.
-\emph{\#geo:Paris\_France}).
-It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.
-In contrast to this approach we do not require users to change their behavior by requiring them to use another type of hash tags.
-Instead, our method finds Linked Open Data entities which are related to the query automatically.
-
-Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks.
-They have instantiated their system to analyze data from Twitter.
-In their system, they collect data from one or several users.
-The system by Passant et al.
-\cite{key:smob} is used for transforming twitter data to semantic data.
-The triplified data can then be analysed using SPARQL.
-They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
-
-Relating semantic concepts with twitter messages has been attempted by various authors:
-Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
-% from stakovic et al.
-%In order to make tweets more searchable and make them useful for the described
-%scenario one would need to have represent them in a structured format and associate
-%those tweets with the topics that refer to. As a basic approach we process the text of
-%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
-%concepts related to a tweet, but is useful only on a limited number of tweets directly
-%mentioning a particular topic. In the example data set we produced from ESWC2010,
-%tweet topics are represented using dc:subject property.
-Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages (as proposed by Wagner \cite{key:clauwa}) as input to the extraction component.
-
-Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.
-
-Kinsella et al.
-\cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
-We too use external data to augment the set of Twitter messages supplied to the Wikifier system.
-
-The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
-The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hash tags to Wikipedia/DBpedia concepts.
 
@@
 the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result.
+In the following we will illustrate our approach based on a search for the hashtag $\#Libya$, a hashtag
+which is frequently used to describe posts related to the country of Libya.
 
 The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
-receipt of a query four steps are performed. In the following we will illustrate
-these steps using the example of a search for the hash tag $\#Libya$, a hashtag
-which is frequently used to describe posts related to the country of Libya.
+receipt of a query $q$ four steps are performed.
 
@@
 \begin{enumerate}
-	\item In a first step, the most recent search results for the query are
+	\item In a first step, the most recent search results $R$ for the query are
 	obtained.\newline In our example, calling the Wrapper with query $\#Libya$ will
@@
 	\newline
-	An
-example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
-for a single retrieved post is the following:\newline\texttt{\justify{"Arab
-League calls for no-fly zone in \#Libya http://t.co/ZsLNIWa"}},\newline posted
-by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
+	An example\footnote{\url{http://twitter.com/SenJohnMcCain/statuses/46619460060196865}}
+for a single retrieved post is the following:
+{\small
+\begin{verbatim}
+"Arab League calls for no-fly zone in #Libya http://t.co/ZsLNIWa"
+\end{verbatim}}
+This messageposted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
 
@@
 Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
-the text found at the link should return the following text:\newline
-\texttt{\justify{"Arab League calls for Libya no-fly zone-state TV
-- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
-Security Council to impose a no-fly zone on Libya, Egyptian state television
-reported, a decision that would give a regional seal of approval that NATO has
-said is needed for any military action."}}
+the text found at the link should return the following text:
+{\small\begin{verbatim}"Arab League calls for Libya no-fly zone-state TV - CAIRO, March 12
+(Reuters) - The Arab League on Saturday called on the U.N. Security 
+Council to impose a no-fly zone on Libya, Egyptian state television
+reported, a decision that would give a regional seal of approval
+that NATO has said is needed for any military action."\end{verbatim}}
 	\item In a third step entities matching the search result are retrieved. The
@@
 step 1 would be matched with the website content obtained in step 2 into a
-single input stream:\newline\texttt{\justify{"Arab
-League calls for no-fly zone in \#Libya Arab League calls for Libya no-fly zone-state TV
-- CAIRO, March 12 (Reuters) - The Arab League on Saturday called on the U.N.
-Security Council to impose a no-fly zone on Libya, Egyptian state television
-reported, a decision that would give a regional seal of approval that NATO has
-said is needed for any military action."}}\newline This string is appended to
-the Twitter content and the external content of all other posts in the result.
+single input stream:
+\begin{verbatim}"Arab League calls for no-fly zone in #Libya
+Arab League calls for Libya no-fly zone-state TV - CAIRO, 
+March 12 (Reuters) - The Arab League on Saturday called on the 
+U.N. Security Council to impose a no-fly zone on Libya, 
+Egyptian state television reported, a decision that would give
+a regional seal of approval that NATO has said is needed for 
+any military action."\end{verbatim}
+This string is appended to the Twitter content and the external content of all other posts in the result.
 
@@
 	\item	Finally, an RDF document is generated representing the search results and
-	the annotations. \newline
-	Continuing our example, the output RDF document should contain the following
-	triples to reference the DBPedia mappings:\newline
-    \texttt{\justify{<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap?q\newline=\%23lybia>
-    rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,\newline
-    <http://dbpedia.org/resource/Gaddafi> ,\newline
-    <http://dbpedia.org/resource/Arab\_League> .}}\newline
+	the annotations. Continuing our example, the output RDF document should contain the following
+	triples to reference the DBPedia mappings:
+	{\small\begin{verbatim}	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
+	?q=\%23lybia>
+     rdfs:seeAlso <http://dbpedia.org/resource/Lybia> ,
+        <http://dbpedia.org/resource/Gaddafi> ,
+        <http://dbpedia.org/resource/Arab\_League> .\end{verbatim}}
 	The Twitter posts matching the search term \#Libya are likewise all described
-	in the output document. Here, the description for the initially given post
-	abbreviated \texttt{m} results in the following
-	triples:\newline
-	\texttt{\justify{<http://km.aifb.kit.edu/services/twitterwrap/statuses/show/4661\newline
-	9460060196865\#id> foaf:page
-	<http://twitter.com/SenJohnMcCain/\newline statuses/46619460060196865>
-	;\newline dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;\newline geo:long "8.411879" ;\newline foaf:maker
-	<http://km.aifb.kit.edu/services/twitterwrap/users/\newline
-	 show?screen\_name=SenJohnMcCain\#id> ;\newline dc:description "Arab League
-	calls for no-fly zone in \#Libya http://\newline t.co/ZsLNIWa" . }}
-
+	in the output document. The description for the post from our example 
+	%abbreviated \texttt{m} 
+	results in the following triples:
+	{\small\begin{verbatim}<http://km.aifb.kit.edu/services/twitterwrap/statuses/
+	show/46619460060196865\#id> 
+	   foaf:page <http://twitter.com/SenJohnMcCain/statuses/
+	      46619460060196865>;
+	   dc:date "2011-03-12T17:12:00Z" ;\newline geo:lat "49.010239" ;
+	   geo:long "8.411879" ;
+	   foaf:maker <http://km.aifb.kit.edu/services/twitterwrap/users/
+		    show?screen\_name=SenJohnMcCain\#id> ;
+	   dc:description "Arab League calls for no-fly zone in \#Libya 
+	      http://\newline t.co/ZsLNIWa" . \end{verbatim}}     
 \end{enumerate}
@@
 
-In the Twitter Search Wrapper\footnote{Available at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
+We provide an implementation of our approach in the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}}.
 
-The implementation is based on a set of existing components: Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}.
+The implementation is based on a set of existing components: 
+\begin{itemize}
+\item Twitter search results are obtained by using the Twitter search API\footnote{\url{http://dev.twitter.com/doc/get/search}}, a RESTful API which delivers search results in JSON.
 The result is a feed containing the 100 most recently published Twitter messages, which are publicly visible and match the query, and their authors.
@@
 
-The optional step of dereferencing URLs which are posted in messages contained
-in the result set can be triggered using the option \texttt{extern=true} in our
-system. To keep the input size for the next steps manageable, we do not use the
-whole content of the referenced sites but only the first 50 words. The content
+\item The optional step of dereferencing URLs which are posted in messages contained
+in the result set can be triggered using the option \texttt{extern=true}. To keep the input size for the next steps manageable, only the first 50 words of the referenced sites are used. The content
 retrieved from external websites is beautified for our purpose removing
@@
 
-The Wikifier \cite{key:wikifier} is used for obtaining content annotations. This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
+\item The Wikifier \cite{key:wikifier} is used for obtaining content annotations.
+This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analysed text.
+It represents a state-of-the-art annotation tool and was chosen as it allows for finding entities not from some tool-specific knowledge base but from DBpedia, which is one of the most widely used data sources on the Linked Data Web.
 
-The system generates and outputs an RDF document in RDF/XML Syntax containing a
-description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
-the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
-Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
-Vocabulary \cite{key:geo}. A single twitter message is described by its
-individual page using \texttt{foaf:page} predicate. The date and time the
-message has been posted is specified using \texttt{dc:date} predicate. The messages content
-is annotated using \texttt{dc:description}, while the geographic location of the
-message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
-creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
-uses RDF to describe information related to a Twitter user which has previously
-been implemented here at the institute as the message creators URI.
+\item The system generates and outputs an RDF document in RDF/XML Syntax containing a
+description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. 
+%It describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+A single Twitter message is described by its individual page using the \texttt{foaf:page} predicate.
+The date and time the message has been posted is specified using the \texttt{dc:date} predicate.
+The message's content is annotated using \texttt{dc:description}, while the geographic location of the message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates.
+The creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that uses RDF to describe information related to a Twitter user which has previously been implemented here at the institute as the message creators URI.
 
@@
 
-%The example twitter message given in the previous section is represented in
+\end{itemize}
+
+%The example Twitter message given in the previous section is represented in
 %the output of the Twitter Search Wrapper as follows:\newline
@@
 %rdf:about="http://km.aifb.kit.edu/services/\newline
-%twitterwrap/statuses/show/1234567890\#id">\newline
+%Twitterwrap/statuses/show/1234567890\#id">\newline
 %	<foaf:page
-%	rdf:resource="http://twitter.com/sample\_user\_12345/\newline
+%	rdf:resource="http://Twitter.com/sample\_user\_12345/\newline
 %	statuses/1234567890"/>\newline
@@
 
-We have evaluated our approach to assess whether the entities which are found as related to a specific hash tag are useful and stable over time.
+We have evaluated our approach to assess whether the entities which are found as related to a specific hashtag are stable over time.
 
@@
 
-We have conducted the evaluation on two sets of queries: the first set are the trending topics worldwide and in Germany on Twitter retrieved on February 24th 17:20h (GMT) -- these topics are listed in Table \ref{tbl:terms}.
-Trending topics are chosen as they cover a variety of recently talked about topics which due to its recent nature may be of high interest for further processing.
-
-\begin{table}[ht*]
-\centering
-\begin{tabular}{ l }
-Trending Topics Worldwide  \\
-\hline
-\#goodlucknickj  \\
-\#smalljoys \\
-\#thingsthedevilinvented \\
-Adam Wainwright  \\
-CatchPetrovaFire \\
-Gadafi  \\
-Libia \\
-Precious Minaj \\
-Tommy John  \\
-\end{tabular}
-\begin{tabular}{l}
-Trending Topics Germany \\
-\hline
-\#gaddafi \\
-\#guttenberg  \\
-\#libya  \\
-Doktorarbeit \\
-Gef\"{u}hl  \\
-Lion  \\
-MBP \\
-Thunderbolt \\
-Vorratsdatenspeicherung \\
-\end{tabular}
-\caption{Search terms}\label{tbl:terms}
-\end{table}
-
-The second query set consists of hash tags that are frequently used on Twitter.
+We have conducted experiments on a set of queries which were identified to be hashtags which are frequently used on Twitter.
 To obtain these, we have sampled the Twitter message feed using Twitter's
@@
 \centering
+\small
 \begin{tabular}{ l|l|l|l|l|l|l|l|l }
@@
 \hline
-ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
-np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
-nowplaying & 144 & 17 & 0.4514 & 0.0251 & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
-winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
-fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & - & - \\
-rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
-mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
-blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
-tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
-thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
-fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
-teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
-iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
-bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
-news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & - & -  \\
-jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & - & - \\
-libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & - & - \\
-followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & - & -\\
-partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
-sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & - & - \\
-damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
-tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
-soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
-nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & - & - \\
-quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
+\#ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
+\#np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
+\#nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
+\#winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
+\#fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\
+\#rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
+\#mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
+\#blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
+\#tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
+\#thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
+\#fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
+\#teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
+\#iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
+\#bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
+\#news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
+\#jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
+\#libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
+\#followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\
+\#partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
+\#sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\
+\#damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
+\#tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
+\#soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
+\#nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\
+\#quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
 %\end{tabular}
@@
 %\hline
-nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
-quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
-shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
-jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
-carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
-tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
-followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	- &	- \\
-followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
-follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
-egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
-retweet & 22 & 48 & 4.6991 & 13.4434 & 0.1570 & 0.1232 & 0.1353 & 0.0306 \\
-fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
-win & 20 & 0 & 4.2949 & 5.1856 & 0.0347 & 0.0221 & - & - \\
-tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & - & - \\
-music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & - & - \\
-in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & 0.0251 & 0.0206 \\
-imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
-nowwatching & 19 & 48 & 7.9110 & 8.6833 & 0.0672 & 0.0214 & 0.1293 & 0.0211 \\
-cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
-twexit & 18 & 48 & 12.5672 & 255.8178 & 0.3125 & 0.2148 & 0.2417 & 0.1783 \\
-lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
-fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & 0.2447 & 0.4635 & 0.2448 \\
-bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & - & -  \\
-nemuritsuzuketeshinu & 17 & 48 & 314.1120 & 25053.5657 & 1.0000 & 0.0000 & 1.0000 & 0.0000 \\
-fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
+\#nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
+\#quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
+\#shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
+\#jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
+\#carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
+\#tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
+\#followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	-- &	-- \\
+\#followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
+\#follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
+\#egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
+\#retweet & 22 & 48 & 4.6991 & 13.4434 & 0.1570 & 0.1232 & 0.1353 & 0.0306 \\
+\#fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
+\#win & 20 & 0 & 4.2949 & 5.1856 & \textbf{0.0347} & 0.0221 & -- & -- \\
+\#tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & -- & -- \\
+\#music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & -- & -- \\
+\#in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & \textbf{0.0251} & 0.0206 \\
+\#imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
+\#nowwatching & 19 & 48 & 7.9110 & 8.6833 & 0.0672 & 0.0214 & 0.1293 & 0.0211 \\
+\#cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
+\#twexit & 18 & 48 & 12.5672 & 255.8178 & 0.3125 & 0.2148 & 0.2417 & 0.1783 \\
+\#lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
+\#fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & \textbf{0.2447} & 0.4635 & \textbf{0.2448} \\
+\#bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & -- & --  \\
+\#nemuritsuzuketeshinu & 17 & 48 & \textbf{314.1120} & \textbf{25053.5657} & \textbf{1.0000} & \textbf{0.0000} & \textbf{1.0000} & \textbf{0.0000} \\
+\#fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
 \end{tabular}
@@
 \begin{itemize}
-\item {\bf Temporal Sliding Window}\newline The query is executed and the n
-most recent results are retrieved every t minutes. The Temporal Sliding Window
-method may lead to duplicate messages in the retrieved documents, but needs to
-handle much less data and allows for an analysis over larger time frames.
-\item {\bf $k$-item Sliding Window}\newline  The k-item Sliding Window methods
-retrieves all messages that match the query exactly one time. Each time k new messages are
-available matching the given query a document containing those k messages
-is retrieved. This method can lead to high data volume and needs constant
-monitoring of recently posted messages matching the search term.
+\item {\bf Temporal Sliding Window}\newline The query is executed and the $n$
+most recent results are retrieved every $t$ minutes. The Temporal Sliding Window
+method may lead to duplicate messages in the retrieved documents.
+\item {\bf $k$-item Sliding Window}\newline  The $k$-item Sliding Window method
+retrieves all messages that match the query exactly one time. Each time $k$ new messages are
+available matching the given query a document containing those $k$ messages
+is retrieved. This method needs constant monitoring of recently posted messages matching the search term.
 \end{itemize}
@@
 
-For both data set queries were executed twice per hour using the Temporal
-Sliding Window method for data acquisition in a 24 hour time frame. Data for the
-trending topics was collected on 2011-02-24, for the frequent hash tags data was
+For our data set queries were executed twice per hour using the Temporal
+Sliding Window method in a 24 hour time frame. Data was
 collected on 2011-03-07\footnote{Collected data is available under
@@
 \begin{definition}[Evaluation Measures]
-Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, where each result set $R_i$ consists of twitter messages $r_i1,\ldots,r_iK$ with time stamps $t_i1,\ldots,t_iK$ we define:
+Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with sets of entities $E_1,\ldots,E_n$, where each result set $R_i$ consists of Twitter messages $r_i1,\ldots,r_iK$ with time stamps $t_i1,\ldots,t_iK$ we define:
 \begin{itemize}
-	\item The average update time within a result set $aut(R_i)$ for a query is the average time that lies between messages that match the query which produced the search result: $$aut(R_i)=\frac{\sum_{j=1}^{n}t_{i,j+1}-t_{i,j}}{K-1}$$
-	A high $aut(R)$ means that new messages that match the query are not generated very often. If new messages matching the query are frequently published, then the $adt(R)$ is low.
+	\item The average update time within a result set $aut(R_i)$ for a query is the average time that lies between messages that match the query which produced the search result: $$aut(R_i)=\frac{\sum_{j=1}^{K}t_{i,j+1}-t_{i,j}}{K-1}$$
+	A high $aut(R)$ means that new messages that match the query are not generated very often. If new messages matching the query are frequently published, then the $aut(R)$ is low.
 
-	The mean $aut(q)$ and the variance $autv(q)$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query.
+	The mean $E(aut(q))$ and the variance $Var(aut(q))$ of the $aut(R_i)$ can be used to describe update properties for the result sets that are generated for a given query.
 E.g.
-if for a given query $aut(q)$ is high and $autv(q)$ is low, then the rate at which messages are published is stable at a quite low level.
+if for a given query $E(aut(q))$ is high and $Var(aut(q))$ is low, then the rate at which messages are published is stable at a quite low level.
 %	\item The global stability $gs$ of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{|\bigcap_{i=1}^{n}E_i|}{|\bigcup_{i=1}^{n}E_i|}$$
@@
 
-	The variance of time stabilities $ts(q,t_i)$ over all $t_i$ helps to determine whether the rate at which the found entities change is rather stable or whether it is changing a lot over time.
+	The variance $Var(ts(q))$ of time stabilities $ts(q,t_i)$ over all $t_i$ helps to determine whether the rate at which the found entities change is rather stable or whether it is changing a lot over time.
 \end{itemize}
@@
 
-An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}.
+An overview of the results we obtained for the frequently used hashtags is given in Table~\ref{tbl:hashtags}.
+The most frequent entities for some of the tags are listed in Table~\ref{tbl:entities}.
 In total, we have analysed 48 result sets for each of the query tags.
@@
 $E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets.
-A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent.
-In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e.
+In our analysis estimated $aut$s range from $0.45$ seconds to $314.11$ seconds, i.e.
 approximately $5$ minutes.
 In order to avoid any duplicates in the result sets, an average update time of less than $18$ seconds is needed.
-Note that this value is only an average and does not guarantee disjointness of the result sets, as high update frequencies in one result set may outweigh low update frequencies in other result sets.
-Thus, we have additionally analysed the variance of the $aut$s.
-A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly.
+Note that update times below this value do not guarantee disjointness of the result sets, as the value is only an average, and high update frequencies in one result set may outweigh low update frequencies in other result sets.
+Additionally, we have analysed the variance of the $aut$s.
+A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hashtag were posted rather irregularly.
 In general, higher average update times are associated with a higher variance in the update times.
@@
 the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$.
-For these tags updates came at a relatively regular level.
+For these tags updates were published at a relatively regularly.
 
-We also report the average time stability over all time points as well as the variance for each hash tag.
+\begin{table}[ht]
+\centering
+\small
+\begin{tabular}{l|l|l|l}
+Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
+\hline
+$\#tilltheworldends$ & false & Britney Spears & .9583 \\
+& &  iTunes & .6875 \\
+& &  itunes & .625 \\ 
+\hline
+$\#nowplaying$ & false & iTunes & .5208 \\
+& & Michael Jackson & .333 \\
+& & Lady Gaga & .333 \\
+\hline
+$\#nowplaying$ & true & YouTube & .8235 \\
+& & Hip Hop Music & .6471 \\
+& & The Notorious B.I.G. & .5883 \\
+\hline
+$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
+& & Usher & .3125 \\
+& & Lil Wayne & .2917 \\
+\hline
+$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
+& & YouTube & .375 \\
+& & Ne-Yo & .315 \\
+\hline
+$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
+& & Twitter & .2291 \\
+& & twitter & .1667 \\
+\hline
+$\#thataintwinning$ & true & twitter & .5208 \\
+& & Twitter & .5 \\
+& & Two and a half men & .125 \\
+\hline
+$\#blackpeoplemovies$ & false & Devil & .4791 \\
+& & Tyler Perry & .2708 \\
+& & Harry Potter & .2292 \\
+\hline
+$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
+& & YouTube & 1 \\
+& & amazon.com & 1
+\end{tabular}
+\label{tbl:entities}
+\caption{Most frequent entities and their single term stabilities}
+\end{table}
+
+We also report the average time stability over all time points as well as the variance for each hashtag.
 A high time stability indicates that more or less the same entities were used for annotation at all times.
-The high stability of $1$ was achieved for the tag $\#nemuritsuzuketeshinu$, because no entities could be associated with the results of this search.
-This can be explained as the tag is only used by Japanese twitter users in Japanese twitter messages.
+The highest stabilities were achieved for the tags $\#nemuritsuzuketeshinu$ and $\#partiu$, because no (resp.
+very few) entities could be associated with the results of this search.
+This can be explained as the tags are only used in Japanese resp.
+Spanish Twitter messages.
 However, the Wikifier analyses the content of the results as being English text.
-A similar problem was encountered when analysing the trending topics in Germany.
-We assumed that these topics would mostly be tweeted about in German and thus called the German version of the Wikifier when analysing the results.
-However, it turned out that although the topics were trending in Germany, the tags were also used in messages in other languages.
-
-Surprisingly, the second highest stability value was reached with the tag $\#partiu$ which is mainly used in Spanish twitter messages. 
-\myremark{Uta}{Liegt auch an nichtgefundenen Entitäten}
+A solution could be to search only for English messages, however, this is not possible as Twitter messages have no language tags and location attributes are no sufficient indicator for the language in which a user will write messages.
 
 The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
-Accordingly, the entities which were most frequently used for annotation are "Britney Spears" ($95.83\%$), "iTunes" ($68.75\%$), "itunes" ($62.5\%$), "Itunes" ($31.25\%$), "Madonna\_(entertainer)" ($16.6\%$).
-The values in brackets indicate the single term stabilities for each of the terms.
-\myremark{Uta}{Weiß jemand, wie Madonna da reinkommt? Gibt es ne Erklärung für die unterschiedlichen Schreibweisen von iTunes? JA, liegt am Wikifier der keine normalisierten URIs zurückliefert}
+The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalized entities.
 
 Very low time stability was obtained for the tag $\#nowplaying$ which is used to tell which song one is currently listening to (a similarly low stability is obtained for the tag $\#np$ which is often used synonymously with $\#nowplaying$).
-As these messages contain all kinds of artist names and songs names.
-It is thus expected that the entities which are found vary between the result sets.
-In this case the most frequent entities were "iTunes" ($52.08\%$), "Michael Jackson" ($33.3\%$), "Lady Gaga" ($33.3\%$), "Lil Wayne" ($29.16\%$), "Katy Perry" ($22.92\%$).
-%\myremark{Uta}{In der Evaluationstabelle sollte dann auf jeden Fall noch dabei stehen, wie viele Resultsets wir zu den einzelnen Queries haben}
+As these messages contain all kinds of artist names and songs names, it is thus expected that the entities which are found vary between the result sets.
 
 The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing.
-\myremark{Uta}{Meine Hypothese wäre, dass es in Fällen, wo auf sehr unterschiedliche Quellen verwiesen wird, destabilisierend wirkt, in Fällen wo auf die gleichen/ähnliche Seiten verwiesen wird, stabilisierend - habe aber keine Daten, um das zu überprüfen.}
-\myremark{todo}{Hypothesis: high average update time leads to stable results}
+The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$.
+Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.
 
-\subsection{Discussion}
+\section{Related Work}
+\label{sect:relWork}
 
-@@@highlight the remarkable outcomes
-@@@what is did we learn from the results?
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
+
+The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
+Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
+The transformation is syntactic and does not include links to topics.
+
+Passant et al.
+\cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hashtags.
+The idea is to use URIs as hashtags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities on the Linked Data Web via these semantic hashtags.
+In contrast we do not require users to change their behavior by requiring them to use another type of hashtags. Instead, our method finds DBpedia entities which are related to the query automatically.
+
+Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks.
+They have instantiated their system to analyse data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming Twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide an actual method how this annotation can be achieved.
+
+Relating semantic concepts with Twitter messages has been attempted by various authors:
+Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
+% from stakovic et al.
+%In order to make tweets more searchable and make them useful for the described
+%scenario one would need to have represent them in a structured format and associate
+%those tweets with the topics that refer to. As a basic approach we process the text of
+%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+%concepts related to a tweet, but is useful only on a limited number of tweets directly
+%mentioning a particular topic. In the example data set we produced from ESWC2010,
+%tweet topics are represented using dc:subject property.
+Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages as input to the extraction component.
+
+Similar to our approach, Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.
+
+Kinsella et al.
+\cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
+We too use external data to augment the set of Twitter messages supplied to the Wikifier system in a variant of our method.
+
+The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
+The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hashtags to Wikipedia/DBpedia concepts.
 
@@
 
-@@@ not possible to map one hashtag to a single dbpedia concept: \#ka may be used for Karlsruhe or Ford Ka
+We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities, as well as an implementation and an evaluation of the approach.
 
-@@@ tricky to deal with different languages - wikifier (or any nlp technique) is language dependent, but the trending topics may be commented on in a variety of languages
+Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases.
+One reason is the use of hashtags in different contexts, another reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
 
-@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
+Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms.
+However, NLP techniques which are used to analyse the messages are language dependent.
+
+%@@@ how to select external data (parse text from HTML, which part of web page to select - boilerplate stuff might spoil the results (reference blog cleansing paper
 

### 2011-03-14 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 
-Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential over the last years.
+Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential.
 The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters.
@@
 
-On microblogging platforms it is possible to search for messages containing a specific hash tag.
-This search returns a fixed number of most recent messages containing the tag.
+On microblogging platforms it is possible to search for messages containing a specific hashtag.
+This search returns the most recent messages containing the tag.
 However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
 As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
-
 To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
@@
 In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities.
-While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for the annotation tool.
+While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
 Thus, we chose to generate annotations for the whole search result.
 
-The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia.
+Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
 The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
 Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
-Note however that a direct mapping of hash tags to entities is not possible in many cases: e.g.
-there is no entity in dbpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.
+External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible.
+Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g.
+there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not be mapped directly.
 
 Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
-In an evaluation of our approach we have tried to analyze the stability of the result.
+In an evaluation of our approach we have tried to analyse the stability of the result.
 
@@
 the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result.
+In the following we will illustrate our approach based on a search for the hashtag $\#Libya$, a hashtag
+which is frequently used to describe posts related to the country of Libya.
 
 The architecture of our proposed system is shown in Figure~\ref{fig:arch}. Upon
-receipt of a query $q$ four steps are performed. In the following we will illustrate
-these steps using the example of a search for the hash tag $\#Libya$, a hashtag
-which is frequently used to describe posts related to the country of Libya.
+receipt of a query $q$ four steps are performed.
 
@@
 for a single retrieved post is the following:
+{\small
 \begin{verbatim}
-"Arab League calls for no-fly zone in \#Libya 
-http://t.co/ZsLNIWa"}}
-\end{verbatim}
-,posted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
+"Arab League calls for no-fly zone in #Libya http://t.co/ZsLNIWa"
+\end{verbatim}}
+This messageposted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
 
@@
 the text found at the link should return the following text:
-\begin{verbatim}
-"Arab League calls for Libya no-fly zone-state TV - CAIRO, 
-March 12 (Reuters) - The Arab League on Saturday called on the
-U.N. Security Council to impose a no-fly zone on Libya, 
-Egyptian state television reported, a decision that would give
-a regional seal of approval that NATO has said is needed for 
-any military action."
-\end{verbatim}
+{\small\begin{verbatim}"Arab League calls for Libya no-fly zone-state TV - CAIRO, March 12
+(Reuters) - The Arab League on Saturday called on the U.N. Security 
+Council to impose a no-fly zone on Libya, Egyptian state television
+reported, a decision that would give a regional seal of approval
+that NATO has said is needed for any military action."\end{verbatim}}
 	\item In a third step entities matching the search result are retrieved. The
@@
 a regional seal of approval that NATO has said is needed for 
-any military action."}
-\end{verbatim}
+any military action."\end{verbatim}
 This string is appended to the Twitter content and the external content of all other posts in the result.
@@
 	triples to reference the DBPedia mappings:
-	\begin{verbatim}
-	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
+	{\small\begin{verbatim}	<http://km.aifb.kit.edu/services/twittersearchwrap/searchwrap
 	?q=\%23lybia>
@@
         <http://dbpedia.org/resource/Gaddafi> ,
-        <http://dbpedia.org/resource/Arab\_League> .
-  \end{verbatim}
+        <http://dbpedia.org/resource/Arab\_League> .\end{verbatim}}
 	The Twitter posts matching the search term \#Libya are likewise all described
@@
 	results in the following triples:
-	\begin{verbatim}
-	<http://km.aifb.kit.edu/services/twitterwrap/statuses/
+	{\small\begin{verbatim}<http://km.aifb.kit.edu/services/twitterwrap/statuses/
 	show/46619460060196865\#id> 
@@
 	   dc:description "Arab League calls for no-fly zone in \#Libya 
-			http://\newline t.co/ZsLNIWa" . 
-	\end{verbatim}
-
+	      http://\newline t.co/ZsLNIWa" . \end{verbatim}}     
 \end{enumerate}
@@
 
-In the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}} we provide an implementation of our approach.
+We provide an implementation of our approach in the Twitter Search Wrapper\footnote{Online at \url{http://km.aifb.kit.edu/services/twittersearchwrap/}}.
 
@@
 \item The optional step of dereferencing URLs which are posted in messages contained
-in the result set can be triggered using the option \texttt{extern=true} in our
-system. To keep the input size for the next steps manageable, we do not use the
-whole content of the referenced sites but only the first 50 words. The content
+in the result set can be triggered using the option \texttt{extern=true}. To keep the input size for the next steps manageable, only the first 50 words of the referenced sites are used. The content
 retrieved from external websites is beautified for our purpose removing
@@
 \item The Wikifier \cite{key:wikifier} is used for obtaining content annotations.
-This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analyzed text.
-It represents a state-of-the-art annotation tool.
-It was chosen as it allows for finding entities not from some tool-specific knowledge base but from dbpedia, which is one of the most widely used data sources within the Linked Open Data cloud.
+This tool takes a text as input and returns a set of Wikipedia entities which are relevant for the analysed text.
+It represents a state-of-the-art annotation tool and was chosen as it allows for finding entities not from some tool-specific knowledge base but from DBpedia, which is one of the most widely used data sources on the Linked Data Web.
 
 \item The system generates and outputs an RDF document in RDF/XML Syntax containing a
-description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. It describes
-the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin
-Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo
-Vocabulary \cite{key:geo}. A single twitter message is described by its
-individual page using \texttt{foaf:page} predicate. The date and time the
-message has been posted is specified using \texttt{dc:date} predicate. The messages content
-is annotated using \texttt{dc:description}, while the geographic location of the
-message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates. The
-creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that
-uses RDF to describe information related to a Twitter user which has previously
-been implemented here at the institute as the message creators URI.
-
-\end{itemize}
+description of the retrieved messages matching the search query for the given query and references to the DBpedia articles that have been returned by the Wikifier. 
+%It describes the result by means of the popular vocabularies FOAF \cite{key:foaf}, Dublin Core\footnote{\url{http://dublincore.org/documents/dcmi-terms/}}, the Basic Geo Vocabulary \cite{key:geo}.
+A single Twitter message is described by its individual page using the \texttt{foaf:page} predicate.
+The date and time the message has been posted is specified using the \texttt{dc:date} predicate.
+The message's content is annotated using \texttt{dc:description}, while the geographic location of the message is indicated by \texttt{geo:lat} and \texttt{geo:long} predicates.
+The creator of the Twitter message is referenced by \texttt{foaf:maker} predicate which points to a service that uses RDF to describe information related to a Twitter user which has previously been implemented here at the institute as the message creators URI.
 
@@
 
-We have conducted experiments on a set of queries which were identified to be hash tags which are frequently used on Twitter.
+We have conducted experiments on a set of queries which were identified to be hashtags which are frequently used on Twitter.
 To obtain these, we have sampled the Twitter message feed using Twitter's
@@
 \hline
-ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
-np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
-nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
-winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
-fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\
-rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
-mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
-blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
-tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
-thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
-fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
-teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
-iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
-bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
-news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
-jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
-libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
-followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\
-partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
-sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\
-damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
-tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
-soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
-nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\
-quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
+\#ff &     460 & 48 & 2.2936 & 0.7014 & 0.1268 & 0.0681 & 0.2037 & 0.0281 \\
+\#np &     172 & 48 & 0.4737 & 0.0287 & 0.0655 & 0.0196 & 0.0717 & 0.0195\\
+\#nowplaying & 144 & 17 & \textbf{0.4514} & \textbf{0.0251} & 0.0565 & 0.0198 & 0.0458 & 0.0212 \\
+\#winning &     134 & 48 & 0.8236 & 0.2365 & 0.1101 & 0.0666 & 0.1816 & 0.0272 \\
+\#fb & 105 & 1 & 1.1705 & 1.1826 & 0.1083 & 0.0933 & -- & -- \\
+\#rt & 83 & 48 & 1.7980 & 3.7309 & 0.0979 & 0.0763 & 0.1487 & 0.0267 \\
+\#mentionke & 61 & 48 & 7.5459 & 195.6829 & 0.1406 & 0.0921 & 0.2215 & 0.0408 \\
+\#blackpeoplemovies & 57 & 3 & 90.6195 & 2007.5551 & 0.3327 & 0.0606 & 0.0349 & 0.0244\\
+\#tigerblood & 56 & 48 & 3.4029 & 4.8740 & 0.1497 & 0.0692 & 0.2330 & 0.0278 \\
+\#thataintwinning & 53 & 48 & 16.8075 & 236.8694 & 0.0768 & 0.0435 & 0.1668 & 0.0387 \\
+\#fail & 53 & 48 & 2.3356 & 2.0669 & 0.1927 & 0.1517 & 0.1073 & 0.0460 \\
+\#teamfollowback & 52 & 48 & 0.9269 & 0.4871 & 0.1912 & 0.0932 & 0.1813 & 0.0245 \\
+\#iftwitterwashighschool & 51 & 48 & 114.8342 & 1771.4564 & 0.5113 & 0.0405 & 0.5144 & 0.0352 \\
+\#bieberfact & 51 & 48 & 11.0126 & 63.0455 & 0.0587 & 0.0290 & 0.0765 & 0.0270 \\
+\#news & 46 & 0 & 1.8696 & 0.1943 & 0.1024 & 0.0210 & -- & --  \\
+\#jobs & 45 & 0 & 1.3866 & 0.4198 & 0.1006 & 0.0192 & -- & -- \\
+\#libya & 44 & 1 & 16.0309 & 117.2024 & 0.2701 & 0.0427 & -- & -- \\
+\#followmejp & 44 & 0	& 1.5398 & 0.1255 & 0.0688 & 0.0410 & -- & --\\
+\#partiu & 41 & 48 & 7.5809 & 84.0531 & 0.6042 & 0.2391 & 0.5313 & 0.2438 \\
+\#sougofollow & 39 & 0 & 2.1010 & 0.1820 & 0.0720 & 0.0427 & -- & -- \\
+\#damnitstrue & 39 & 48 & 5.7507 & 16.5725 & 0.1805 & 0.1387 & 0.2177 & 0.1579 \\
+\#tilltheworldends & 37 & 48 & 85.4526 & 1366.8588 & 0.5682 & 0.0709 & 0.5116 & 0.0324 \\
+\#soalcinta & 35 & 48 & 8.4143 & 103.7817 & 0.3451 & 0.1987 & 0.3120 & 0.2014 \\
+\#nicovideo & 35 & 0 & 51.0720 & 5521.3529 & 0.3604 & 0.1893 & -- & -- \\
+\#quran & 33 & 48 & 45.8290 & 90.4157 & 0.4271 & 0.0501 & 0.4188 & 0.0387 \\
 %\end{tabular}
@@
 %\hline
-nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
-quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
-shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
-jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
-carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
-tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
-followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	-- &	-- \\
-followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
-follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
-egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
-retweet & 22 & 48 & 4.6991 & 13.4434 & 0.1570 & 0.1232 & 0.1353 & 0.0306 \\
-fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
-win & 20 & 0 & 4.2949 & 5.1856 & \textbf{0.0347} & 0.0221 & -- & -- \\
-tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & -- & -- \\
-music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & -- & -- \\
-in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & \textbf{0.0251} & 0.0206 \\
-imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
-nowwatching & 19 & 48 & 7.9110 & 8.6833 & 0.0672 & 0.0214 & 0.1293 & 0.0211 \\
-cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
-twexit & 18 & 48 & 12.5672 & 255.8178 & 0.3125 & 0.2148 & 0.2417 & 0.1783 \\
-lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
-fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & \textbf{0.2447} & 0.4635 & \textbf{0.2448} \\
-bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & -- & --  \\
-nemuritsuzuketeshinu & 17 & 48 & \textbf{314.1120} & \textbf{25053.5657} & \textbf{1.0000} & \textbf{0.0000} & \textbf{1.0000} & \textbf{0.0000} \\
-fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
+\#nw & 32 & 48 & 2.6054 & 2.1094 & 0.0672 & 0.0231 & 0.0901 & 0.0418 \\
+\#quote & 31 & 48 & 4.3007 & 0.5706 & 0.1074 & 0.0197 & 0.1012 & 0.0212 \\
+\#shoutout & 30 & 48 & 2.6030 & 3.3256 & 0.2347 & 0.0987 & 0.2526 & 0.0488 \\
+\#jfb & 30 & 48 & 23.9911 & 1453.3113 & 0.2483 & 0.1654 & 0.2158 & 0.1379 \\
+\#carnaval & 27 & 48 & 34.2574 & 1100.9818 & 0.3229 & 0.2134 & 0.2578 & 0.1646 \\
+\#tfb & 26 & 48 & 2.5994 & 0.8777 & 0.2292 & 0.1766 & 0.1760 & 0.0319 \\
+\#followme & 26 & 0 & 3.2194 & 0.4650 & 0.1209 & 0.0952 &	-- &	-- \\
+\#followfriday & 25 & 48 & 13.6749 & 20.0701 & 0.1910 & 0.1152 & 0.2060 & 0.0676 \\
+\#follow & 24 & 48 & 3.0945 & 1.9622 & 0.2916 & 0.1927 & 0.2046 & 0.0305 \\
+\#egypt & 23 & 16 & 3.1850 & 3.2745 & 0.1357 & 0.0239 & 0.0704 & 0.0263 \\
+\#retweet & 22 & 48 & 4.6991 & 13.4434 & 0.1570 & 0.1232 & 0.1353 & 0.0306 \\
+\#fact & 22 & 48 & 5.5613 & 12.0766 & 0.0915 & 0.0762 & 0.0783 & 0.0612 \\
+\#win & 20 & 0 & 4.2949 & 5.1856 & \textbf{0.0347} & 0.0221 & -- & -- \\
+\#tweetmyjobs & 20 & 0 & 35.5697 & 1590.6997 & 0.3244 & 0.0621 & -- & -- \\
+\#music & 20 & 1 & 4.4665 & 4.6392 & 0.0833 & 0.0196 & -- & -- \\
+\#in & 20 & 3	& 8.2367 & 6.8944 & 0.0649 & 0.0236 & \textbf{0.0251} & 0.0206 \\
+\#imagine & 20 & 48	& 8.3378 & 30.4317 & 0.2465 & 0.1759 & 0.1813 & 0.1375 \\
+\#nowwatching & 19 & 48 & 7.9110 & 8.6833 & 0.0672 & 0.0214 & 0.1293 & 0.0211 \\
+\#cumannanyaindonesia & 19 & 48 & 77.9680 & 2739.7782 & 0.3901 & 0.1885 & 0.4323 & 0.2033 \\
+\#twexit & 18 & 48 & 12.5672 & 255.8178 & 0.3125 & 0.2148 & 0.2417 & 0.1783 \\
+\#lcv & 18 & 48 & 28.6309 & 477.9193 & 0.4236 & 0.2395 & 0.2813 & 0.1969 \\
+\#fui & 18 & 48 & 11.5515 & 165.3850 & 0.4896 & \textbf{0.2447} & 0.4635 & \textbf{0.2448} \\
+\#bot &      18 & 1 & 13.3533 &	8.2469 & 0.2708 & 0.1975 & -- & --  \\
+\#nemuritsuzuketeshinu & 17 & 48 & \textbf{314.1120} & \textbf{25053.5657} & \textbf{1.0000} & \textbf{0.0000} & \textbf{1.0000} & \textbf{0.0000} \\
+\#fato & 17 & 48 & 17.6223 & 569.5627 & 0.1875 & 0.1523 & 0.2353 & 0.1304 \\
 \end{tabular}
@@
 
-An overview of the results we obtained for the frequently used hash tags is given in Table~\ref{tbl:hashtags}.
+An overview of the results we obtained for the frequently used hashtags is given in Table~\ref{tbl:hashtags}.
 The most frequent entities for some of the tags are listed in Table~\ref{tbl:entities}.
@@
 $E(aut)$ and $Var(aut)$ give the results for analysing the average update times of the result sets.
-A low $E(aut)$ means that updates are frequently posted, a high $E(aut)$ means that updates are rather infrequent.
-In the case of our analysis estimated update frequencies range from $0.45$ seconds to $314.11$ seconds, i.e.
+In our analysis estimated $aut$s range from $0.45$ seconds to $314.11$ seconds, i.e.
 approximately $5$ minutes.
@@
 Note that update times below this value do not guarantee disjointness of the result sets, as the value is only an average, and high update frequencies in one result set may outweigh low update frequencies in other result sets.
-Thus, we have additionally analysed the variance of the $aut$s.
-A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hash tag were posted rather irregularly.
+Additionally, we have analysed the variance of the $aut$s.
+A low variance means that the update intervals remain relatively stable over time, while a high variance indicates that messages using the hashtag were posted rather irregularly.
 In general, higher average update times are associated with a higher variance in the update times.
@@
 the case for the tags $\#bieberfact$, $\#quran$, $\#followfriday$.
-For these tags updates came at a relatively regular level.
+For these tags updates were published at a relatively regularly.
 
@@
 \centering
+\small
 \begin{tabular}{l|l|l|l}
-Tag & extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
+Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
 \hline
-$\#tilltheworldends$ & false & Britney Spears .9583 \\
+$\#tilltheworldends$ & false & Britney Spears & .9583 \\
 & &  iTunes & .6875 \\
 & &  itunes & .625 \\ 
+\hline
 $\#nowplaying$ & false & iTunes & .5208 \\
@@
 & & Lady Gaga & .333 \\
+\hline
 $\#nowplaying$ & true & YouTube & .8235 \\
@@
 & & The Notorious B.I.G. & .5883 \\
+\hline
 $\#np$ & false & Chris Brown\_(entertainer) & .5 \\
@@
 & & Lil Wayne & .2917 \\
+\hline
 $\#np$ & true & Chris Brown\_(entertainer) & .5 \\
@@
 & & Ne-Yo & .315 \\
+\hline
 $\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
@@
 & & twitter & .1667 \\
+\hline
 $\#thataintwinning$ & true & twitter & .5208 \\
@@
 & & Two and a half men & .125 \\
+\hline
 $\#blackpeoplemovies$ & false & Devil & .4791 \\
@@
 & & Harry Potter & .2292 \\
+\hline
 $\#blackpeoplemovies$ & true & Amazon.com & 1 \\
@@
 
-We also report the average time stability over all time points as well as the variance for each hash tag.
+We also report the average time stability over all time points as well as the variance for each hashtag.
 A high time stability indicates that more or less the same entities were used for annotation at all times.
@@
 This can be explained as the tags are only used in Japanese resp.
-Spanish twitter messages.
+Spanish Twitter messages.
 However, the Wikifier analyses the content of the results as being English text.
@@
 The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
-The different URIs which are used for annotation are explained by the fact, that the Wikifier does not return normalized entities.
+The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalized entities.
 
@@
 The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$.
-Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hash tags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.
+Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.
+
+\section{Related Work}
+\label{sect:relWork}
+
+Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.
+
+The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
+Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
+The transformation is syntactic and does not include links to topics.
+
+Passant et al.
+\cite{key:smob} have proposed a data model for making Twitter data available on the Semantic Web.
+They propose a data model which allows for the association of URIs with users, microblogs and microposts.
+To this end, SIOC and FOAF vocabularies are used and extended.
+Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced.
+Additionally, they propose the use of so-called semantic hashtags.
+The idea is to use URIs as hashtags (e.g.
+\emph{\#geo:Paris\_France}).
+It becomes thus possible to link microposts to entities on the Linked Data Web via these semantic hashtags.
+In contrast we do not require users to change their behavior by requiring them to use another type of hashtags. Instead, our method finds DBpedia entities which are related to the query automatically.
+
+Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks.
+They have instantiated their system to analyse data from Twitter.
+In their system, they collect data from one or several users.
+The system by Passant et al.
+\cite{key:smob} is used for transforming Twitter data to semantic data.
+The triplified data can then be analysed using SPARQL.
+They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide an actual method how this annotation can be achieved.
+
+Relating semantic concepts with Twitter messages has been attempted by various authors:
+Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages. 
+% from stakovic et al.
+%In order to make tweets more searchable and make them useful for the described
+%scenario one would need to have represent them in a structured format and associate
+%those tweets with the topics that refer to. As a basic approach we process the text of
+%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
+%concepts related to a tweet, but is useful only on a limited number of tweets directly
+%mentioning a particular topic. In the example data set we produced from ESWC2010,
+%tweet topics are represented using dc:subject property.
+Instead of mining single messages which provide little signal to the extraction algorithm we use an aggregation of messages as input to the extraction component.
+
+Similar to our approach, Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction. As such, our approach is closely related.
+
+Kinsella et al.
+\cite{key:kinsella} use hyperlinks in posts to derive a richer representation of those posts.
+We too use external data to augment the set of Twitter messages supplied to the Wikifier system in a variant of our method.
+
+The challenge task in the WePS-3 Online Reputation Management Task\cite{key:clef} requires systems to detect mentions of company names in Twitter messages.
+The corpus contains evaluation results solicited via Mechanical Turk. In contrast to the WePS-3 task, we associate generic hashtags to Wikipedia/DBpedia concepts.
 
@@
 
-We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities.
+We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities, as well as an implementation and an evaluation of the approach.
+
 Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases.
-One reason is the use of hashtags in different contexts, another reason is that hash tags do not necessarily describe an entity, but are rather used to describe contexts.
+One reason is the use of hashtags in different contexts, another reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
 
 Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms.
-However, NLP techniques which are used to analyze the messages are language dependent.
+However, NLP techniques which are used to analyse the messages are language dependent.
 

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex
rewrote abstract and intro

@@
 \author{Uta L\"{o}sch \and David M\"{u}ller \and Andreas Harth}
-\institute{
-	Karlsruhe Institute of Technology (KIT), D-76131 Karlsruhe, Germany\\ 
+\institute{Institute AIFB, Karlsruhe Institute of Technology (KIT), Germany\\ 
 	\email{uta.loesch@kit.edu},\\
@@
 \begin{abstract}
-Microblog messages contain so-called hashtags which are usedto mark keywords or topics.
-To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context.
-In an evaluation we analyse the stability of the related entities.
+Microblog posts may contain so-called hashtags that mark keywords or topics.
+Hashtags are used in an ad-hoc fashion; the meaning of hashtags is implicitly defined via their use, which makes understanding and querying hashtags difficult.
+In this paper we devise a method for annotating microblog posts which contain hashtags with related encyclopedia entities.
+% that best describe the hashtag.
+Thus, users have the means to quickly grasp the meaning of a hashtag, and gain starting points for further exploration of the hashtags' context.
+%By relating the hashtags to external content, users 
+We implement two variants of our method based on an existing system for linking content to Wikipedia and analyse the stability of annotated  Twitter search results for popular hashtags.
 \end{abstract}
 
+\nop{
 Keywords: Twitter, Wikipedia, DBpedia, RDF
 
-\nop{
 http://tagdef.com/ has a list of popular tags
@@
 
-Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential over the last years.
-The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million Twitter messages a day.
-Thus, Twitter represents a huge data source on the web.
+Microblogging services allow users to publish short messages online.
+Twitter\footnote{\url{http://twitter.com/}} is the largest dedicated microblogging site; as of March 2011, its users create an average of 140 millions post a day\footnote{\url{http://blog.twitter.com/2011/03/numbers.html}}.
+Given a 140-character limit for posts, Twitter users invented shortcuts for certain expressions.
+So-called hashtags (starting with a \# sign followed by a keyword) are frequently used to associate posts with a specific topic, place, person or event.
+For example, posts covering current events in Lybia are frequently tagged with $\#Libya$.
+%the Extended Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
 
-On microblogging platforms it is possible to search for messages containing a specific hashtag.
-This search returns a fixed number of most recent messages containing the tag.
-However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
-As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+Hashtags can help to organise microblog messages and thus are useful for supporting search.
+Microblogging platforms offer functionality to search for messages containing a specific hashtag.
+%This search returns the most recent messages containing the tag.
+However, as hashtags are implicitly defined via their use, the meaning of a hashtag is often unclear.
+Services such as tagdef\footnote{\url{http://www.tagdef.com/}} provide means to provide a definition of a hashtag, but these services rely on user input and thus only cover a subset of all hashtags.
+In addition, since hashtags are not related to other structured information sources, querying is limited to direct keyword search.
 
-To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+We propose a method to associate hashtags to encyclopedia entities.
+In our experiments we use Wikipedia as entity source which covers a wide range of topics.
+Furthermore, automatic tools for annotating text with Wikipedia entities are readily available, for example Milne and Witten's Wikifier \cite{key:wikifier}.
+Wikipedia entities are widely linked to external data sources via DBpedia \cite{key:dbpedia}, thus combined querying of DBpedia and Twitter becomes possible.
 
-Furthermore, this annotation will help to understand hashtags.
-Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms.
-For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
-If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
-However, understanding a search result is difficult and time-consuming.
-Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
-These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.
+Matching entities in microposts is a difficult problem \cite{key:clef} as microblog post are very short and contain little information.
+Our approach uses search results for a given hashtag as input to the entity matching component and returns messages using the hashtag including a set of related Wikipedia entities.
+% which have been detected in the search result.
+The matched entities not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+%These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.
+
+%with a set of entities which reflect the content of the result feeds.
+%, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+%grasp the context of the results and to get further information on the topic that was searched for.
+%To facilitate this putting into context of the search results, 
+%Furthermore, this annotation will help to understand hashtags. 
+%If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
+%However, understanding a search result is difficult and time-consuming.
+
+\nop{
+Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
+}
+
+In this paper, we present a method to automatically annotate hashtag search results with encyclopedia entities.
 If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag.
-A system may be envisioned which automatically finds entitities which are equivalent to a hashtag.
-Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.
-
-Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
-Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used.
-For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
-The tag $\#ka$ is however also used in the context of the car type Ford Ka.
-Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
-An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.
-
-In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities.
-While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
-Thus, we chose to generate annotations for the whole search result.
-
-The implementation we provide is based on Twitter, as it is the most widely used and biggest microblogging platform, and on Wikipedia.
-The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
-Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
-External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible.
-Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g.
-there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not mapped directly.
-
+We envision a system which automatically finds entities equivalent to a hashtag.
+%While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
+%Thus, we chose to generate annotations for the whole search result. 
+%Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
 Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
-In an evaluation of our approach we have tried to analyse the stability of the result.
+In an evaluation of our approach we analyse the stability of the results of the entity matching for hashtag search results.
 
@@
 \begin{itemize}
-	\item We present an approach for finding entities which are related to search results on microblogging platforms
-	\item We specify a formatting of microblogging messages as RDF
+	\item We present an approach for finding entities which are related to search results on microblogging platforms.
+%	\item We specify a formatting of microblogging messages as RDF.
 	\item We evaluate the stability of the found entities.
@@
 
-The remainder of this paper is organized as follows: in Section~\ref{sect:relWork} we discuss related work, in Section~\ref{sect:method} we present our approach, the results of our evaluation are presented in Section~\ref{sect:eval}, before we conclude in Section~\ref{sect:conclusion}.
+The remainder of this paper is organised as follows: Section~\ref{sect:method} overviews the approach,
+Section~\ref{sect:impl} presents the implementation,
+Section~\ref{sect:eval} covers the results of the evaluation,
+Section~\ref{sect:relWork} discusses related work and  Section~\ref{sect:conclusion} concludes.
 
@@
 
-The goal of our method is to, given a search query $q$ as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e.
+The goal of our method is, given a search query $q$ as input, to provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/}} document describing the search result $R$, i.e.
 the most recent messages that match the query, the authors of these messages and the most relevant entities $E$ for this result.
@@
 \end{verbatim}}
-This messageposted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geotagged} and the date the message has been posted are furthermore known.
+This message posted by Twitter user \texttt{SenJohnMcCain}; geo coordinates\footnote{The original Twitter message posted by SenJohnMcCain was not geo-tagged} and the date the message has been posted are furthermore known.
 
@@
 \url{http://t.co/ZsLNIWa}, which redirects to an article on the situation in
-Libya published on \url{http://reuters.com}. Dereferencing this URL and grabbing
+Libya published on \url{http://reuters.com/}. Dereferencing this URL and grabbing
 the text found at the link should return the following text:
@@
 a regional seal of approval that NATO has said is needed for 
-any military action."\end{verbatim}
+any military action."
+\end{verbatim}
 This string is appended to the Twitter content and the external content of all other posts in the result.
@@
 \section{Implementation}
+\label{sect:impl}
 
@@
 Streaming API for one minute twice an hour from 2011-03-03 to 2011-03-06. The
-top-50 hashtags dervied from the aggregate sample are listed in Table
+top-50 hashtags derived from the aggregate sample are listed in Table
 \ref{tbl:hashtags}, count is the number of times we encountered them during the
@@
 \hline
-$\#tilltheworldends$ & false & Britney Spears & .9583 \\
+\#tilltheworldends & false & Britney Spears & .9583 \\
 & &  iTunes & .6875 \\
@@
 \hline
-$\#nowplaying$ & false & iTunes & .5208 \\
+\#nowplaying & false & iTunes & .5208 \\
 & & Michael Jackson & .333 \\
@@
 \hline
-$\#nowplaying$ & true & YouTube & .8235 \\
+\#nowplaying & true & YouTube & .8235 \\
 & & Hip Hop Music & .6471 \\
@@
 \hline
-$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
+\#np & false & Chris Brown\_(entertainer) & .5 \\
 & & Usher & .3125 \\
@@
 \hline
-$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
+\#np & true & Chris Brown\_(entertainer) & .5 \\
 & & YouTube & .375 \\
@@
 \hline
-$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
+\#thataintwinning & false & Mozilla Firefox & .2291 \\
 & & Twitter & .2291 \\
@@
 \hline
-$\#thataintwinning$ & true & twitter & .5208 \\
+\#thataintwinning & true & twitter & .5208 \\
 & & Twitter & .5 \\
@@
 \hline
-$\#blackpeoplemovies$ & false & Devil & .4791 \\
+\#blackpeoplemovies & false & Devil & .4791 \\
 & & Tyler Perry & .2708 \\
@@
 \hline
-$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
+\#blackpeoplemovies & true & Amazon.com & 1 \\
 & & YouTube & 1 \\
@@
 The third highest stability was achieved by the tag $\#tilltheworldends$ which refers to Britney Spears' newest single.
-The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalized entities.
+The different spellings of iTunes which are used for annotation occur as the Wikifier does not return normalised entities.
 
@@
 
-The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilizing.
-The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occured for the tag $\#blackpeoplemovies$.
-Our hypothesis is that destabilization occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilizing.
+The effect of considering external content in the annotation is beneficial in some cases, in others the effect was destabilising.
+The highest decrease in stability was observed for the tag $\#thataintwinning$, the highest increase occurred for the tag $\#blackpeoplemovies$.
+Our hypothesis is that de-stabilisation occurs especially in cases where the posted links cover a variety of topics, while for more specific hashtags referenced web sites are more likely to cover a specific topics and will thus be stabilising.
 
@@
 
-The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
+The SemanticTweet\footnote{\url{http://semantictweet.com/}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter.
 Thus, an automatic way of mapping the Twitter social network to semantic data is made available.
@@
 The triplified data can then be analysed using SPARQL.
-They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide an actual method how this annotation can be achieved.
+They propose that the result data could be enriched using entities from other Linked Open Data vocabularies like DBpedia\footnote{\url{http://dbpedia.org/}} or GeoNames\footnote{\url{http://www.geonames.org/}}, but they do not provide an actual method how this annotation can be achieved.
 
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \label{sect:conclusion}
 
-We have presented an approach for annotating search results on microblogging platforms with Wikipedia entities, as well as an implementation and an evaluation of the approach.
+We have presented an approach for annotating Twitter hashtags with Wikipedia entities.
+We have described an implementation of two variants of the method and evaluated the approach.
 
-Our evaluation has shown that a direct mapping of hashtags to a single dbpedia concept is not possible in many cases.
-One reason is the use of hashtags in different contexts, another reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
+Our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
+One reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
+Another reason is the use of hashtags for different entities.
+For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
+The tag $\#ka$ is however also used to denote the car type Ford Ka.
+Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
+An approach which aims at finding relevant entities for a given search will have to be able to disambiguate homonym hashtags.
+%deal with these problems.
 
-Another difficult problem we encountered is that different languages have to be dealt with: Topics are often commented on in a variety of languages on microblogging platforms.
-However, NLP techniques which are used to analyse the messages are language dependent.
+An issue we have encountered is that different languages have to be dealt with: topics are often commented on in a variety of languages, and the built-in language identifiers are often incorrect.
+As the entity matching system is language-dependent we would need to include a language detection component in future versions of the system.
+
+%Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g.
+there is no entity in DBpedia which describes the Extended Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not be mapped directly.
+%Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used.
 

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex
updated table 2

@@
 \usepackage{latexsym}
+\usepackage{multirow}
 
@@
 \small
-\begin{tabular}{l|l|l|l}
-Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
+\begin{tabular}{l|l|l|l|l}
+Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
 \hline
-\#tilltheworldends & false & Britney Spears & .9583 \\
-& &  iTunes & .6875 \\
-& &  itunes & .625 \\ 
+\#tilltheworldends & - & false & Britney Spears & .9583 \\
+& & &  iTunes & .6875 \\
+& & &  itunes & .625 \\ 
 \hline
-\#nowplaying & false & iTunes & .5208 \\
-& & Michael Jackson & .333 \\
-& & Lady Gaga & .333 \\
+\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
+             & are currently listening & & Michael Jackson & .333 \\
+             & to. & & Lady Gaga & .333 \\
 \hline
-\#nowplaying & true & YouTube & .8235 \\
-& & Hip Hop Music & .6471 \\
-& & The Notorious B.I.G. & .5883 \\
+\#nowplaying & same & true & YouTube & .8235 \\
+             &  &  & Hip Hop Music & .6471 \\
+             &  &  & The Notorious B.I.G. & .5883 \\
 \hline
-\#np & false & Chris Brown\_(entertainer) & .5 \\
-& & Usher & .3125 \\
-& & Lil Wayne & .2917 \\
+\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
+& & & Usher & .3125 \\
+& & & Lil Wayne & .2917 \\
 \hline
-\#np & true & Chris Brown\_(entertainer) & .5 \\
-& & YouTube & .375 \\
-& & Ne-Yo & .315 \\
+\#np & same & true & Chris Brown\_(entertainer) & .5 \\
+& & & YouTube & .375 \\
+& & & Ne-Yo & .315 \\
 \hline
-\#thataintwinning & false & Mozilla Firefox & .2291 \\
-& & Twitter & .2291 \\
-& & twitter & .1667 \\
+\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
+& & & Twitter & .2291 \\
+& & & twitter & .1667 \\
 \hline
-\#thataintwinning & true & twitter & .5208 \\
-& & Twitter & .5 \\
-& & Two and a half men & .125 \\
+\#thataintwinning & - & true & twitter & .5208 \\
+& & & Twitter & .5 \\
+& & & Two and a half men & .125 \\
 \hline
-\#blackpeoplemovies & false & Devil & .4791 \\
-& & Tyler Perry & .2708 \\
-& & Harry Potter & .2292 \\
+\#blackpeoplemovies & - & false & Devil & .4791 \\
+& & & Tyler Perry & .2708 \\
+& & & Harry Potter & .2292 \\
 \hline
-\#blackpeoplemovies & true & Amazon.com & 1 \\
-& & YouTube & 1 \\
-& & amazon.com & 1
+\#blackpeoplemovies & - & true & Amazon.com & 1 \\
+& & & YouTube & 1 \\
+& & & amazon.com & 1
 \end{tabular}

### 2011-03-14 trunk/lids/twittersearchwrap/paper/paper.tex
removed commented out parts in abstract

@@
 \begin{abstract}
-Microblog messages contain so-called hashtags which are usedto mark keywords or topics.
-To facilitate understanding the meaning of a hashtag in the context of microblog, we have developed a system which annotates hashtags based on Twitter search results with encyclopedia entities that best describe the hashtag, thus offering means of quickly grasping the meaning of the hashtag and relating the hashtags to external content, thus providing starting points for further exploration of the hashtags' context.
-In an evaluation we analyse the stability of the related entities.
+Microblog posts may contain so-called hashtags that mark keywords or topics.
+Hashtags are used in an ad-hoc fashion; the meaning of hashtags is implicitly defined via their use, which makes understanding and querying hashtags difficult.
+In this paper we devise a method for annotating microblog posts which contain hashtags with related encyclopedia entities.
+Thus, users have the means to quickly grasp the meaning of a hashtag, and gain starting points for further exploration of the hashtags' context.
+We implement two variants of our method based on an existing system for linking content to Wikipedia and analyse the stability of annotated  Twitter search results for popular hashtags.
 \end{abstract}
 
+\nop{
 Keywords: Twitter, Wikipedia, DBpedia, RDF
 
-\nop{
 http://tagdef.com/ has a list of popular tags
@@
 
-Microblogging has become more and more popular over the last years, especially with the most prominent and most widely used microblogging platform Twitter\footnote{\url{http://twitter.com}} which has become very influential.
-The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of Twitter the restriction is 140 characters.
-Twitter has a total of about 190 million of users who produce 65 million Twitter messages a day.
-Thus, Twitter represents a huge data source on the web.
+Microblogging services allow users to publish short messages online.
+Twitter\footnote{\url{http://twitter.com/}} is the largest dedicated microblogging site; as of March 2011, its users create an average of 140 millions post a day\footnote{\url{http://blog.twitter.com/2011/03/numbers.html}}.
+Given a 140-character limit for posts, Twitter users invented shortcuts for certain expressions.
+So-called hashtags (starting with a \# sign followed by a keyword) are frequently used to associate posts with a specific topic, place, person or event.
+For example, posts covering current events in Lybia are frequently tagged with $\#Libya$.
+%the Extended Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
 
-On microblogging platforms it is possible to search for messages containing a specific hashtag.
-This search returns the most recent messages containing the tag.
-However, it is hard to grasp the context of the results and to get further information on the topic that was searched for.
-As each single microblog post is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
-To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds.
-These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+Hashtags can help to organise microblog messages and thus are useful for supporting search.
+Microblogging platforms offer functionality to search for messages containing a specific hashtag.
+%This search returns the most recent messages containing the tag.
+However, as hashtags are implicitly defined via their use, the meaning of a hashtag is often unclear.
+Services such as tagdef\footnote{\url{http://www.tagdef.com/}} provide means to provide a definition of a hashtag, but these services rely on user input and thus only cover a subset of all hashtags.
+In addition, since hashtags are not related to other structured information sources, querying is limited to direct keyword search.
 
-Furthermore, this annotation will help to understand hashtags.
-Hash tags are frequently used to associate messages with a specific topic, place, person or event on microblogging platforms.
-For example, messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$.
-If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
-However, understanding a search result is difficult and time-consuming.
-Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result.
-These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.
+We propose a method to associate hashtags to encyclopedia entities.
+In our experiments we use Wikipedia as entity source which covers a wide range of topics.
+Furthermore, automatic tools for annotating text with Wikipedia entities are readily available, for example Milne and Witten's Wikifier \cite{key:wikifier}.
+Wikipedia entities are widely linked to external data sources via DBpedia \cite{key:dbpedia}, thus combined querying of DBpedia and Twitter becomes possible.
+
+Matching entities in microposts is a difficult problem \cite{key:clef} as microblog post are very short and contain little information.
+Our approach uses search results for a given hashtag as input to the entity matching component and returns messages using the hashtag including a set of related Wikipedia entities.
+% which have been detected in the search result.
+The matched entities not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.
+%These entities will help the user to gain an understanding in which context the hashtag is used and what it may mean.
+
+%with a set of entities which reflect the content of the result feeds.
+%, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used.
+%grasp the context of the results and to get further information on the topic that was searched for.
+%To facilitate this putting into context of the search results, 
+%Furthermore, this annotation will help to understand hashtags. 
+%If users encounter this hashtag and do not understand it, they can search for it on the microblogging platform.
+%However, understanding a search result is difficult and time-consuming.
+
+\nop{
+Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
+}
+
+In this paper, we present a method to automatically annotate hashtag search results with encyclopedia entities.
 If a hashtag can be associated with an entity with high confidence, the entity can be seen as descriptive for the hashtag.
-A system may be envisioned which automatically finds entitities which are equivalent to a hashtag.
-Thus, these hashtag-entity pairs may be used similarly to systems in which hashtags can be defined manually, such as is possible on \#tagdef\footnote{\url{http://www.tagdef.com}}.
-
-Finding entities matching a query, especially a query for a given hashtag is difficult as little context is available due to the short length of each single message.
-Additional problems are due to synonyms and homonyms in the set of hashtags that are frequently used.
-For example, both the hashtags $\#ka$ and $\#karlsruhe$ are frequently used when talking about topics which are related to the city Karlsruhe.
-The tag $\#ka$ is however also used in the context of the car type Ford Ka.
-Thus, when searching for $\#ka$ on a microblogging platform, messages relating to Karlsruhe will be found as well as messages related to Ford Ka.
-An approach which aims at finding relevant entities for a given search will have to be able to deal with these problems.
-
-In this paper, we present a system which automatically annotates a microblog search result with encyclopedia entities.
-While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
-Thus, we chose to generate annotations for the whole search result.
-
-Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
-The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics.
-Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).
-External data sources also map to DBpedia, thus combined querying of external sources and Twitter search results becomes possible.
-Note however that a direct mapping of hashtags to entities is not possible in many cases: e.g.
-there is no entity in DBpedia which describes the European Semantic Web Conference 2011, thus the tag $\#eswc2011$ can not be mapped directly.
-
+We envision a system which automatically finds entities equivalent to a hashtag.
+%While it would be more interesting to annotate each single microblog message with relevant entities, microblog messages are too short to contain much relevant information which could be used as input for an annotation tool such as the Wikifier \cite{key:wikifier}.
+%Thus, we chose to generate annotations for the whole search result. 
+%Our implementation is based on Twitter, the most widely used and biggest microblogging platform, and on Wikipedia.
 Annotations should be stable over time, unless the topics discussed in the microblog messages containing the search term change.
-In an evaluation of our approach we have tried to analyse the stability of the result.
+In an evaluation of our approach we analyse the stability of the results of the entity matching for hashtag search results.
 
@@
 \small
-\begin{tabular}{l|l|l|l}
-Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
+\begin{tabular}{l|l|l|l|l}
+Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
 \hline
-$\#tilltheworldends$ & false & Britney Spears & .9583 \\
-& &  iTunes & .6875 \\
-& &  itunes & .625 \\ 
+\#tilltheworldends & - & false & Britney Spears & .9583 \\
+& & &  iTunes & .6875 \\
+& & &  itunes & .625 \\ 
 \hline
-$\#nowplaying$ & false & iTunes & .5208 \\
-& & Michael Jackson & .333 \\
-& & Lady Gaga & .333 \\
+\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
+             & are currently listening & & Michael Jackson & .333 \\
+             & to. & & Lady Gaga & .333 \\
 \hline
-$\#nowplaying$ & true & YouTube & .8235 \\
-& & Hip Hop Music & .6471 \\
-& & The Notorious B.I.G. & .5883 \\
+\#nowplaying & same & true & YouTube & .8235 \\
+             &  &  & Hip Hop Music & .6471 \\
+             &  &  & The Notorious B.I.G. & .5883 \\
 \hline
-$\#np$ & false & Chris Brown\_(entertainer) & .5 \\
-& & Usher & .3125 \\
-& & Lil Wayne & .2917 \\
+\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
+& & & Usher & .3125 \\
+& & & Lil Wayne & .2917 \\
 \hline
-$\#np$ & true & Chris Brown\_(entertainer) & .5 \\
-& & YouTube & .375 \\
-& & Ne-Yo & .315 \\
+\#np & same & true & Chris Brown\_(entertainer) & .5 \\
+& & & YouTube & .375 \\
+& & & Ne-Yo & .315 \\
 \hline
-$\#thataintwinning$ & false & Mozilla Firefox & .2291 \\
-& & Twitter & .2291 \\
-& & twitter & .1667 \\
+\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
+& & & Twitter & .2291 \\
+& & & twitter & .1667 \\
 \hline
-$\#thataintwinning$ & true & twitter & .5208 \\
-& & Twitter & .5 \\
-& & Two and a half men & .125 \\
+\#thataintwinning & - & true & twitter & .5208 \\
+& & & Twitter & .5 \\
+& & & Two and a half men & .125 \\
 \hline
-$\#blackpeoplemovies$ & false & Devil & .4791 \\
-& & Tyler Perry & .2708 \\
-& & Harry Potter & .2292 \\
+\#blackpeoplemovies & - & false & Devil & .4791 \\
+& & & Tyler Perry & .2708 \\
+& & & Harry Potter & .2292 \\
 \hline
-$\#blackpeoplemovies$ & true & Amazon.com & 1 \\
-& & YouTube & 1 \\
-& & amazon.com & 1
+\#blackpeoplemovies & - & true & Amazon.com & 1 \\
+& & & YouTube & 1 \\
+& & & amazon.com & 1
 \end{tabular}

### 2011-03-15 trunk/lids/twittersearchwrap/paper/paper.tex

@@
 \hline
+\#tilltheworldends & - & false & Britney Spears & 1 \\
+& & &  itunes & .75 \\
+& & &  Amazon.com & .5625 \\ 
+\hline
 \#nowplaying & What people on Twitter & false & iTunes & .5208 \\
@@
 We have described an implementation of two variants of the method and evaluated the approach.
+In an evaluation we have shown that meaningful entities were found for many hashtags and that these entities remain stable over time.
 
-Our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
+However, our evaluation has shown that a direct mapping of hashtags to a single DBpedia concept is not always possible.
 One reason is that hashtags do not necessarily describe an entity, but are rather used to describe contexts.
